### 2023-07-07 Article.tex
Initial commit

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[metals,article,submit,pdftex,moreauthors]{Definitions/mdpi}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

\usepackage{gensymb}
\usepackage{accents}
\usepackage{xspace}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{\alph{subfigure}}
\DeclareCaptionLabelFormat{subcaptionlabel}{\normalfont(\textbf{#2}\normalfont)}
\captionsetup[subfigure]{labelformat=subcaptionlabel}

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

% This is used to add comments into the text
%
% Will have to be removed from final version
%
\usepackage{soul}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150}
\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Pierre Tize Mha, Prashant Dhondapure, Mohammad Jahazi, Amèvi Tongne, Olivier Pantalé}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Tize Mha, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., Montréal, QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}

% Contact information of the corresponding author
\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.}
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{}

% Keywords
\keyword{artificial neural network; constitutive flow law; Gleeble}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
\cite{Pantale-2023}

%----------------------------------------------------------------------------------
\section{Conclusions\label{sec:Conclusions}}
%----------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Patents}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{
Conceptualization, P.T.M. and O.P.;
methodology, O.P.;
software, P.T.M. and O.P.;
validation, O.P.;
formal analysis, O.P.;
investigation, P.D.;
resources, P.D. and M.J.;
data curation, P.T.M. and P.D.;
writing---original draft preparation, P.T.M.;
writing---review and editing, O.P.;
visualization, O.P.;
supervision, M.J., A.T. and O.P.;
project administration, M.J.;
funding acquisition, M.J.
All authors have read and agreed to the published version of the manuscript.}

\funding{This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) (Grant Number 5364418).}

%\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

%\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.
%
%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{The raw/processed data required to reproduce these findings cannot be shared at this time due to privacy and ethical concerns.}

\acknowledgments{The authors acknowledge Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Abdelhalim Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK

\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
%\sampleavailability{Samples of the compounds ... are available from the authors.}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
ANN & Artificial neural network \\
AR & Arrhenius \\
CPU & Central processing unit \\
DRV & Dynamic recovery\\
DRX & Dynamic recrystallization \\
FEA & Finite element analysis \\
HS & Hansel--Spittel \\
JC & Johnson--Cook \\
MZA & Modified-Zerilli--Armstrong \\
WH & Work hardening \\
ZA & Zerilli--Armstrong
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}\label{sec:Appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
\bibliography{bibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2023-07-20 Article.tex
Update text and figures for first part

@@
 \usepackage{xspace}
+\usepackage{tabularx}
+
 \usepackage[labelformat=simple]{subcaption}
@@
 %----------------------------------------------------------------------------------
-\cite{Pantale-2023}
+
+%----------------------------------------------------------------------------------
+\section{Materials and experiments\label{sec:MaterialsExperiments}}
+%----------------------------------------------------------------------------------
+The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
+For further information, readers may refer to this other publication by our research team.
+We will, however, list here-after the main points required to understand the proposed approach. \OP{Add a small introduction}
+
+%----------------------------------------------------------------------------------
+\subsection{Experimental procedure and compression tests results\label{subsec:ExperimentalProcedure}}
+%----------------------------------------------------------------------------------
+The material used for this study is a medium-carbon steel with the chemical composition shown in Table \ref{tab:Composition}.
+\begin{table}[H]
+\centering
+\caption{Chemical composition of medium carbon steel. Fe = balance.}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LCCCCCCC}
+\hline
+\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
+\hline
+\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
+\hline
+\end{tabularx}
+\label{tab:Composition}
+\end{table}
+Hot compression tests of cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm were carried out on a Gleeble-3800 thermomechanical simulator, for $5$ temperature levels (between $1050\celsius$ and $1250\celsius$), and $6$ strain rates (between $0.001~\ps$ and $5~\ps$).
+The imposed displacement is set to $d=6$~mm, leading to a reduction of $40\%$ of the  initial height.
+To minimize friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
+To eliminate thermal gradients, the samples were heated at a rate of $2$\celsius/s to a temperature of $1260\celsius$ and held at that temperature for $5$~min.
+They were then cooled to the test temperature at a rate of $1$\celsius/s and then held at constant temperature for $1$~min prior to forming.
+During compression, the specimen temperature is kept constant by the machine's thermal control system.
+The sample is then rapidly cooled to freeze the microstructure for later analysis.
+
+The raw stress-strain data are exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of $30$ flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
+All strain/stress data is composed of $701$ equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\columnwidth]{Figures/rawData}
+\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device for 5 temperatures ($T$) and 6 strain rates ($\mdot\varepsilon$).}
+\label{fig:RawData}
+\end{figure}
+
+The flow stress ($\sigma$) increases with increasing strain rate ($\mdot\varepsilon$) but decreases with increasing temperature ($T$).
+It is noteworthy that the flow stress is also influenced by the strain.
+For the lowest strain rates, the flow stress increases up-to $\sigma_p$ with the strain until reaching a value of approximately $\varepsilon_p=0.2$ to $0.3$.
+Subsequently, it decreases to maintain a relatively constant value throughout the test.
+Conversely, for the highest strain rates (above $1~\ps$), the flow stress consistently increases during the entire test duration.
+The slight increase in stress at low strain rates with large strain values is due to friction between the sample and the anvil during testing as reported by Galos \eal \cite{Galos-2022}.
+This frictional effect becomes more pronounced as lubrication decreases over time.
+
+The initial stress increase observed during deformation up to $\varepsilon=0.1$ is attributed to work hardening (WH).
+Subsequently, from $\varepsilon=0.1$ to $0.2$, the flow stress demonstrates a continuous decline as the stress level increases until a peak or inflection point is reached, indicating the dominant influence of thermal softening surpassing work hardening.
+At this stage, the stress-strain curve exhibits three different patterns as the strain increases: (i) gradual decrease to a steady state with DRV/DRX softening.
+This pattern is observed for all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except for those at $1050\celsius$ and $1100\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$; (iii) continuous increase with significant work hardening observed for all deformation temperatures and a strain rate of $1~\ps$.
+This suggests that softening due to DRX (dynamic recrystallization) occurs at high temperatures and low strain rates.
+In contrast, at higher strain rates and lower temperatures, the rate of softening due to DRX is slowed down by higher work hardening rates.
+As a result, both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
+The drop in stress observed at all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is due to the occurrence of DRX.
+
+Dynamic recrystallization is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
+In some materials, such as aluminum, dynamic recrystallization can balance work hardening, resulting in the rapid appearance of a plateau.
+However, in many austenitic steels, the kinetics of restoration are weak and, as a result, dynamic recrystallization can be triggered at a critical condition of strain accumulation.
+Because of the significant influence of dynamic recrystallization on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of dynamic recrystallization is therefore crucial to good material characterization.
+Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition dynamic recrystallization, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
+However, this technique requires extensive sampling before and after critical deformation.
+In addition, phase changes during cooling from the hot working temperature modify the deformed structure, making metallographic analysis difficult.
+Hence the need for simpler techniques, such as the development of analytical models.
+With this in mind, a number of studies have been carried out to determine analytically the initiation of dynamic recrystallization.
+
+In this paper we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to compute the evolution of DRX of the material during the deformation.
+The raw data acquired from the Gleeble thermosimulator will subsequently be used to identify the material flow law and the parameters of the DRX model.
+
+%----------------------------------------------------------------------------------
+\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
+%----------------------------------------------------------------------------------
+
+In this Section we will determine the critical deformation required to initiate recrystallization.
+Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of dynamic recrystallization and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
+Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the dynamic recrystallization hypothesis describing this inflection point.
+Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of dynamic recrystallization.
+In their approach, a polynomial of $3^\text{th}$ degree is adopted to describe the shape of the curve $\theta(\sigma)$ and, using the second derivative, they manage to identify the critical stress and strain ($\sigma_c$ and $\varepsilon_c$).
+
+As introduced earlier, the determination of critical values for the initiation of DRX involves determining the inflection point located on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
+One of the first difficulties is to numerically evaluate the value of the derivative of stress versus strain, since experimental data from compression tests show oscillations, as illustrated in Figure \ref{fig:RawData}.
+It is therefore not possible to calculate the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.
+
+To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for \cite{Najafizadeh-2006}) or identifying an analytical form (e.g.
+a polynomial of relatively high order) using a minimization algorithm.
+But, depending on the degree of the polynomial and for the same stress/strain curve, several solutions can be obtained, leading to the definition of several possible forms for the $\theta(\sigma)$ function.
+
+%----------------------------------------------------------------------------------
+\subsubsection{ANN based filtering method for raw data\label{subsec:ANNbasics}}
+%----------------------------------------------------------------------------------
+In order to improve the results obtained from the critical value identification procedure, we propose here to use the universal approximator capability of artificial neural networks to replace each strain-hardening curve by its representation in the form of an ANN with 1 input (strain) and 1 output (stress).
+In such a network, each layer of neurons is connected to the one before it and the one after it by weighted connections.
+Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
+\begin{equation}
+y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
+\end{equation}
+where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
+Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
+For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+\begin{equation}
+\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
+\end{equation}
+
+No activation function was used for the output neuron of the ANN as usually done in a regression application.
+The architecture chosen for our application corresponds to 2 hidden layers of 7 and 5 neurons respectively, as illustrated in Figure \ref{fig:ANN-7-5}.
+If $n$ and $m$ are the number of neurons of the first and second hidden layers respectively, the number of internal parameters $N_{int}$ of the model is given by $N_{int}=m(2+n)+2n+1$.
+So that for a $7-5$ network, $N_{int}=60$.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
+\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\label{fig:ANN-7-5}
+\end{figure}
+The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
+The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
+
+%----------------------------------------------------------------------------------
+\subsubsection{ANN filtering results and DRX model parameters evaluation\label{subsec:ANNapplication}}
+%----------------------------------------------------------------------------------
+Since the DRX occurs only for the 4 strain rates within the range $[0.001~\ps-1.0~\ps]$, we will only use the first 20 stress/strain curves for the DRX critical parameters' identification.
+Each of the 20 curves, made up of 701 couples of strain-stress values, was processed independently by a neural network, leading to 20 identified architectures.
+As an example, Figure \ref{fig:AnnFit} shows the experimental values of the stress/strain curve for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (blue line) and the results from the neural network identified from these data (red line).
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
+\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\label{fig:AnnFit}
+\end{figure}
+The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
+\begin{equation}
+\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
+\end{equation}
+and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
+\begin{equation}
+\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
+\end{equation}
+where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
+For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
+\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\label{fig:AnnTheta}
+\end{figure}
+
+%\begin{table}[H]
+%\caption{Architecture and accuracy coefficients for all the proposed networks.}
+%\newcolumntype{C}{>{\centering\arraybackslash}X}
+%\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+%\begin{tabularx}{\textwidth}{LCCCCCC}
+%\hline
+%Coefficient & $\mdot\varepsilon$ & $1050\celsius$ & $1100\celsius$ & $1150\celsius$ & $1200\celsius$ & $1250\celsius$  \\
+%\hline
+%$\MARE(\%)$ & $0.001$ & $0.231$ & $1.13$ & $1.05$ & $1.08$ & $0.75$ \\
+%$\RMSE(\MPa)$ & $0.001$ & $0.093$ & $0.59$ & $0.57$ & $0.65$ & $0.46$ \\
+%\hline
+%\end{tabularx}
+%\label{tab:Errors}
+%\end{table}
+
+%----------------------------------------------------------------------------------
+\section{Numerical simulation of the compression\label{sec:NumSim}}
+%----------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------
+\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
+%----------------------------------------------------------------------------------
+In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
+The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
+This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
+Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
+As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to dynamic recrystallization visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
+Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
+Only the Arrhenius model can more or less account for this softening at low strain rates.
+As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
+Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.
+
+According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we developed in Tize Mha \eal \cite{TizeMha-2023} a two hidden layers ANN based flow law whose general structure is reported in Figure \ref{fig:ANN-2HL}.
+This ANN contains an input layer of three neurons corresponding to the entries of the model ($\varepsilon$, $\mdot\varepsilon$ and $T$), an output layer with one neuron ($\sigma$), and $2$ hidden layers.
+
+All details about the artificial neural network, setup of the experimental data and the training method is reported the paper proposed by Pantalé \cite{Pantale-2023}.
+%Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/ANN-scheme-2HL}
+\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
+\label{fig:ANN-2HL}
+\end{figure}
+
+We again used the Tensorflow library for the development of the training program, and the ADAM optimizer was used for the training phase.
+The provided database presented in Section \ref{subsec:ExperimentalProcedure} consists of $21,030$ quadruplets of strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$) and stress ($\sigma$) values.
+%The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of $21,030$ quadruplets of ($\varepsilon$, $\mdot\varepsilon$, $T$, $\sigma$) values.
+
+We selected 6 different networks, named 3-$n$-$m$-1, where $n$ is the number of neurons in the first hidden layer and $m$ is the number of neurons in the second hidden layer, to show the importance of selecting the adequate number of neurons in the two layers.
+
+The training was performed on the basis of $5000$ epochs of the experimental dataset.
+It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
+
+Figure \ref{fig:ANN-conv} shows the evolution of the training error defined by the $\log_{10}$ of the internal $\RMSE$ during the training phase and Table \ref{tab:Errors} summarizes the final values of this criterion, along with the final values of the $\MARE$ and the $\RMSE$ for the 6 configurations of the neural network.
+On the basis of those results, we have selected the 3-15-7-1 network for further study, as it has the best convergence evolution and the lowest final error values ($\MARE=0.62\%$ and $\RMSE=0.38~\MPa$), while keeping a reasonable number of internal parameters ($N_{int}=180$).
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/Conv-ANN-6}
+\caption{Evolution of the convergence of the models during the training procedure for the 6 proposed network architectures.}
+\label{fig:ANN-conv}
+\end{figure}
+
+\begin{table}[H]
+\caption{Architecture and accuracy coefficients for all the proposed networks.}
+\newcolumntype{C}{>{\centering\arraybackslash}X}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\begin{tabularx}{\textwidth}{LCCCCCC}
+\hline
+\textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
+\hline
+$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
+\hline
+$\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
+$\MARE(\%)$ & $1.13$ & $1.05$ & $1.08$ & $0.91$ & $0.75$ & $0.62$ \\
+$\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
+\hline
+\end{tabularx}
+\label{tab:Errors}
+\end{table}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\columnwidth]{Figures/CompExpANN-3-15-7-1}
+\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma$ by the 3-15-7-1 ANN model.}
+\label{fig:ANN-3-15-7-1}
+\end{figure}
+This model will be used as the material flow law for the numerical simulations presented in Section \ref{subsec:DRXSimulation}.
+
+%----------------------------------------------------------------------------------
+\subsection{DRX simulation\label{subsec:DRXSimulation}}
+%----------------------------------------------------------------------------------
 

### 2023-08-22 Article.tex
Article update

@@
 \usepackage{tabularx}
+\usepackage{lscape}
+\usepackage{comment}
+\usepackage{inputenc}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Title}
+\Title{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}
+
+%\Title{Artificial neural network based critical conditions for dynamic recrystallization initiation of medium carbon steel  and Application : Analytical and Finite Element Modeling}%
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Title}
+\TitleCitation{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}
 
@@
 \newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
-\newcommand{\orcidauthorC}{0000-0002-5360-5121}
+\newcommand{\orcidauthorC}{0000-0002-5360-5121}% Add \orcidB{} behind the
+%author's name
+\newcommand{\orcidauthorD}{0000-0002-0815-1984}
 
 % Authors, for the paper (add full first names)
-\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
+\Author{Pierre Tize Mha $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{}
+\abstract{\textcolor{red}{The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
+As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
+These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
+As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
+These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
+As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
+These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.}}
 
@@
 %----------------------------------------------------------------------------------
+Dynamic recrystallization (DRX) is a process that occurs in certain materials, especially in metals and alloys, when they undergo plastic deformation (deformation that is not reversible).
+It is a phenomenon commonly observed during hot working processes like hot rolling, hot forging, or hot extrusion.
+When a metal or alloy is subjected to high temperatures and significant plastic deformation, the existing grain structure is broken down, and new, smaller grains form in its place and this phenomenon is called DRX.
+It is different from static recrystallization, which occurs at lower temperatures and takes longer to form new grains.
+The process of DRX is driven by the energy stored in the metal due to plastic deformation.
+As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
+These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.
+DRX offers several advantages during hot working processes in the sense that it helps in refining the grain size, which enhances the mechanical properties of the material, such as strength and toughness.
+Additionally, it reduces the overall strain energy, which can lead to a more uniform microstructure and improved material properties.
+
+It is well known that during hot deformation with a relatively high strain rate, the dislocation density increases while dynamic recovery (DRC) tries to diminish the density.
+If the rate of dislocation density increase is greater than can be accommodated by DRC, DRX is initiated at a certain point.
+This applies particularly to low and medium stacking fault energy for fcc metals.
+Therefore, mastery of critical conditions for DRX is of considerable interest for the modeling of industrial processes but the extent of DRX depends on several factors, including the material's composition, deformation temperature, strain rate, and the degree of deformation.
+It is an essential phenomenon to be taken into account and controlled in industrial processes where hot working is employed to shape metals and alloys into various products.
+By optimizing the parameters, engineers can achieve desired microstructures and mechanical properties in the final product.
+Several researchers have proposed various techniques to determine DRX's critical conditions such as metallography.
+However, this technique requires extensive sampling before and after the critical deformation.
+Additionally, phase changes during cooling from the hot working temperature alter the deformed structure, making metallographic analysis challenging.
+Hence, there is a need to resort to other simpler techniques, such as the development of analytical models.
+In this context, several studies have been conducted to analytically determine the initiation of DRX.
+For example, Barnett \eal \cite{barnett2000predicting} have identified the critical strain for initiation of DRX using the kinetics of static recrystallization (SRX) modified to allow SRX to begin before the end of deformation.
+This approach defines the critical stress for the initiation of SRX during deformation.
+On the basis of a dislocation density work hardening model, Gottstein \eal \cite{gottstein2004prediction} have also predicted the critical strain for initiation of DRX.
+The onset of DRX can also be identified phenomenologically from the inflection point in the strain hardening rate $\theta=\frac{\partial \sigma}{\partial \varepsilon} = f(\sigma)$ whose understanding is crucial in materials processing and design..
+
+The DRX phenomenon based on inflection point was first studied by Ryan and McQueen \cite{ryan1989dynamic,ryan1990dynamic,ryan1990flow}, who observed the appearance of an inflection point on the curve $\theta=f(\sigma)$ before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this inflection point.
+Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} further demonstrated that this inflection point is associated with the thermodynamic energy released during the movement of dislocations, thus confirming the hypothesis of DRX describing this inflection point; this signifies that an additional softening mechanism begins to operate (in addition to DRC).
+Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used nowadays, to determine the critical conditions for the initiation of DRX.
+In their approach, they adopted a third-degree polynomial to describe the shape of the curve $\theta=f(\sigma)$ and, by using the second derivative, they identified the critical strain $\varepsilon_c$ and stress $\sigma_c$.
+Once the critical conditions are calculated, they are considered as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}, which is widely used to estimate the volumic fraction of DRX ($X_{drx}$) during hot working.
+Li \eal \cite{li2015experimental} explored the DRX characteristics of micro-alloyed plastic molding steel, using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to identify all key parameters.
+Zhang \eal \cite{zhang2016kinetics} studied the DRX behaviors of medium carbon CreNieMo steel alloy using the Avrami kinetics model equation, and qualitatively characterized the metallurgical properties as a function of the Zener-Hollomon parameter.
+Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} predicted the microstructural evolution of Mn alloy (with an emphasis on the DRX and grain growth phenomena) using this well-known model and found that the predicted microstructures were consistent with those revealed by multiple compression tests.
+The same equation was used by Wan \eal \cite{wan2017experimental} to predict the microstructural evolution of TiAl-based alloys during hot compression.
+Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts.
+Cui \eal \cite{cui2016hot} investigated DRX using the Avrami
+kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.
+
+The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained.
+Indeed, the direct use of raw data from experiments does not provide usable curves.
+Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it.
+The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$.
+However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior.
+Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX.
+In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data.
+By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.
+\textcolor{red}{Using ANN in materials science and engineering has gained popularity due to their ability to learn complex patterns and relationships from data, making them valuable tools for various predictions and analyses in the field.
+By leveraging a ANN in this context, researchers aim to improve the accuracy and reliability of predictions related to DRX behavior in materials during deformation}.
 
@@
 The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
-For further information, readers may refer to this other publication by our research team.
-We will, however, list here-after the main points required to understand the proposed approach. \OP{Add a small introduction}
+For further information, readers may refer to this other publication by our research group.
+We will, however, list here-after the main points required to understand the proposed approach.
+The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
+At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
+In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
+It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.\OP{Already done}
 
@@
 This pattern is observed for all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except for those at $1050\celsius$ and $1100\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$; (iii) continuous increase with significant work hardening observed for all deformation temperatures and a strain rate of $1~\ps$.
-This suggests that softening due to DRX (dynamic recrystallization) occurs at high temperatures and low strain rates.
+This suggests that softening due to DRX  occurs at high temperatures and low strain rates.
 In contrast, at higher strain rates and lower temperatures, the rate of softening due to DRX is slowed down by higher work hardening rates.
@@
 
-Dynamic recrystallization is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
-In some materials, such as aluminum, dynamic recrystallization can balance work hardening, resulting in the rapid appearance of a plateau.
-However, in many austenitic steels, the kinetics of restoration are weak and, as a result, dynamic recrystallization can be triggered at a critical condition of strain accumulation.
-Because of the significant influence of dynamic recrystallization on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of dynamic recrystallization is therefore crucial to good material characterization.
-Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition dynamic recrystallization, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
+DRX is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
+In some materials, such as aluminum, DRX can balance work hardening, resulting in the rapid appearance of a plateau.
+However, in many austenitic steels, the kinetics of restoration are weak and, as a result, DRX can be triggered at a critical condition of strain accumulation.
+Because of the significant influence of DRX on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of DRX is therefore crucial to good material characterization.
+Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition DRX, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
 However, this technique requires extensive sampling before and after critical deformation.
@@
 Hence the need for simpler techniques, such as the development of analytical models.
-With this in mind, a number of studies have been carried out to determine analytically the initiation of dynamic recrystallization.
+With this in mind, a number of studies have been carried out to determine analytically the initiation of DRX.
 
@@
 The raw data acquired from the Gleeble thermosimulator will subsequently be used to identify the material flow law and the parameters of the DRX model.
+The parameters of JMAK model are obtained through a two-step process.
+Firstly, the critical stresses and strains are determined, where the ANN model is utilized to obtain well-filtered curves.
+Secondly, these critical values are employed as input data for the calculation of parameters in the JMAK model, aiming to predict the volume fraction of dynamic recrystallization.
 
@@
 In this Section we will determine the critical deformation required to initiate recrystallization.
-Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of dynamic recrystallization and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
-Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the dynamic recrystallization hypothesis describing this inflection point.
-Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of dynamic recrystallization.
+Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of DRX and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
+Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the DRX hypothesis describing this inflection point.
+Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of DRX.
 In their approach, a polynomial of $3^\text{th}$ degree is adopted to describe the shape of the curve $\theta(\sigma)$ and, using the second derivative, they manage to identify the critical stress and strain ($\sigma_c$ and $\varepsilon_c$).
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN based filtering method for raw data\label{subsec:ANNbasics}}
+\subsubsection{ANN based filtering model's archicture \label{subsec:ANNbasics}}
 %----------------------------------------------------------------------------------
@@
 \begin{figure}[H]
-\centering
+%\centering
 \includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN filtering results and DRX model parameters evaluation\label{subsec:ANNapplication}}
+\subsubsection{ANN filtering based model's application \label{subsec:ANNapplication}}
 %----------------------------------------------------------------------------------
@@
 \begin{figure}[H]
-\centering
+%\centering
 \includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
@@
 
+It can clearly be observed that using the ANN model to describe the $\sigma=f(\varepsilon)$ curve is better than using a $11^{th}$ order polynomial fit, as evidenced by the lower estimated error.
+Therefore, this architecture of the ANN model is employed for the remaining curves, leading directly to deduce the hardening $\theta=f(\sigma)$ curves, which represent the rate of change of stress with respect to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
+An example of computing the hardening curve for one temperature is given on Figure \ref{fig:AnnTheta} and for remaining temperatures, Figure \ref{fig:nThetaOP} can give an overview.
+The same procedure is used for the four initial strain rates.
+These curves provide essential information about critical stresses and strains needed for predicting DRX in the subsequent analysis.
+
 \begin{figure}[H]
-\centering
+%\centering
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\caption{An example of computing hardening curve based on ANN model.}
 \label{fig:AnnTheta}
@@
 
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
+\caption{Work hardening computation for $1$ strain rate and $5$ temperatures.}
+\label{fig:nThetaOP}
+\end{figure}
+
+%----------------------------------------------------------------------------------
+\subsubsection{Critical conditions evaluation\label{subsec:CrConditions}}
+%----------------------------------------------------------------------------------
+As mentioned in the previous section, dynamic recrystallization initiates if and only if a certain critical condition level is reached.
+Determining these critical conditions remains challenging, as it requires the development of models capable of calculating the corresponding critical stress and strain.
+Thus, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, widely recognized today, will be employed in this study.
+The method involves using a third-degree polynomial function to describe the functions $\theta(\sigma)$ and $\ln \theta(\varepsilon)$curves as shown in Figure \ref{fig:fThetaOP} , with the purpose of identifying the inflection points corresponding to critical stress $\sigma_c$ and critical strain $\varepsilon_c$.
+Also from those curves, peak stress $\sigma_p$ and peak strain $\varepsilon_p$ can be deduced.
+The Poliak and  Jonas model \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} is given as follow:
+\begin{equation}
+\theta = A\sigma^3 + B\sigma^2 + C\sigma + D
+\end{equation}
+Where $A, B, C,$ and $D$ are constants specific to a given deformation condition.
+The inflection point of a function is determined by setting the second derivative of that function to zero and the following equation is obtained:
+\begin{equation}
+\frac{d^2 \theta}{d \sigma^2} = 6A\sigma + 2B
+\end{equation}
+Therefore, the critical stress for the initiation of DRX is obtained as follows:
+\begin{equation}
+6A\sigma_c + 2B = 0 \Longrightarrow \sigma_c = -B/3A
+\end{equation}
+Similarly, the critical strain is calculated using the following equations:
+\begin{equation}
+\ln \theta = A_1\varepsilon^3 + B_1\varepsilon^2 + C_1\varepsilon + D_1 
+\end{equation}
+\begin{equation}
+\frac{d^2 \ln \theta}{d \varepsilon^2} = 6\varepsilon A_1 + 2B_1 ~~\text{and} ~~\frac{d^2 \ln \theta}{d \varepsilon^2}= 0 \Longrightarrow \varepsilon_c = -B_1/3A_1
+\end{equation}
+Applying the same method to the first four strain rates and all temperatures, the critical stress and strain, peak stress and peak strain are summarised in the Table \ref{tab:OPparams}.
+Once the critical conditions of the DRX are known, therefore they can be used as input to deduce the volume fraction of the DRX, which will be the subject of the next section.
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
+\caption{Work hardening polynomial fiting based on Poliak and Jonas  model  \cite{najafizadeh2006predicting}.}
+\label{fig:fThetaOP}
+\end{figure}
+
+\begin{comment}
+\begin{landscape}
+\begin{table}[h]
+\caption{functions $\theta=f(\sigma)$ and $\ln\theta=f(\varepsilon)$ coefficients based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}\vspace{1mm}
+%\begin{center}
+\begin{tabular}{cccc}
+\toprule
+$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C)  & $\theta$ = f($\sigma$) & $\ln$$\theta$=f($\varepsilon$)\\
+\hline
+&$1050	$&$ -0.252593\sigma^3 + 23.2834\sigma^2 - 719.045\sigma + 7561.2	 $&$-2274.82\varepsilon^3 + 592.899\varepsilon^2 - 61.0014\varepsilon + 6.71048$\\
+&$1100	$&$ -0.469287\sigma^3 + 35.0169\sigma^2 - 875.042\sigma + 7418.89	 $&$-4813.49\varepsilon^3 + 1020.98\varepsilon^2 - 79.8778\varepsilon + 6.65741$\\
+$0.001	$&$1150	$&$ -0.280343\sigma^3 + 15.2183\sigma^2 - 287.655\sigma + 2008.9	 $&$-899.654\varepsilon^3 + 15.7144\varepsilon^2 - 17.0976\varepsilon + 5.59789$\\
+&$1200	$&$ -0.165122\sigma^3 + 7.34045\sigma^2 - 127.854\sigma + 949.691	 $&$10803.3\varepsilon^3 - 1567.6\varepsilon^2 + 31.5185\varepsilon + 4.92891$\\
+&$1250	$&$ 0.430135\sigma^3 - 13.9807\sigma^2 + 123.725\sigma - 137.032 	 $&$-9130.5\varepsilon^3 + 1125.18\varepsilon^2 - 69.4152\varepsilon + 5.34578$\\
+%\hline
+&$1050	$&$ -0.316563\sigma^3 + 41.6041\sigma^2 - 1780.61\sigma + 24890.6	 $&$-760.548\varepsilon^3 + 302.444\varepsilon^2 - 47.4264\varepsilon + 6.96767$\\
+&$1100	$&$-0.254362\sigma^3 + 27.7695\sigma^2 - 1002.47\sigma  + 12089.1   $&$-957.925\varepsilon^3 + 326.362\varepsilon^2 - 48.1866\varepsilon + 6.78809$\\
+$0.01	$&$1150	$&$ -0.125197\sigma^3 + 11.765\sigma^2 - 378.088\sigma + 4266.7$&$-1904.84\varepsilon^3 + 452.618\varepsilon^2 - 46.9027\varepsilon + 6.35515$\\
+&$1200	$&$ -0.386264\sigma^3 + 28.6922\sigma^2 - 713.252\sigma + 6045.79	 $&$-1260.32\varepsilon^3 + 283.718\varepsilon^2 - 39.3944 \varepsilon + 6.12705$\\
+&$1250	$&$ -0.274371\sigma^3 + 15.2491\sigma^2 - 291.928\sigma + 2051.22	 $&$2054.13\varepsilon^3 - 545.571\varepsilon^2 + 11.6535\varepsilon + 5.15417$\\
+%\hline
+&$1050	$&$ -0.109041\sigma^3 + 22.8574\sigma^2 - 1554.51\sigma + 34276.6	 $&$22.5257\varepsilon^3 - 10.6333\varepsilon^2 - 10.5919\varepsilon + 6.15546$\\
+&$1100	$&$ -0.197437\sigma^3 + 32.5449\sigma^2 - 1740.23\sigma + 30179.2	 $&$-119.588\varepsilon^3 + 98.0419\varepsilon^2 - 32.5318\varepsilon + 6.75459$\\
+$0.1	$&$1150	$&$ -0.273236\sigma^3 + 36.2143\sigma^2 - 1566.6\sigma + 22180.5	 $&$-245.608\varepsilon^3 + 155.747\varepsilon^2 - 40.2746\varepsilon + 6.76$\\
+&$1200	$&$ -0.263314\sigma^3 + 29.6662\sigma^2 - 1095.93\sigma + 13363.4	 $&$-113.711\varepsilon^3 + 65.8505\varepsilon^2 - 25.9935\varepsilon + 6.30479$\\
+&$1250	$&$ -0.390101\sigma^3 + 36.635\sigma^2 - 1132.85\sigma + 11626.3	 $&$-66.6657\varepsilon^3 + 88.2893\varepsilon^2 - 33.1747\varepsilon + 6.35758$\\
+%\hline
+&$1050	$&$ -0.0746046\sigma^3 + 21.1153\sigma^2 - 1933.09\sigma + 56923.3    $&$ -23.0014\varepsilon^3 + 42.4459\varepsilon^2 - 23.8994\varepsilon + 6.7553$\\
+&$1100	$&$ -0.107164\sigma^3 + 25.6015\sigma^2 - 1978.33\sigma + 49199	 $&$-13.408\varepsilon^3 + 30.6189\varepsilon^2 - 20.0411\varepsilon + 6.3443$\\
+$1	$&$1150	$&$ -0.139902\sigma^3 + 27.9237\sigma^2 - 1799.15\sigma + 37231	 $&$-14.1508\varepsilon^3 + 30.1129\varepsilon^2 - 19.4669\varepsilon + 6.11887$\\
+&$1200	$&$ -0.150668\sigma^3 + 25.0242\sigma^2 - 1351.37\sigma + 23734.1	 $&$ 26.6437\varepsilon^3 - 11.2098\varepsilon^2 - 9.52699\varepsilon + 5.39017$\\
+&$1250	$&$ -0.112709\sigma^3 + 16.0385\sigma^2 - 751.823\sigma + 11702	 $&$ 55.0921\varepsilon^3 - 38.055\varepsilon^2 - 4.07206\varepsilon + 4.95987$\\
+\bottomrule
+\end{tabular}	
+%\end{center}
+\label{tab:JJparams1}
+\end{table}
+\end{landscape}
+\end{comment}
+
+\begin{table}[h!]
+\caption{Critical conditions based on Poliak and Jonas model  \cite{najafizadeh2006predicting}.}\vspace{-5mm}
+\begin{center}
+\begin{tabular}{cccccc}
+\toprule
+$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C) & $\varepsilon_p$ & $\sigma_p$ (MPa)& $\varepsilon_c$ & $\sigma_c$ (MPa) \\
+\hline
+         & $1050$  & $0.178$  & $37.862$& $0.083$ & $33.050$ \\
+& $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$ \\
+$0.001$  & $1150$  & $0.124$  & $23.330$& $0.051$ & $19.116$ \\
+& $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$ \\
+& $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$ \\
+
+& $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$ \\
+& $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$ \\
+$0.01$   & $1150$  & $0.195$  & $38.249$& $0.086$ & $33.435$ \\
+& $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$ \\
+& $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$ \\
+
+& $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$ \\
+& $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$ \\
+$0.1$    & $1150$  & $0.344$  & $57.774$& $0.160$ & $51.723$ \\
+& $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$ \\
+& $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$ \\
+
+& $1050$ & $0.700$ & $127.172$&$0.577$ /&$116.1$ / \\ 
+& $1100$ & $0.700$ & $106.608$& $0.329$/& $94.51$/ \\
+$1$      & $1150$  & $0.700$  & $89.525$& $0.668$ & $89.067$ \\
+& $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$ \\
+& $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$ \\
+\bottomrule
+\end{tabular}	
+\end{center}
+\label{tab:OPparams}
+\end{table}
+
+%----------------------------------------------------------------------------------
+\subsection{DRX model parameters evaluation\label{subsec:DRXparams}}
+%----------------------------------------------------------------------------------
+The DRX begins at a critical deformation, as previously mentioned, and the level of recrystallization can be determined experimentally.
+Figure \ref{fig:DRXschema} illustrates three stages of recrystallization: nucleation, grain growth, and grain coalescence.
+\begin{figure}[!ht]
+%\centering
+\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
+\caption[Diagramme des trois étapes de la DRX]{Diagramme des trois étapes de la DRX \cite{wan2017experimental}}
+\label{fig:DRXschema}
+\end{figure}
+The subsequent behavior of DRX affects the material's flow stress curve as the rate of work hardening is influenced by dislocations within the free grains.
+The Avrami model is the most commonly used law to predict this behavior, known as the JMAK model, whose expression is given by the following equation estimating the volumic fraction of the DRX:
+\begin{equation}
+X_{drx,pred} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
+\label{eq:drxpred}
+\end{equation}
+With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
+\begin{equation}
+X_{drx,exp} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
+\label{eq:drxexp}
+\end{equation}
+
+Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress resectivly.
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation:
+\begin{equation}
+\begin{cases}
+\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
+\end{cases}
+\label{eq:paramsZ}
+\end{equation}
+With $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$ the parameters describing the dependency of specific strains and stresses on the Zener-Hollomon parameter where their identification procedure is explained later in this paper.
+
+The calculation of the parameters of JMAK model involves two main steps.
+Firstly, it entails determining the coefficients $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$.
+Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).To compute these parameters, a Python code using the $curve\_fitting$ method is used.
+Specifically, the critical strains and stresses calculated in the previous sections are used as input data for these parameter identifications.
+The curve fitting method aims to find the best-fitting values for the coefficients by iteratively adjusting them to minimize the difference between the predicted and experimental critical strains and stresses.
+This optimization process involves trying various combinations of the coefficients and evaluating their fitness to the given data.
+The curve fitting technique adjusts the coefficients until it achieves the closest match between the model's predictions and the experimental values.
+
+Once the constants that define the Zener-Hollomon parameter dependency are calculated, they can be used to deduce the JMAK model parameters using an optimization technique that minimizes the error between the predicted recrystallization $X_{drx, pred}$ and the experimental value $X_{drx, exp}$.
+The dependency of the Zener-Hollomon parameters and the JMAK model parameters  are provided in the Table \ref{tab:allparams}.
+
+\begin{table}[h]
+%\centering{}
+\caption{JMAK model and Zener-Hollomon dependency parameters }\vspace{-1mm}
+\begin{tabular}{cc}
+\toprule
+Parameters & Values  \\
+\hline
+$A_c$&$4.4268\times10^{-5}	$\\
+$A_p$&$29.85\times10^{-5}$\\
+$B_c$&$0.0720627$\\
+$B_p$&$0.103141	$\\
+$B_s$&$10265.8	$\\
+$n_c$&$0.235832	$\\
+$n_p$&$0.203678	$\\
+$m_c$&$0.188236	$\\
+$m_p$&$0.181822	$\\
+$m_s$&$-0.19708	$\\
+$k$  &$0.48632	$\\
+$n_k$&$3.36531$ \\
+\bottomrule
+\end{tabular}	
+\label{tab:allparams}
+\end{table}
+
+The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
+From this figure, we can observe that the predictions align well with the experimental data, thus demonstrating the validity of the utilized model.
+Therefore, these results will be used subsequently in the simulation section.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.99\columnwidth]{Figures/nDRX}
+\caption{Comparision beteween DRX experimental data and JMAK model based prediction}
+\label{fig:nDRX}
+\end{figure}
 %\begin{table}[H]
@@
 %----------------------------------------------------------------------------------
-
+In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed.
+To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of this particular material.
+In our prior publication, a comparison between analytical constitutive laws and neural network-based approaches was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
+As a result, this section comprises a two-fold focus: firstly, a recapitulation of the constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
 %----------------------------------------------------------------------------------
@@
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
-As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to dynamic recrystallization visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
+As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to DRX visible on experimental curves for strain rates below $1~\ps$ as reported in Figure  \ref{fig:RawData}.
 Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
@@
 \begin{figure}[H]
-\centering
+%\centering
 \includegraphics[width=0.7\columnwidth]{Figures/ANN-scheme-2HL}
@@
 \subsection{DRX simulation\label{subsec:DRXSimulation}}
+In order to assess the effectiveness of the implementation of the model presented in the previous sections, a compression test is simulated in this section.
+For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model.
+An axisymmetric Finite Element Method (FEM) model of hot cylinder compression with a height of $15$ mm and a diameter of $5$ mm is used, as shown in Figure \ref{fig:Mesh}.
+The frictional coefficient at the material/Die interface was assumed to be $0.2$ \cite{zhang2019elevated,sun2020kinetique}.
+The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
+The FEM model is simulated using Abaqus/Implicit due to the computation time caused by the low strain rates.
+A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen.
+The radial displacement $u_r$ of the upper part of the specimen is left free, while its axial displacement $u_z$ is imposed.
+The lower part of the cylinder remains fixed during the simulation.
+The effect of reducing the cylinder in combination with strain rate or temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
+For this simulation, three temperatures ($1050^\circ$C, $1150^\circ$C, and $1250^\circ$C) and four strain rates ($0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$ and $1.0~\text{s}^{-1}$) are considered.
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
+\caption{Numerical model for the compression test}
+\label{fig:Mesh}
+\end{figure}
+
 %----------------------------------------------------------------------------------
-
+\subsubsection{Temperature effect on DRX distribution\label{subsec:TempEffect}}
+%----------------------------------------------------------------------------------
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.98\columnwidth]{Figures/Temp_DRX}
+\caption{$X_{drx}$ values at a strain rate of $0.01~\text{s}^{-1}$ for different reductions and initial temperatures.}
+\label{fig:TempEffect}
+\end{figure}
+%----------------------------------------------------------------------------------
+\subsubsection{Strain rate effect on DRX distribution\label{subsec:SRatEffect}}
+%----------------------------------------------------------------------------------
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.98\columnwidth]{Figures/SR_DRX}
+\caption{$X_{drx}$ values at a fixed $T_0=1150^\circ$C for different reductions and strain rates.}
+\label{fig:SREffect}
+\end{figure}
 %----------------------------------------------------------------------------------
@@
 CPU & Central processing unit \\
-DRV & Dynamic recovery\\
+DRC & Dynamic recovery\\
 DRX & Dynamic recrystallization \\

### 2023-08-23 Article.tex
semifinal version of the paper

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{\textcolor{red}{The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
-As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
-These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
-As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
-These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.The process of dynamic recrystallization is driven by the energy stored in the metal due to plastic deformation.
-As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
-These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.}}
+\abstract{This study presents a novel and comprehensive approach for understanding and simulating the dynamic recrystallization (DRX) process during hot compression.
+To achieve this, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800 and ANN based flow behaviour law was used to model the plastic behaviour.
+The accuracy of the DRX volumic fraction, both during its identification using analytical models and its numerical implementation in finite element software, relies on critical conditions and therfore, in this study, an artificial neural network, as a universal approximator, is proposed to fit the necessary data for calculating the critical conditions of DRX.
+The JMAK model was used as an analytical model to calculate the volumic fraction of DRX, and its validation against experimental data was successful.
+A numerical implementation of the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model was implemented into ABAQUS software, and the obtained results were compared with experimental data through microstructure analysis, revealing a strong correlation between simulation and experimentation.
+Temperature, strain rate and the amount of deformation effects on DRX evoultion were also investigated in this study and it was observed that the DRX rises with temperature and deformation while it decreases with the increase of strain rates.
+}
 
 % Keywords
-\keyword{artificial neural network; constitutive flow law; Gleeble}
+\keyword{Artificial Neural Network; Constitutive Flow Law; Gleeble simulator, Dynamic Recrystallization, Finite Element Analysis}
 
@@
 \begin{document}
-
 %----------------------------------------------------------------------------------
@@
 Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts.
-Cui \eal \cite{cui2016hot} investigated DRX using the Avrami
-kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.
+Cui \eal \cite{cui2016hot} investigated DRX using the Avrami kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.
+Recently, Chen \eal \cite{chen2023finite} performed Finite Element Analysis of DRX based on GCr15 microstruture analysis and observed that temperature, strain rate have important effect on the DRX initiation.
 
@@
 By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.
-\textcolor{red}{Using ANN in materials science and engineering has gained popularity due to their ability to learn complex patterns and relationships from data, making them valuable tools for various predictions and analyses in the field.
-By leveraging a ANN in this context, researchers aim to improve the accuracy and reliability of predictions related to DRX behavior in materials during deformation}.
 
@@
 In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
-It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.\OP{Already done}
+It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
 
@@
 
-To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for \cite{Najafizadeh-2006}) or identifying an analytical form (e.g.
+To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for example \cite{Najafizadeh-2006}) or identifying an analytical form (e.g.
 a polynomial of relatively high order) using a minimization algorithm.
@@
 \begin{table}[h!]
-\caption{Critical conditions based on Poliak and Jonas model  \cite{najafizadeh2006predicting}.}\vspace{-5mm}
-\begin{center}
+%\centering
+\caption{Critical conditions based on Poliak and Jonas model  \cite{najafizadeh2006predicting}.}\vspace{-1mm}
 \begin{tabular}{cccccc}
@@
 
-& $1050$ & $0.700$ & $127.172$&$0.577$ /&$116.1$ / \\ 
-& $1100$ & $0.700$ & $106.608$& $0.329$/& $94.51$/ \\
-$1$      & $1150$  & $0.700$  & $89.525$& $0.668$ & $89.067$ \\
+& $1050$ & $0.700$ & $127.172$&$0.577$  &$116.1$  \\ 
+& $1100$ & $0.700$ & $106.608$& $0.329$ & $94.51$ \\
+$1$      & $1150$  & $0.700$  & $89.525$& $0.268$ & $89.067$ \\
 & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$ \\
@@
 \end{tabular}	
-\end{center}
 \label{tab:OPparams}
@@
 Firstly, it entails determining the coefficients $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$.
-Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).To compute these parameters, a Python code using the $curve\_fitting$ method is used.
+Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
+To compute these parameters, a Python code using the $curve\_fitting$ method is used.
 Specifically, the critical strains and stresses calculated in the previous sections are used as input data for these parameter identifications.
@@
 \caption{JMAK model and Zener-Hollomon dependency parameters }\vspace{-1mm}
-\begin{tabular}{cc}
+\begin{tabular}{cccccc}
 \toprule
-Parameters & Values  \\
+$A_c$ & $A_p$& $B_c$&  $B_p$& $B_s$& $n_c$ \\
 \hline
-$A_c$&$4.4268\times10^{-5}	$\\
-$A_p$&$29.85\times10^{-5}$\\
-$B_c$&$0.0720627$\\
-$B_p$&$0.103141	$\\
-$B_s$&$10265.8	$\\
-$n_c$&$0.235832	$\\
-$n_p$&$0.203678	$\\
-$m_c$&$0.188236	$\\
-$m_p$&$0.181822	$\\
-$m_s$&$-0.19708	$\\
-$k$  &$0.48632	$\\
-$n_k$&$3.36531$ \\
+$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141	$&$10265.8	$&$0.235832	$\\
+\toprule
+$n_p$ & $m_c$& $m_p$&  $m_s$& $k$& $n_k$ \\
+\hline
+$0.203678	$& $0.188236$&$0.181822$&$-0.19708$&$0.48632$&$3.36531$\\
 \bottomrule
@@
 In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed.
-To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of this particular material.
-In our prior publication, a comparison between analytical constitutive laws and neural network-based approaches was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
-As a result, this section comprises a two-fold focus: firstly, a recapitulation of the constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
+To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of the material.
+In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approache was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
+As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
 %----------------------------------------------------------------------------------
@@
 %\centering
-\includegraphics[width=0.7\columnwidth]{Figures/ANN-scheme-2HL}
+\includegraphics[width=0.55\columnwidth]{Figures/ANN-scheme-2HL}
 \caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
@@
 \begin{tabularx}{\textwidth}{LCCCCCC}
-\hline
+\toprule
 \textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
@@
 $N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
-\hline
+\toprule
 $\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
@@
 $\RMSE(\MPa)$ & $0.59$ & $0.57$ & $0.65$ & $0.55$ & $0.46$ & $0.38$ \\
-\hline
+\bottomrule
 \end{tabularx}
@@
 %----------------------------------------------------------------------------------
-\subsection{DRX simulation\label{subsec:DRXSimulation}}
-In order to assess the effectiveness of the implementation of the model presented in the previous sections, a compression test is simulated in this section.
+\subsection{Dynamic recrystallization simulation\label{subsec:DRXSimulation}}
+%----------------------------------------------------------------------------------
+In order to assess the effectiveness of the implementation of the DRX model presented in the previous sections, a compression test is simulated in this section.
 For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model.
@@
 The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
-The FEM model is simulated using Abaqus/Implicit due to the computation time caused by the low strain rates.
+The FEM model is simulated using Abaqus/Implicit due to the computation time related to the low strain rates.
 A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen.
@@
 The lower part of the cylinder remains fixed during the simulation.
-The effect of reducing the cylinder in combination with strain rate or temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
+The effect of reducing the cylinder in combination with strain rate and temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
 For this simulation, three temperatures ($1050^\circ$C, $1150^\circ$C, and $1250^\circ$C) and four strain rates ($0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$ and $1.0~\text{s}^{-1}$) are considered.
@@
 %----------------------------------------------------------------------------------
-\subsubsection{Temperature effect on DRX distribution\label{subsec:TempEffect}}
+\subsubsection{Temperature and strain rate effects \label{subsec:TempSReffect}}
 %----------------------------------------------------------------------------------
+
+Temperature and strain rate play a crucial role in influencing dynamic recrystallization in materials, particularly for metals and alloys in the sense that they lead to the formation of new grains within the material.
+Indeed, higher temperature and low strain rate generally lead to increased nucleation rates and faster growth rates of new grains during dynamic recrystallization while in opposite lower temperature and higher strain rate lead to imcomplete dynamic recrystallization.
+At elevated temperatures, the mobility of atoms and dislocations is enhanced, allowing for the creation of new grain boundaries and the growth of new grains.
+This results in a finer and more equiaxed grain structure.
+Also, higher temperatures can lead to a higher fraction of recrystallized material because the enhanced mobility of dislocations promotes the formation of new grains.
+This can result in a significant change in the microstructure and mechanical properties of the material.
+Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} illustrate the simulated results of the DRX fraction of P20 steel under varying deformation conditions.
+Figure \ref{fig:TempEffect} illustrates that as the temperature rises, the scope of dynamic recrystallization expands.
+The gradual rise in the dynamic recrystallization fraction within the center is evident, spreading outward.
+This expansion is attributed to heightened thermal activation and increased atomic diffusion at elevated temperatures, rendering the material more susceptible to dynamic recrystallization.
+The $X_{drx}$ clearly increases with increasing temperature and reduction.
+At $45\%$ and $60\%$ reduction, the $X_{drx}$ of P20 steel
+reached $100\%$ in the central part of the specimen for all the initial sample temperatures.
+Indeed, the plastic deformation of a material is accompanied by the creation of dislocations.
+These dislocations represent a "store of elastic energy".
+When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganisation of the crystal structure, in two stages: restoration and recrystallisation.
+The nature of the phases does not change (those that are thermodynamically stable), the atoms keep the same lattice, but the grain boundaries and the orientation of the crystallites change.
+
 \begin{figure}[H]
@@
 \end{figure}
-%----------------------------------------------------------------------------------
-\subsubsection{Strain rate effect on DRX distribution\label{subsec:SRatEffect}}
-%----------------------------------------------------------------------------------
 \begin{figure}[H]
@@
 \end{figure}
+
+The temperature at which these phenomena occur depends on the rate of deformation: the more a material is deformed, the more elastic energy it 'stores', so the earlier (at a lower temperature) restoration and recrystallisation will begin.
+According to Figure \ref{fig:SREffect}, the magnitude of dynamic recrystallization diminishes with escalated strain rates, leading to a reduction in the extent of recrystallization.
+This outcome is attributed to the accelerated pace of deformation at higher strain rates, elevating the critical strain and lowering the likelihood of internal dynamic recrystallization within the material.
+
+%----------------------------------------------------------------------------------
+\subsubsection{Experimental validation \label{subsec:ExpValid}}
+%----------------------------------------------------------------------------------
+In this section, a comparison beteween experimental and simulation will be carried out.
+Indeed, the percentage of dynamic recrystallization of selected regions is observed and then compared to the simulation.
+The Figure \ref{fig:expNumDRX} presents a comparison between experimental data and simulation for a test conducted at a temperature of $1150^\circ$C with a deformation strain rate $0.01~\text{s}^{-1}$.
+Five zones have been selected to observe the percentage of recrystallization, which varies between $5\%$ and $100\%$.
+In fact, $5\%$ corresponds to the value associated with the dead zone; which is the contact between the sample and die exposed to friction effects.
+On the other hand, $100\%$ corresponds to the value observed at the center of the sample, where deformation is higher.
+In the center of the sample, the temperature is high, leading to a significant accumulation of energy.
+Conversely, at the edges of the sample, a relatively complete recrystallization is observed because the temperature during deformation migrates from the center towards the outer regions of the piece, enabling recrystallization to take place.
+Microscopic observations corresponding to each zone reveal large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, whereas small grains (Figure \ref{fig:expNumDRX} (a)) are observed at the center of the sample, resulting from complete recrystallization.
+\begin{figure}[H]
+%\centering
+\includegraphics[width=0.98\columnwidth]{Figures/expNumDRX}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150^\circ$C and strain rate $\mdot{\varepsilon}=0.01~\text{s}^{-1}$.}
+\label{fig:expNumDRX}
+\end{figure}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
+In this study, we have harnessed the capabilities of ANN technique to gain a profound understanding of the dynamic recrystallization process and its evolution under varying conditions.
+The integration of ANN modeling, fundamental material models, simulation software, and experimental validation has led to a comprehensive framework that contributes significantly to the field of materials science and engineering.
+Initially, we successfully employed a ANN model to fit flow stress curves, enabling the prediction of critical conditions using the Poliak model.
+Doing this has allowed us to accurately anticipate the conditions at which the DRX process initiates, providing an invaluable tool for anticipating material behavior under specific deformation scenarios.
+
+We harnessed the predicted critical conditions to feed into the JMAK model and by doing so, we achieved the prediction of the DRX volumic fraction, thereby offering insights into the kinetics and mechanisms governing recrystallization.
+This integration bridges the gap between theoretical models and real-world phenomena, offering a deeper understanding of the intricate processes taking place during deformation.
+Taking our investigation further, we have seamlessly integrated the JMAK model into the ABAQUS software, a widely-utilized platform for simulation and analysis.
+Through this integration, we were able to simulate the evolution of DRX during hot compression tests, capturing the process's response to varying conditions.
+By comparing our simulation results with experimental data and employing microstructure analysis, we validated the accuracy of our simulations and affirmed the efficacy of our predictive models.
+
+It is important to note that while our research marks a significant milestone, it also presents opportunities for future exploration.
+Fine-tuning our model, expanding our dataset, and refining the integration process can further enhance the accuracy and applicability of our predictions.
+Moreover, the successful linkage of theory, simulation, and experimentation provides a robust framework for tackling complex material behavior challenges in industries spanning from manufacturing to aerospace.
 

### 2023-08-24 Article.tex
Split paragraphs
Update abstract and title page

@@
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
-\newcommand{\orcidauthorC}{0000-0002-5360-5121}% Add \orcidB{} behind the
-%author's name
+\newcommand{\orcidauthorA}{0000-0001-7367-5453}
+\newcommand{\orcidauthorB}{0000-0002-1522-2787}
+\newcommand{\orcidauthorC}{0000-0002-5360-5121}
 \newcommand{\orcidauthorD}{0000-0002-0815-1984}
@@
 % Contact information of the corresponding author
-\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}
+\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562442933}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{This study presents a novel and comprehensive approach for understanding and simulating the dynamic recrystallization (DRX) process during hot compression.
-To achieve this, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800 and ANN based flow behaviour law was used to model the plastic behaviour.
-The accuracy of the DRX volumic fraction, both during its identification using analytical models and its numerical implementation in finite element software, relies on critical conditions and therfore, in this study, an artificial neural network, as a universal approximator, is proposed to fit the necessary data for calculating the critical conditions of DRX.
-The JMAK model was used as an analytical model to calculate the volumic fraction of DRX, and its validation against experimental data was successful.
-A numerical implementation of the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model was implemented into ABAQUS software, and the obtained results were compared with experimental data through microstructure analysis, revealing a strong correlation between simulation and experimentation.
-Temperature, strain rate and the amount of deformation effects on DRX evoultion were also investigated in this study and it was observed that the DRX rises with temperature and deformation while it decreases with the increase of strain rates.
-}
+\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process while hot-compressing steel.
+To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
+We also employed an artificial neural network (ANN) to model thermo-visco-plastic behavior with a flow law.
+The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
+This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations.
+The Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
+A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
+The comparison revealed a strong correlation between simulation and experiment.
+The study investigated the impact of temperature, deformation magnitude, and strain rate on DRX evolution.
+The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}
 
@@
 % Only for the journal Applied Sciences
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work.This section is not mandatory.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.
-
 %----------------------------------------------------------------------------------

### 2023-08-25 Article.tex
Update Introduction

@@
 The comparison revealed a strong correlation between simulation and experiment.
-The study investigated the impact of temperature, deformation magnitude, and strain rate on DRX evolution.
+The study investigated the impact of temperature, strain, and strain rate on DRX evolution.
 The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}
@@
 \begin{document}
+
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-Dynamic recrystallization (DRX) is a process that occurs in certain materials, especially in metals and alloys, when they undergo plastic deformation (deformation that is not reversible).
-It is a phenomenon commonly observed during hot working processes like hot rolling, hot forging, or hot extrusion.
-When a metal or alloy is subjected to high temperatures and significant plastic deformation, the existing grain structure is broken down, and new, smaller grains form in its place and this phenomenon is called DRX.
-It is different from static recrystallization, which occurs at lower temperatures and takes longer to form new grains.
-The process of DRX is driven by the energy stored in the metal due to plastic deformation.
-As the metal deforms, the internal energy increases, and at elevated temperatures, atoms have sufficient mobility to rearrange themselves, leading to the formation of new, strain-free, equiaxed grains.
-These newly formed grains are usually much smaller than the original grains, and their growth is accelerated by the presence of high stored energy and the high temperatures.
-DRX offers several advantages during hot working processes in the sense that it helps in refining the grain size, which enhances the mechanical properties of the material, such as strength and toughness.
-Additionally, it reduces the overall strain energy, which can lead to a more uniform microstructure and improved material properties.
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible plastic deformation.
+It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
+When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
+During this deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
+DRX differs from static recrystallization (SRX), which takes longer to form new grains and occurs at lower temperatures.
+The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
+As the metal deforms, internal energy increases.
+At high temperatures, metal atoms have enough mobility to rearrange themselves, forming new equiaxed grains free of strain.
+Typically, these newly formed grains are much smaller than the original grains of the undeformed material.
+Their growth is accelerated by the stored energy and high temperatures.
+DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness.
+Additionally, it decreases the total strain energy, resulting in a more uniform microstructure and better material properties.
 
-It is well known that during hot deformation with a relatively high strain rate, the dislocation density increases while dynamic recovery (DRC) tries to diminish the density.
-If the rate of dislocation density increase is greater than can be accommodated by DRC, DRX is initiated at a certain point.
-This applies particularly to low and medium stacking fault energy for fcc metals.
-Therefore, mastery of critical conditions for DRX is of considerable interest for the modeling of industrial processes but the extent of DRX depends on several factors, including the material's composition, deformation temperature, strain rate, and the degree of deformation.
-It is an essential phenomenon to be taken into account and controlled in industrial processes where hot working is employed to shape metals and alloys into various products.
-By optimizing the parameters, engineers can achieve desired microstructures and mechanical properties in the final product.
-Several researchers have proposed various techniques to determine DRX's critical conditions such as metallography.
-However, this technique requires extensive sampling before and after the critical deformation.
-Additionally, phase changes during cooling from the hot working temperature alter the deformed structure, making metallographic analysis challenging.
-Hence, there is a need to resort to other simpler techniques, such as the development of analytical models.
-In this context, several studies have been conducted to analytically determine the initiation of DRX.
-For example, Barnett \eal \cite{barnett2000predicting} have identified the critical strain for initiation of DRX using the kinetics of static recrystallization (SRX) modified to allow SRX to begin before the end of deformation.
-This approach defines the critical stress for the initiation of SRX during deformation.
-On the basis of a dislocation density work hardening model, Gottstein \eal \cite{gottstein2004prediction} have also predicted the critical strain for initiation of DRX.
-The onset of DRX can also be identified phenomenologically from the inflection point in the strain hardening rate $\theta=\frac{\partial \sigma}{\partial \varepsilon} = f(\sigma)$ whose understanding is crucial in materials processing and design..
+During high-rate hot deformation, dislocation density typically rises while a dynamic recovery (DRC) helps to mitigate such increases.
+DRX occurs when the dislocation density rises to an extent beyond the DRC’s accommodation.
+This is especially true for low and medium stacking fault energies \OP{what is it?} in fcc metals.\OPP{can you explain what you mean?}
+Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
+However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and degree of deformation.
+DRX is a crucial phenomenon that must be considered and controlled in industrial processes that use hot working to shape metals and alloys into products.
+By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
+Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography.
+However, this technique demands abundant sampling prior to and after the critical deformation.
+Additionally, the cooling phase entails phase changes from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
+In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
+For instance, Barnett \eal \cite{barnett2000predicting} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
+This approach defines the critical stress required for the initiation of SRX during deformation.
+According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
+The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
+This understanding is crucial for materials processing and design purposes.
 
-The DRX phenomenon based on inflection point was first studied by Ryan and McQueen \cite{ryan1989dynamic,ryan1990dynamic,ryan1990flow}, who observed the appearance of an inflection point on the curve $\theta=f(\sigma)$ before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this inflection point.
-Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} further demonstrated that this inflection point is associated with the thermodynamic energy released during the movement of dislocations, thus confirming the hypothesis of DRX describing this inflection point; this signifies that an additional softening mechanism begins to operate (in addition to DRC).
-Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used nowadays, to determine the critical conditions for the initiation of DRX.
-In their approach, they adopted a third-degree polynomial to describe the shape of the curve $\theta=f(\sigma)$ and, by using the second derivative, they identified the critical strain $\varepsilon_c$ and stress $\sigma_c$.
-Once the critical conditions are calculated, they are considered as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}, which is widely used to estimate the volumic fraction of DRX ($X_{drx}$) during hot working.
-Li \eal \cite{li2015experimental} explored the DRX characteristics of micro-alloyed plastic molding steel, using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to identify all key parameters.
-Zhang \eal \cite{zhang2016kinetics} studied the DRX behaviors of medium carbon CreNieMo steel alloy using the Avrami kinetics model equation, and qualitatively characterized the metallurgical properties as a function of the Zener-Hollomon parameter.
-Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} predicted the microstructural evolution of Mn alloy (with an emphasis on the DRX and grain growth phenomena) using this well-known model and found that the predicted microstructures were consistent with those revealed by multiple compression tests.
-The same equation was used by Wan \eal \cite{wan2017experimental} to predict the microstructural evolution of TiAl-based alloys during hot compression.
-Li \eal \cite{li2018finite} verified the reliability of the Avrami kinetics model equation during compression testing of Inconel 718 bolts.
-Cui \eal \cite{cui2016hot} investigated DRX using the Avrami kinetics model equation and showed that the evolution of a $\beta$-solidifying TiAl alloy commonly began at triangular boundaries and only later affected the lamellae.
-Recently, Chen \eal \cite{chen2023finite} performed Finite Element Analysis of DRX based on GCr15 microstruture analysis and observed that temperature, strain rate have important effect on the DRX initiation.
+The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
+They observed the appearance of an inflection point on the $\theta=f(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta=f(\sigma)$} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
+Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements.
+This indicates the onset of an additional softening mechanism, in addition to DRC.
+Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
+Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta=f(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
+Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
+This model is commonly utilized to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
+Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by utilizing the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine essential parameters.
 
-The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained.
-Indeed, the direct use of raw data from experiments does not provide usable curves.
-Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it.
-The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$.
-However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior.
-Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX.
-In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data.
-By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.
+Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (CreNieMo steel) using the Avrami kinetics model equation.
+They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
+Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of Mn alloy, with a focus on DRX and grain growth phenomena.
+Their results showed consistency with multiple compression tests.
+Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructural evolution of TiAl-based alloys during hot compression.
+Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
+Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triangular boundaries before affecting the lamellae.
+Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
+
+The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta=f(\sigma)$.
+Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma=f(\varepsilon)$ \OP{I suggest the following writing: $\sigma(\varepsilon)$ instead of $\sigma=f(\varepsilon)$} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta=f(\sigma)$ curve from it is commonly used.
+The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma=f(\varepsilon)$.
+Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials.
+Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
+In other words, the proposed method suggests utilizing an artificial neural network (ANN) to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
+By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.
+
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
+
 The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
@@
 JC & Johnson--Cook \\
-MZA & Modified-Zerilli--Armstrong \\
+MZA & Modified Zerilli--Armstrong \\
+SRX & Static recrystallization \\
 WH & Work hardening \\

### 2023-08-25 Article.tex
Update Section 2

@@
 %----------------------------------------------------------------------------------
+
 Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible plastic deformation.
@@
 According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
-The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
+The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
 This understanding is crucial for materials processing and design purposes.
@@
 The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
-They observed the appearance of an inflection point on the $\theta=f(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta=f(\sigma)$} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
+They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta=f(\sigma)$} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
 Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements.
@@
 Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
-Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta=f(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
+Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
 Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
@@
 
-The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta=f(\sigma)$.
-Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma=f(\varepsilon)$ \OP{I suggest the following writing: $\sigma(\varepsilon)$ instead of $\sigma=f(\varepsilon)$} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta=f(\sigma)$ curve from it is commonly used.
-The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma=f(\varepsilon)$.
+The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
+Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma(\varepsilon)$ instead of $\sigma=f(\varepsilon)$} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
+The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
 Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials.
@@
 
-The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
-For further information, readers may refer to this other publication by our research group.
-We will, however, list here-after the main points required to understand the proposed approach.
-The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
-At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
-In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
-It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
+The experimental tests used in this work are identical to those previously published by Tize Mha \eal \cite{TizeMha-2023}.
+For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
+Nonetheless, we will outline the key aspects necessary to comprehend the suggested methodology.
+%The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
+%At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
+%In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
+%It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
 
@@
 %----------------------------------------------------------------------------------
-The material used for this study is a medium-carbon steel with the chemical composition shown in Table \ref{tab:Composition}.
+
+The material utilized for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
 \begin{table}[H]
@@
 \end{table}
-Hot compression tests of cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm were carried out on a Gleeble-3800 thermomechanical simulator, for $5$ temperature levels (between $1050\celsius$ and $1250\celsius$), and $6$ strain rates (between $0.001~\ps$ and $5~\ps$).
-The imposed displacement is set to $d=6$~mm, leading to a reduction of $40\%$ of the initial height.
-To minimize friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
-To eliminate thermal gradients, the samples were heated at a rate of $2$\celsius/s to a temperature of $1260\celsius$ and held at that temperature for $5$~min.
-They were then cooled to the test temperature at a rate of $1$\celsius/s and then held at constant temperature for $1$~min prior to forming.
-During compression, the specimen temperature is kept constant by the machine's thermal control system.
-The sample is then rapidly cooled to freeze the microstructure for later analysis.
+Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
+The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
+The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
+To reduce friction during testing, thin tantalum sheets were utilized as a lubricant on the contact surface of the anvils and specimens.
+In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
+They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
+During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
+Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.
 
-The raw stress-strain data are exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of $30$ flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
-All strain/stress data is composed of $701$ equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
+The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
+All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
 \begin{figure}[H]
@@
 
-The flow stress ($\sigma$) increases with increasing strain rate ($\mdot\varepsilon$) but decreases with increasing temperature ($T$).
-It is noteworthy that the flow stress is also influenced by the strain.
-For the lowest strain rates, the flow stress increases up-to $\sigma_p$ with the strain until reaching a value of approximately $\varepsilon_p=0.2$ to $0.3$.
-Subsequently, it decreases to maintain a relatively constant value throughout the test.
-Conversely, for the highest strain rates (above $1~\ps$), the flow stress consistently increases during the entire test duration.
-The slight increase in stress at low strain rates with large strain values is due to friction between the sample and the anvil during testing as reported by Galos \eal \cite{Galos-2022}.
-This frictional effect becomes more pronounced as lubrication decreases over time.
+The flow stress ($\sigma$) increases as the strain rate ($\mdot\varepsilon$) rises but decreases as the temperature ($T$) increases.
+Notably, the strain also affects the flow stress.
+At the lowest strain rates, the flow stress increases up to $\sigma_p$ as the strain approaches a value of about $\varepsilon_p=0.2$ to $0.3$.
+Then, it decreases to maintain a relatively constant value throughout the entire test.
+Conversely, at strain rates above $1~\ps$, the flow stress increases steadily throughout the test.
+The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
+Furthermore, this frictional effect becomes more apparent as lubrication reduces over time.
 
-The initial stress increase observed during deformation up to $\varepsilon=0.1$ is attributed to work hardening (WH).
-Subsequently, from $\varepsilon=0.1$ to $0.2$, the flow stress demonstrates a continuous decline as the stress level increases until a peak or inflection point is reached, indicating the dominant influence of thermal softening surpassing work hardening.
-At this stage, the stress-strain curve exhibits three different patterns as the strain increases: (i) gradual decrease to a steady state with DRV/DRX softening.
-This pattern is observed for all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except for those at $1050\celsius$ and $1100\celsius$; (ii) higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$; (iii) continuous increase with significant work hardening observed for all deformation temperatures and a strain rate of $1~\ps$.
-This suggests that softening due to DRX occurs at high temperatures and low strain rates.
-In contrast, at higher strain rates and lower temperatures, the rate of softening due to DRX is slowed down by higher work hardening rates.
-As a result, both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
-The drop in stress observed at all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is due to the occurrence of DRX.
+The initial increase in stress seen during deformation up to $\varepsilon=0.1$ is believed to be due to work hardening (WH).
+After $\varepsilon=0.1$ up to $0.2$, the flow stress indicates a steady decrease as the stress level rises until a peak or inflection point is attained.
+This peak suggests that thermal softening is now the predominant influence, overtaking work hardening.
+At this stage, the stress-strain curve displays three distinct patterns as strain increases.
+The first pattern is a gradual decrease to a steady state with DRV/DRX softening, which is observed at all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except at $1050\celsius$ and $1100\celsius$.
+The second pattern is higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$.
+The last pattern is a continuous increase with significant work hardening observed for all deformation temperatures and a strain rate above $1~\ps$.
+This indicates that DRX softening happens at high temperatures and low strain rates,
+and the rate of softening due to DRX slows down at higher strain rates and lower temperatures due to higher work hardening rates.
+The result is that both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
+The decrease in stress detected across all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is attributed to the event of dynamic recrystallization (DRX).
 
-DRX is an important phenomenon for controlling the microstructural and mechanical properties of a material during hot working.
-In some materials, such as aluminum, DRX can balance work hardening, resulting in the rapid appearance of a plateau.
-However, in many austenitic steels, the kinetics of restoration are weak and, as a result, DRX can be triggered at a critical condition of strain accumulation.
-Because of the significant influence of DRX on the material's flow stress at high temperature, this inevitably affects the material's microstructure after hot working, and prediction of the critical conditions for the onset of DRX is therefore crucial to good material characterization.
-Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation and the deformation parameters (deformation rate, temperature and deformation) condition DRX, which can only be triggered if the critical deformation is reached, and this deformation can be determined using metallography.
-However, this technique requires extensive sampling before and after critical deformation.
-In addition, phase changes during cooling from the hot working temperature modify the deformed structure, making metallographic analysis difficult.
-Hence the need for simpler techniques, such as the development of analytical models.
-With this in mind, a number of studies have been carried out to determine analytically the initiation of DRX.
+Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
+In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
+However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
+Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
+Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
+Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the deformation parameters (deformation rate, temperature, and deformation) condition dynamic recrystallization (DRX), which can only be triggered once the critical deformation is reached and can be determined via metallography.
+However, this technique necessitates extensive sampling pre- and post-critical deformation.
+In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis.
+Hence simpler techniques, like developing analytical models have been implemented.
+Several studies analyzing the initiation of DRX have been conducted with this objective in mind.
 
-In this paper we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to compute the evolution of DRX of the material during the deformation.
-The raw data acquired from the Gleeble thermosimulator will subsequently be used to identify the material flow law and the parameters of the DRX model.
-The parameters of JMAK model are obtained through a two-step process.
-Firstly, the critical stresses and strains are determined, where the ANN model is utilized to obtain well-filtered curves.
-Secondly, these critical values are employed as input data for the calculation of parameters in the JMAK model, aiming to predict the volume fraction of dynamic recrystallization.
+In this paper, we will utilize the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
+The information obtained from the Gleeble thermosimulator will be utilized to identify the material flow law and the parameters of the DRX model.
+We obtain the parameters of the JMAK model through a two-step process.
+First, critical stresses and strains are determined using the ANN model to filter curves effectively.
+Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of forecasting the volume fraction of dynamic recrystallization.
 
@@
 
-In this Section we will determine the critical deformation required to initiate recrystallization.
-Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the first to study this phenomenon, observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$ and attributed to this inflection point the start of DRX and therefore the critical values $\varepsilon_c$ and $\sigma_c$ of the strain and the stress respectively.
-Later Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} further demonstrated that this inflection point is associated with a thermodynamic free energy released during dislocation motion, and consequently endorse the DRX hypothesis describing this inflection point.
-Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified the thermodynamic model of Poliak and Jonas by developing an analytical technique, widely used today, to determine the critical conditions for the initiation of DRX.
-In their approach, a polynomial of $3^\text{th}$ degree is adopted to describe the shape of the curve $\theta(\sigma)$ and, using the second derivative, they manage to identify the critical stress and strain ($\sigma_c$ and $\varepsilon_c$).
+In this subsection we will determine the critical deformation required to initiate recrystallization.
+Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
+Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
+Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
+Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
+Their widely-used approach adopts a $3^\text{rd}$ degree polynomial to describe the curve $\theta(\sigma)$, enabling the identification of critical stress and strain ($\sigma_c$ and $\varepsilon_c$) through the second derivative.
 
-As introduced earlier, the determination of critical values for the initiation of DRX involves determining the inflection point located on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
-One of the first difficulties is to numerically evaluate the value of the derivative of stress versus strain, since experimental data from compression tests show oscillations, as illustrated in Figure \ref{fig:RawData}.
-It is therefore not possible to calculate the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.
+As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
+One challenge is calculating the derivative of stress versus strain values numerically, as compression test data exhibits oscillations, as depicted in Figure \ref{fig:RawData}.
+It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.
 
-To get around this problem, some authors recommend smoothing the experimental data (using the Excel solver for example \cite{Najafizadeh-2006}) or identifying an analytical form (e.g.
-a polynomial of relatively high order) using a minimization algorithm.
-But, depending on the degree of the polynomial and for the same stress/strain curve, several solutions can be obtained, leading to the definition of several possible forms for the $\theta(\sigma)$ function.
+To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver \cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
+But, depending on the degree of the polynomial and for the same stress/strain curve, multiple solutions may be obtained.
+This results in multiple possible forms for the $\theta(\sigma)$ function.
 
@@
 %----------------------------------------------------------------------------------
-In order to improve the results obtained from the critical value identification procedure, we propose here to use the universal approximator capability of artificial neural networks to replace each strain-hardening curve by its representation in the form of an ANN with 1 input (strain) and 1 output (stress).
-In such a network, each layer of neurons is connected to the one before it and the one after it by weighted connections.
+
+To enhance the outcomes attained from the critical value identification process, we suggest employing the universal approximator capability of artificial neural networks.
+This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
 Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
@@
 
-No activation function was used for the output neuron of the ANN as usually done in a regression application.
-The architecture chosen for our application corresponds to 2 hidden layers of 7 and 5 neurons respectively, as illustrated in Figure \ref{fig:ANN-7-5}.
-If $n$ and $m$ are the number of neurons of the first and second hidden layers respectively, the number of internal parameters $N_{int}$ of the model is given by $N_{int}=m(2+n)+2n+1$.
+No activation function was used for the output neuron of the ANN, as is typically omitted in regression applications.
+The chosen architecture for our application consists of two hidden layers, one with 7 neurons and the other with 5 neurons, as illustrated in Figure \ref{fig:ANN-7-5}.
+To calculate the number of internal parameters $N_{int}$ in the model, where $n$ and $m$ represent the number of neurons in the first and second hidden layers, respectively, the following formula may be used: $N_{int}=m(2+n)+2n+1$.
 So that for a $7-5$ network, $N_{int}=60$.
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
@@
 \end{figure}
-The Python program used for training the neural network was developed using the specialized Python library, Tensorflow \cite{Abadi-2016}.
-The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
+The Python program utilized for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
+The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.
 
@@
 %----------------------------------------------------------------------------------
-Since the DRX occurs only for the 4 strain rates within the range $[0.001~\ps-1.0~\ps]$, we will only use the first 20 stress/strain curves for the DRX critical parameters' identification.
-Each of the 20 curves, made up of 701 couples of strain-stress values, was processed independently by a neural network, leading to 20 identified architectures.
-As an example, Figure \ref{fig:AnnFit} shows the experimental values of the stress/strain curve for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (blue line) and the results from the neural network identified from these data (red line).
+
+Since the dynamic recrystallization phenomenon only occurs for strain rates between $0.001~\ps$ and $1.0~\ps$, we will use only the first 20 stress/strain curves to identify the DRX critical parameters.
+Each of these 20 curves consists of 701 pairs of strain-stress values and was independently processed by a neural network, resulting in the identification of 20 networks.
+As an example, Figure \ref{fig:AnnFit} displays the stress/strain curve experimental values for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (in blue) and the neural network results identified from this data (in red).
+
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
-\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\caption{Filtering of the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
 \label{fig:AnnFit}
 \end{figure}
-The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the mean absolute relative error ($\MARE$) defined by Equation (\ref{eq:AARE}):
+The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by Equation (\ref{eq:AARE}):
 \begin{equation}
@@
 
-It can clearly be observed that using the ANN model to describe the $\sigma=f(\varepsilon)$ curve is better than using a $11^{th}$ order polynomial fit, as evidenced by the lower estimated error.
-Therefore, this architecture of the ANN model is employed for the remaining curves, leading directly to deduce the hardening $\theta=f(\sigma)$ curves, which represent the rate of change of stress with respect to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
-An example of computing the hardening curve for one temperature is given on Figure \ref{fig:AnnTheta} and for remaining temperatures, Figure \ref{fig:nThetaOP} can give an overview.
-The same procedure is used for the four initial strain rates.
-These curves provide essential information about critical stresses and strains needed for predicting DRX in the subsequent analysis.
+It is evident that utilizing the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
+Thus, this architecture of the ANN model is utilized for all subsequent curves, resulting in the deduction of the hardening $\theta(\sigma)$ curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
+An example of calculating the hardening curve for a single temperature is presented in Figure \ref{fig:AnnTheta}, while an overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
+\OP{Have to improve this later.}
+The identical process applies to all 20 stress/strain curves.
+These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.
 
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{An example of computing hardening curve based on ANN model.}
+\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed}}
 \label{fig:AnnTheta}
@@
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
-\caption{Work hardening computation for $1$ strain rate and $5$ temperatures.}
+\caption{Work hardening computation for $1$ strain rate and $5$ temperatures. \OP{Im' not sure that this caption is related to the current figure.}}
 \label{fig:nThetaOP}
@@
 %----------------------------------------------------------------------------------
-As mentioned in the previous section, dynamic recrystallization initiates if and only if a certain critical condition level is reached.
-Determining these critical conditions remains challenging, as it requires the development of models capable of calculating the corresponding critical stress and strain.
-Thus, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, widely recognized today, will be employed in this study.
-The method involves using a third-degree polynomial function to describe the functions $\theta(\sigma)$ and $\ln \theta(\varepsilon)$curves as shown in Figure \ref{fig:fThetaOP} , with the purpose of identifying the inflection points corresponding to critical stress $\sigma_c$ and critical strain $\varepsilon_c$.
-Also from those curves, peak stress $\sigma_p$ and peak strain $\varepsilon_p$ can be deduced.
-The Poliak and Jonas model \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} is given as follow:
+
+As described previously, dynamic recrystallization only occurs when a particular critical condition is met.
+The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
+Consequently, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, which is currently well-regarded, will be utilized in this investigation.
+The method utilizes a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
+The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those curves.
+
+The determination of critical values is carried out in two consecutive steps for each of the curves.
+Firstly, based on the definition of the $\theta(\sigma)$ curve as depicted in Figure \ref{fig:nThetaOP}, we utilize the polyfit method from the numpy library to determine the optimal values of the constants $a_i$ for a third-degree polynomial function $p(\sigma)$ approximating $\theta(\sigma)$:
 \begin{equation}
-\theta = A\sigma^3 + B\sigma^2 + C\sigma + D
+p(\sigma) = a_0\sigma^3 + a_1\sigma^2 + a_2\sigma + a_3
 \end{equation}
-Where $A, B, C,$ and $D$ are constants specific to a given deformation condition.
-The inflection point of a function is determined by setting the second derivative of that function to zero and the following equation is obtained:
+Secondly, the inflection point $\sigma_c$ can be obtained from the second derivative of $p(\sigma)$ with:
 \begin{equation}
-\frac{d^2 \theta}{d \sigma^2} = 6A\sigma + 2B
+\frac{d^2 p(\sigma)}{d \sigma^2} = 0 \Longrightarrow \sigma_c = -a_1/3a_0
 \end{equation}
-Therefore, the critical stress for the initiation of DRX is obtained as follows:
+Similarly, the critical strain ($\varepsilon_c$) is calculated by defining a third-degree polynomial function $q(\sigma)$ approximating the $\ln \theta(\varepsilon)$ curve as depicted in Figure \ref{fig:nThetaOP}:
 \begin{equation}
-6A\sigma_c + 2B = 0 \Longrightarrow \sigma_c = -B/3A
+q(\varepsilon) = b_0\varepsilon^3 + b_1\varepsilon^2 + b_2\varepsilon + b_3
 \end{equation}
-Similarly, the critical strain is calculated using the following equations:
-\begin{equation}
-\ln \theta = A_1\varepsilon^3 + B_1\varepsilon^2 + C_1\varepsilon + D_1
-\end{equation}
-\begin{equation}
-\frac{d^2 \ln \theta}{d \varepsilon^2} = 6\varepsilon A_1 + 2B_1 ~~\text{and} ~~\frac{d^2 \ln \theta}{d \varepsilon^2}= 0 \Longrightarrow \varepsilon_c = -B_1/3A_1
-\end{equation}
-Applying the same method to the first four strain rates and all temperatures, the critical stress and strain, peak stress and peak strain are summarised in the Table \ref{tab:OPparams}.
-Once the critical conditions of the DRX are known, therefore they can be used as input to deduce the volume fraction of the DRX, which will be the subject of the next section.
-\begin{figure}[H]
+This later gives the critical strain $\varepsilon_c$ from $\varepsilon_c = -b_1/3b_0$.
+Applying the identical method to the first four strain rates and all temperatures, Table \ref{tab:OPparams} summarizes the critical stress and strain, peak stress, and peak strain.
+Once the critical DRX conditions are established, they can be utilized as input to determine the DRX volume fraction, which will be discussed in the following section.
+
+\OP{Figure 6 has been removed because I think it is useless.}
+%\begin{figure}[H]
 %\centering
-\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
-\caption{Work hardening polynomial fiting based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}
-\label{fig:fThetaOP}
-\end{figure}
-
-\begin{comment}
-\begin{landscape}
-\begin{table}[h]
-\caption{functions $\theta=f(\sigma)$ and $\ln\theta=f(\varepsilon)$ coefficients based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}\vspace{1mm}
-%\begin{center}
-\begin{tabular}{cccc}
-\toprule
-$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C) & $\theta$ = f($\sigma$) & $\ln$$\theta$=f($\varepsilon$)\\
-\hline
-&$1050	$&$ -0.252593\sigma^3 + 23.2834\sigma^2 - 719.045\sigma + 7561.2	 $&$-2274.82\varepsilon^3 + 592.899\varepsilon^2 - 61.0014\varepsilon + 6.71048$\\
-&$1100	$&$ -0.469287\sigma^3 + 35.0169\sigma^2 - 875.042\sigma + 7418.89	 $&$-4813.49\varepsilon^3 + 1020.98\varepsilon^2 - 79.8778\varepsilon + 6.65741$\\
-$0.001	$&$1150	$&$ -0.280343\sigma^3 + 15.2183\sigma^2 - 287.655\sigma + 2008.9	 $&$-899.654\varepsilon^3 + 15.7144\varepsilon^2 - 17.0976\varepsilon + 5.59789$\\
-&$1200	$&$ -0.165122\sigma^3 + 7.34045\sigma^2 - 127.854\sigma + 949.691	 $&$10803.3\varepsilon^3 - 1567.6\varepsilon^2 + 31.5185\varepsilon + 4.92891$\\
-&$1250	$&$ 0.430135\sigma^3 - 13.9807\sigma^2 + 123.725\sigma - 137.032 	 $&$-9130.5\varepsilon^3 + 1125.18\varepsilon^2 - 69.4152\varepsilon + 5.34578$\\
-%\hline
-&$1050	$&$ -0.316563\sigma^3 + 41.6041\sigma^2 - 1780.61\sigma + 24890.6	 $&$-760.548\varepsilon^3 + 302.444\varepsilon^2 - 47.4264\varepsilon + 6.96767$\\
-&$1100	$&$-0.254362\sigma^3 + 27.7695\sigma^2 - 1002.47\sigma + 12089.1  $&$-957.925\varepsilon^3 + 326.362\varepsilon^2 - 48.1866\varepsilon + 6.78809$\\
-$0.01	$&$1150	$&$ -0.125197\sigma^3 + 11.765\sigma^2 - 378.088\sigma + 4266.7$&$-1904.84\varepsilon^3 + 452.618\varepsilon^2 - 46.9027\varepsilon + 6.35515$\\
-&$1200	$&$ -0.386264\sigma^3 + 28.6922\sigma^2 - 713.252\sigma + 6045.79	 $&$-1260.32\varepsilon^3 + 283.718\varepsilon^2 - 39.3944 \varepsilon + 6.12705$\\
-&$1250	$&$ -0.274371\sigma^3 + 15.2491\sigma^2 - 291.928\sigma + 2051.22	 $&$2054.13\varepsilon^3 - 545.571\varepsilon^2 + 11.6535\varepsilon + 5.15417$\\
-%\hline
-&$1050	$&$ -0.109041\sigma^3 + 22.8574\sigma^2 - 1554.51\sigma + 34276.6	 $&$22.5257\varepsilon^3 - 10.6333\varepsilon^2 - 10.5919\varepsilon + 6.15546$\\
-&$1100	$&$ -0.197437\sigma^3 + 32.5449\sigma^2 - 1740.23\sigma + 30179.2	 $&$-119.588\varepsilon^3 + 98.0419\varepsilon^2 - 32.5318\varepsilon + 6.75459$\\
-$0.1	$&$1150	$&$ -0.273236\sigma^3 + 36.2143\sigma^2 - 1566.6\sigma + 22180.5	 $&$-245.608\varepsilon^3 + 155.747\varepsilon^2 - 40.2746\varepsilon + 6.76$\\
-&$1200	$&$ -0.263314\sigma^3 + 29.6662\sigma^2 - 1095.93\sigma + 13363.4	 $&$-113.711\varepsilon^3 + 65.8505\varepsilon^2 - 25.9935\varepsilon + 6.30479$\\
-&$1250	$&$ -0.390101\sigma^3 + 36.635\sigma^2 - 1132.85\sigma + 11626.3	 $&$-66.6657\varepsilon^3 + 88.2893\varepsilon^2 - 33.1747\varepsilon + 6.35758$\\
-%\hline
-&$1050	$&$ -0.0746046\sigma^3 + 21.1153\sigma^2 - 1933.09\sigma + 56923.3  $&$ -23.0014\varepsilon^3 + 42.4459\varepsilon^2 - 23.8994\varepsilon + 6.7553$\\
-&$1100	$&$ -0.107164\sigma^3 + 25.6015\sigma^2 - 1978.33\sigma + 49199	 $&$-13.408\varepsilon^3 + 30.6189\varepsilon^2 - 20.0411\varepsilon + 6.3443$\\
-$1	$&$1150	$&$ -0.139902\sigma^3 + 27.9237\sigma^2 - 1799.15\sigma + 37231	 $&$-14.1508\varepsilon^3 + 30.1129\varepsilon^2 - 19.4669\varepsilon + 6.11887$\\
-&$1200	$&$ -0.150668\sigma^3 + 25.0242\sigma^2 - 1351.37\sigma + 23734.1	 $&$ 26.6437\varepsilon^3 - 11.2098\varepsilon^2 - 9.52699\varepsilon + 5.39017$\\
-&$1250	$&$ -0.112709\sigma^3 + 16.0385\sigma^2 - 751.823\sigma + 11702	 $&$ 55.0921\varepsilon^3 - 38.055\varepsilon^2 - 4.07206\varepsilon + 4.95987$\\
-\bottomrule
-\end{tabular}
-%\end{center}
-\label{tab:JJparams1}
-\end{table}
-\end{landscape}
-\end{comment}
+%\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
+%\caption{Work hardening polynomial fiting based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}
+%\label{fig:fThetaOP}
+%\end{figure}
 
 \begin{table}[h!]
-%\centering
-\caption{Critical conditions based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}\vspace{-1mm}
+\centering
+\caption{Critical conditions based on the proposed approach.\OP{Caption changed}}\vspace{-1mm}
 \begin{tabular}{cccccc}
 \toprule
-$\mdot{\varepsilon}~~(\text{s}^{-1})$ & $T$ ($^\circ$C) & $\varepsilon_p$ & $\sigma_p$ (MPa)& $\varepsilon_c$ & $\sigma_c$ (MPa) \\
+$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
 \hline
-     & $1050$ & $0.178$ & $37.862$& $0.083$ & $33.050$ \\
-& $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$ \\
-$0.001$ & $1150$ & $0.124$ & $23.330$& $0.051$ & $19.116$ \\
-& $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$ \\
-& $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$ \\
+ & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
+ & $1100$ & $0.143$ & $29.770$ & $0.067$ & $25.648$\\
+$0.001$ & $1150$ & $0.124$ & $23.330$ & $0.051$ & $19.116$\\
+ & $1200$ & $0.102$ & $19.373$ & $0.039$ & $16.244$\\
+ & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
 
-& $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$ \\
-& $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$ \\
-$0.01$  & $1150$ & $0.195$ & $38.249$& $0.086$ & $33.435$ \\
-& $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$ \\
-& $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$ \\
+ & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
+ & $1100$ & $0.228$ & $46.107$ & $0.108$ & $40.495$\\
+$0.01$ & $1150$ & $0.195$ & $38.249$ & $0.086$ & $33.435$\\
+ & $1200$ & $0.172$ & $30.991$ & $0.076$ & $26.718$\\
+ & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
 
-& $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$ \\
-& $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$ \\
-$0.1$  & $1150$ & $0.344$ & $57.774$& $0.160$ & $51.723$ \\
-& $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$ \\
-& $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$ \\
+ & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
+ & $1100$ & $0.430$ & $72.662$ & $0.194$ & $65.259$\\
+$0.1$ & $1150$ & $0.344$ & $57.774$ & $0.160$ & $51.723$\\
+ & $1200$ & $0.299$ & $48.473$ & $0.136$ & $42.386$\\
+ & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
 
-& $1050$ & $0.700$ & $127.172$&$0.577$ &$116.1$ \\
-& $1100$ & $0.700$ & $106.608$& $0.329$ & $94.51$ \\
-$1$   & $1150$ & $0.700$ & $89.525$& $0.268$ & $89.067$ \\
-& $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$ \\
-& $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$ \\
+ & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
+ & $1100$ & $0.700$ & $106.61$ & $0.329$ & $94.510$\\
+$1$ & $1150$ & $0.700$ & $89.525$ & $0.268$ & $89.067$\\
+ & $1200$ & $0.700$ & $72.270$ & $0.178$ & $57.929$\\
+ & $1250$ & $0.393$ & $59.992$ & $0.112$ & $54.066$\\
 \bottomrule
@@
 %----------------------------------------------------------------------------------
-\subsection{DRX model parameters evaluation\label{subsec:DRXparams}}
+\subsection{DRXmodel parameters evaluation\label{subsec:DRXparams}}
 %----------------------------------------------------------------------------------
-The DRX begins at a critical deformation, as previously mentioned, and the level of recrystallization can be determined experimentally.
-Figure \ref{fig:DRXschema} illustrates three stages of recrystallization: nucleation, grain growth, and grain coalescence.
+
+The DRX process commences at a critical deformation, as previously noted. 
+The degree of recrystallization can be determined through experimental means.
+Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence. \OP{REF ?}
+
 \begin{figure}[!ht]
-%\centering
+\centering
 \includegraphics[width=0.7\columnwidth]{Figures/picDRX}
-\caption[Diagramme des trois étapes de la DRX]{Diagramme des trois étapes de la DRX \cite{wan2017experimental}}
+\caption{Diagramme des trois étapes de la DRX \cite{wan2017experimental}\OP{Is it a copy/paste from a publication? If so, you can't put it as it!}}
 \label{fig:DRXschema}
 \end{figure}
-The subsequent behavior of DRX affects the material's flow stress curve as the rate of work hardening is influenced by dislocations within the free grains.
-The Avrami model is the most commonly used law to predict this behavior, known as the JMAK model, whose expression is given by the following equation estimating the volumic fraction of the DRX:
+The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
+The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \OP{REF?}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
-X_{drx,pred} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
+X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
 \label{eq:drxpred}
@@
 \begin{equation}
-X_{drx,exp} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
+X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
 \label{eq:drxexp}
@@
 
-Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress resectivly.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation:
+Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively. \OP{Please define steady stress after the peak stress}
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \OP{Who wrote this?
+REF?} according to the following equation:
 \begin{equation}
@@
 \end{equation}
-With $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$ the parameters describing the dependency of specific strains and stresses on the Zener-Hollomon parameter where their identification procedure is explained later in this paper.
+With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.
 
-The calculation of the parameters of JMAK model involves two main steps.
-Firstly, it entails determining the coefficients $A_{c,p}, n_{c,p}, B_{c,p,s}$ and $m_{c,p,s}$.
-Secondly, these coefficients are then incorporated into equation (\ref{eq:paramsZ}) for their final use in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
-To compute these parameters, a Python code using the $curve\_fitting$ method is used.
-Specifically, the critical strains and stresses calculated in the previous sections are used as input data for these parameter identifications.
-The curve fitting method aims to find the best-fitting values for the coefficients by iteratively adjusting them to minimize the difference between the predicted and experimental critical strains and stresses.
-This optimization process involves trying various combinations of the coefficients and evaluating their fitness to the given data.
-The curve fitting technique adjusts the coefficients until it achieves the closest match between the model's predictions and the experimental values.
+The JMAK model's parameter identification involves two main steps, starting with determining the 10 coefficients $A$, $n$, $B$, and $m$.
+Secondly, those coefficients are integrated into equation (\ref{eq:paramsZ}) to be utilized in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
+To calculate these parameters, the curve\_fit method of the scipy library is employed through a Python code.
+These parameter identifications use the critical strains and stresses computed in the preceding sections as input data.
+The curve-fitting method seeks to obtain optimal values for the coefficients by iteratively adjusting them to minimize the gap between predicted and actual critical strains and stresses.
+This optimization process entails experimenting with different combinations of coefficients and assessing their appropriateness for the provided data.
+The curve-fitting technique fine-tunes coefficients until it attains the most accurate match between the model's forecasts and the experimental data.
 
-Once the constants that define the Zener-Hollomon parameter dependency are calculated, they can be used to deduce the JMAK model parameters using an optimization technique that minimizes the error between the predicted recrystallization $X_{drx, pred}$ and the experimental value $X_{drx, exp}$.
-The dependency of the Zener-Hollomon parameters and the JMAK model parameters are provided in the Table \ref{tab:allparams}.
+Once the calculation of the constants that define the dependency of the Zener-Hollomon parameter is completed, an optimization technique can be employed to deduce the JMAK model parameters while minimizing the error between the predicted recrystallization $X_{drx}^{p}$ and the experimental value $X_{drx}^{e}$.
+Table \ref{tab:allparams} displays the dependency of both the Zener-Hollomon parameters and the JMAK model parameters.
 
 \begin{table}[h]
-%\centering{}
-\caption{JMAK model and Zener-Hollomon dependency parameters }\vspace{-1mm}
+\centering
+\caption{JMAK model and Zener-Hollomon dependency parameters.}\vspace{-1mm}
 \begin{tabular}{cccccc}
@@
 The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
-From this figure, we can observe that the predictions align well with the experimental data, thus demonstrating the validity of the utilized model.
-Therefore, these results will be used subsequently in the simulation section.
+From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the utilized model. \OP{I don't agree!}
+These results will therefore be used subsequently in the simulation section.
 \begin{figure}[H]
@@
 \includegraphics[width=0.99\columnwidth]{Figures/nDRX}
-\caption{Comparision beteween DRX experimental data and JMAK model based prediction}
+\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???}}
 \label{fig:nDRX}
 \end{figure}
-%\begin{table}[H]
-%\caption{Architecture and accuracy coefficients for all the proposed networks.}
-%\newcolumntype{C}{>{\centering\arraybackslash}X}
-%\newcolumntype{L}{>{\raggedright\arraybackslash}X}
-%\begin{tabularx}{\textwidth}{LCCCCCC}
-%\hline
-%Coefficient & $\mdot\varepsilon$ & $1050\celsius$ & $1100\celsius$ & $1150\celsius$ & $1200\celsius$ & $1250\celsius$ \\
-%\hline
-%$\MARE(\%)$ & $0.001$ & $0.231$ & $1.13$ & $1.05$ & $1.08$ & $0.75$ \\
-%$\RMSE(\MPa)$ & $0.001$ & $0.093$ & $0.59$ & $0.57$ & $0.65$ & $0.46$ \\
-%\hline
-%\end{tabularx}
-%\label{tab:Errors}
-%\end{table}
 
@@
 %----------------------------------------------------------------------------------
+
 In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed.
 To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of the material.
-In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approache was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
-As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behaviour.
+In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approach was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
+As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behavior.
+
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
+
 In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
@@
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.55\columnwidth]{Figures/ANN-scheme-2HL}
@@
 %----------------------------------------------------------------------------------
+
 In order to assess the effectiveness of the implementation of the DRX model presented in the previous sections, a compression test is simulated in this section.
@@
 The effect of reducing the cylinder in combination with strain rate and temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
-For this simulation, three temperatures ($1050^\circ$C, $1150^\circ$C, and $1250^\circ$C) and four strain rates ($0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$ and $1.0~\text{s}^{-1}$) are considered.
+For this simulation, three temperatures ($1050\celsius$, $1150\celsius$, and $1250\celsius$) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$ and $1.0~\ps$) are considered.
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
@@
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.98\columnwidth]{Figures/Temp_DRX}
-\caption{$X_{drx}$ values at a strain rate of $0.01~\text{s}^{-1}$ for different reductions and initial temperatures.}
+\caption{$X_{drx}$ values at a strain rate of $0.01~\ps$ for different reductions and initial temperatures.}
 \label{fig:TempEffect}
@@
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.98\columnwidth]{Figures/SR_DRX}
-\caption{$X_{drx}$ values at a fixed $T_0=1150^\circ$C for different reductions and strain rates.}
+\caption{$X_{drx}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
 \label{fig:SREffect}
@@
 %----------------------------------------------------------------------------------
+
 In this section, a comparison beteween experimental and simulation will be carried out.
 Indeed, the percentage of dynamic recrystallization of selected regions is observed and then compared to the simulation.
-The Figure \ref{fig:expNumDRX} presents a comparison between experimental data and simulation for a test conducted at a temperature of $1150^\circ$C with a deformation strain rate $0.01~\text{s}^{-1}$.
+The Figure \ref{fig:expNumDRX} presents a comparison between experimental data and simulation for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate $0.01~\ps$.
 Five zones have been selected to observe the percentage of recrystallization, which varies between $5\%$ and $100\%$.
@@
 \begin{figure}[H]
-%\centering
+\centering
 \includegraphics[width=0.98\columnwidth]{Figures/expNumDRX}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150^\circ$C and strain rate $\mdot{\varepsilon}=0.01~\text{s}^{-1}$.}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$.}
 \label{fig:expNumDRX}
 \end{figure}
+
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
+
 In this study, we have harnessed the capabilities of ANN technique to gain a profound understanding of the dynamic recrystallization process and its evolution under varying conditions.

### 2023-08-28 Article.tex
new files and article update

@@
 \newcommand{\orcidauthorD}{0000-0002-0815-1984}
+\newcommand{\orcidauthorE}{0009-0004-1420-7552}
 
 % Authors, for the paper (add full first names)
-\Author{Pierre Tize Mha $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
+\Author{Pierre Tize Mha $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$\orcidE{}, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 DRX occurs when the dislocation density rises to an extent beyond the DRC’s accommodation.
-This is especially true for low and medium stacking fault energies \OP{what is it?} in fcc metals.\OPP{can you explain what you mean?}
+This is especially true for low and medium stacking fault energies \OP{what is it?} \textcolor{red}{mettalurgical phenomena that occurs when there is a deviation from the regular arrangement of atoms in a crystal's structure, I explained it more in details in Chapter 1 of my thesis} in fcc metals.\OPP{can you explain what you mean?}\textcolor{red}{These previous sentenses help to understand the DRX's initiation}.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
@@
 The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
-They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta=f(\sigma)$} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
+They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta = f(\sigma)$} \textcolor{red}{Done throughout the paper} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
 Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements.
@@
 Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
-This model is commonly utilized to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
-Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by utilizing the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine essential parameters.
+This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
+Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine essential parameters.
 
@@
 The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
-Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma(\varepsilon)$ instead of $\sigma=f(\varepsilon)$} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
+Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
 The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
@@
 Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
-In other words, the proposed method suggests utilizing an artificial neural network (ANN) to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
+In other words, the proposed method suggests using an artificial neural network (ANN) to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
 By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.
@@
 %At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
-%In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
+%In this new study, the ANN model will be used for predicting dynamic recrystallization, as explained in the introduction.
 %It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
@@
 
-The material utilized for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
+The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
 \begin{table}[H]
@@
 The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
-To reduce friction during testing, thin tantalum sheets were utilized as a lubricant on the contact surface of the anvils and specimens.
+To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
 In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
@@
 
-In this paper, we will utilize the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
-The information obtained from the Gleeble thermosimulator will be utilized to identify the material flow law and the parameters of the DRX model.
+In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
+The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the DRX model.
 We obtain the parameters of the JMAK model through a two-step process.
@@
 \end{figure}
-The Python program utilized for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
+The Python program used for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
 The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.
@@
 
-It is evident that utilizing the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
-Thus, this architecture of the ANN model is utilized for all subsequent curves, resulting in the deduction of the hardening $\theta(\sigma)$ curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
+It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
+Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening $\theta(\sigma)$ curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
 An example of calculating the hardening curve for a single temperature is presented in Figure \ref{fig:AnnTheta}, while an overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
-\OP{Have to improve this later.}
+\OP{Have to improve this later} \textcolor{red}{Okay}.
 The identical process applies to all 20 stress/strain curves.
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed}}
+\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed} \textcolor{red}{Okay}}
 \label{fig:AnnTheta}
@@
 \includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
-\caption{Work hardening computation for $1$ strain rate and $5$ temperatures. \OP{Im' not sure that this caption is related to the current figure.}}
+\caption{Work hardening computation for $1$ strain rate and $5$ temperatures.
+\OP{Im' not sure that this caption is related to the current figure.} \textcolor{red}{As the results provided by Olivier using an ANN model for each curve are not too much far from those obtained using a single ANN model, I've kept just the Figure directly obtained using a single ANN to illustrate the inflection points.
+This is for illustrative purposes only, as the critical values used for the rest of the calculation are those based on one ANN model for each curve}.}
 \label{fig:nThetaOP}
@@
 The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
-Consequently, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, which is currently well-regarded, will be utilized in this investigation.
-The method utilizes a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
+Consequently, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
+The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
 The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those curves.
@@
 The determination of critical values is carried out in two consecutive steps for each of the curves.
-Firstly, based on the definition of the $\theta(\sigma)$ curve as depicted in Figure \ref{fig:nThetaOP}, we utilize the polyfit method from the numpy library to determine the optimal values of the constants $a_i$ for a third-degree polynomial function $p(\sigma)$ approximating $\theta(\sigma)$:
+Firstly, based on the definition of the $\theta(\sigma)$ curve as depicted in Figure \ref{fig:nThetaOP}, we use the polyfit method from the numpy library to determine the optimal values of the constants $a_i$ for a third-degree polynomial function $p(\sigma)$ approximating $\theta(\sigma)$:
 \begin{equation}
@@
 Applying the identical method to the first four strain rates and all temperatures, Table \ref{tab:OPparams} summarizes the critical stress and strain, peak stress, and peak strain.
-Once the critical DRX conditions are established, they can be utilized as input to determine the DRX volume fraction, which will be discussed in the following section.
+Once the critical DRX conditions are established, they can be used as input to determine the DRX volume fraction, which will be discussed in the following section.
 
-\OP{Figure 6 has been removed because I think it is useless.}
+\OP{Figure 6 has been removed because I think it is useless.} \textcolor{red}{Okay}
 %\begin{figure}[H]
@@
 \centering
-\caption{Critical conditions based on the proposed approach.\OP{Caption changed}}\vspace{-1mm}
+\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay}}\vspace{-1mm}
 \begin{tabular}{cccccc}
@@
 The degree of recrystallization can be determined through experimental means.
-Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence. \OP{REF ?}
+Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}. \OP{REF ?} \textcolor{red}{Done}
 
@@
 \includegraphics[width=0.7\columnwidth]{Figures/picDRX}
-\caption{Diagramme des trois étapes de la DRX \cite{wan2017experimental}\OP{Is it a copy/paste from a publication? If so, you can't put it as it!}}
+\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact \cite{wan2017experimental}.
+\OP{Is it a copy/paste from a publication?
+If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned.
+Please, I will appreciate if you could rearrange it as it would have been made.
+Thanks !}}
 \label{fig:DRXschema}
@@
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \OP{REF?}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 
-Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively. \OP{Please define steady stress after the peak stress}
+Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
+\OP{Please define steady stress after the peak stress} \textcolor{red}{The steady stress is considered as the minimum one after the peak stress}
 It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \OP{Who wrote this?
-REF?} according to the following equation:
+REF?} \textcolor{red}{Now references are given before the equation} according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
 \begin{equation}
@@
 The JMAK model's parameter identification involves two main steps, starting with determining the 10 coefficients $A$, $n$, $B$, and $m$.
-Secondly, those coefficients are integrated into equation (\ref{eq:paramsZ}) to be utilized in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
+Secondly, those coefficients are integrated into equation (\ref{eq:paramsZ}) to be used in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
 To calculate these parameters, the curve\_fit method of the scipy library is employed through a Python code.
@@
 The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
-From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the utilized model. \OP{I don't agree!}
+From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the used model.
+\OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension}
 These results will therefore be used subsequently in the simulation section.
@@
 \centering
-\includegraphics[width=0.99\columnwidth]{Figures/nDRX}
-\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???}}
+\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
+\caption{Comparison between DRX experimental data and JMAK model based prediction.
+\OP{I don't see the comparison?
+Is there many superposed curves ???} \textcolor{red}{As I said in my previous mail, I was writing the paper like the experimental data are already provided.
+Everything is okay now, I think !}}
 \label{fig:nDRX}
@@
 \includegraphics[width=0.98\columnwidth]{Figures/expNumDRX}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$.}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \textcolor{red}{to see if I will remplace these pictures by new ones...}}
 \label{fig:expNumDRX}
@@
 This integration bridges the gap between theoretical models and real-world phenomena, offering a deeper understanding of the intricate processes taking place during deformation.
-Taking our investigation further, we have seamlessly integrated the JMAK model into the ABAQUS software, a widely-utilized platform for simulation and analysis.
+Taking our investigation further, we have seamlessly integrated the JMAK model into the ABAQUS software, a widely-used platform for simulation and analysis.
 Through this integration, we were able to simulate the evolution of DRX during hot compression tests, capturing the process's response to varying conditions.
@@
 DRX & Dynamic recrystallization \\
+$X_{drx}^{e,p}$ & DRX's Volume fraction : $e, p$ for experimental and prediction respectively \\
 FEA & Finite element analysis \\

### 2023-08-28 Article.tex
Corrections on Section 3 and conclusions + figures

@@
 Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
-In other words, the proposed method suggests using an artificial neural network (ANN) to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
+In other words, the proposed method suggests using an artificial neural network to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
 By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.
@@
 \begin{tabularx}{\textwidth}{LCCCCCCC}
-\hline
+\toprule
 \textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
-\hline
+\toprule
 \textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
-\hline
+\bottomrule
 \end{tabularx}
@@
 The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.
+The training was conducted using $50,000$ epochs of the experimental dataset.
+It took approximately 15 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor until the converged parameters were obtained.
 
@@
 It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
-Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening $\theta(\sigma)$ curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
-An example of calculating the hardening curve for a single temperature is presented in Figure \ref{fig:AnnTheta}, while an overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
-\OP{Have to improve this later} \textcolor{red}{Okay}.
+Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
+An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure \ref{fig:AnnTheta}.
+The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
+An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay}.
 The identical process applies to all 20 stress/strain curves.
@@
 $\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
-\hline
+\toprule
  & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
@@
  & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
-
+\hline
  & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
@@
  & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
-
+\hline
  & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
@@
  & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
-
+\hline
  & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
@@
 \includegraphics[width=0.7\columnwidth]{Figures/picDRX}
-\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact \cite{wan2017experimental}.
-\OP{Is it a copy/paste from a publication?
+\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.% \OP{Is it a copy/paste from a publication?
 If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned.
 Please, I will appreciate if you could rearrange it as it would have been made.
-Thanks !}}
+Thanks !}
+}
 \label{fig:DRXschema}
 \end{figure}
+\OP{See the new proposed figure 6}
+
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
@@
 \end{figure}
+\OP{I think this is not finished yet ?}
 
@@
 
-In this section, the numerical validation of the previously performed dynamic recrystallization identification will be addressed.
-To achieve this, it is essential to establish a constitutive law capable of accurately predicting the plastic deformation of the material.
-In our prior publication (Tize Mha \eal \cite{TizeMha-2023}), a comparison between analytical constitutive laws and neural network based approach was conducted, resulting in the identification of an ANN model as the suitable choice for this material.
-As a result, this section comprises a two-fold focus: firstly, a recapitulation of the ANN based constitutive law identification, as presented in the previous article; and secondly, the integration of this identified ANN model with the JMAK model for predicting dynamic recrystallization behavior.
+In this section, we will focus on numerically validating the previously performed identification of dynamic recrystallization.
+This requires establishing a constitutive law capable of accurately predicting the material's plastic deformation.
+In our previous publication (Tize Mha \eal \cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
+The results revealed an artificial neural network model as the most appropriate option for this material.
+As a result, this section has two main focuses: first, a summary of the ANN-based constitutive law identification, as previously presented; and second, the incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization behavior.
 
@@
 In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
-The model can therefore be described as an elastoplastic model with the influence of strain rate and temperature.
-This type of behavior generally leads to Johnson-Cook \cite{Johnson-1983}, Zerilli Armstrong \cite{Zerilli-1987}, Hansel Spittle \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
+This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
+This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
-As reported by Tize Mha \eal \cite{TizeMha-2023}, Johnson-Cook, Zerilli Armstrong or Hansel Spittle type models, while providing a more or less faithful reproduction of material behavior at strain rates above $1~\ps$, do not take into account the softening due to DRX visible on experimental curves for strain rates below $1~\ps$ as reported in Figure \ref{fig:RawData}.
-Indeed, for the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ up to a value of around $\varepsilon=0.2$ to $0.3$ and then decreases to maintain a more or less constant value until the end of the test.
-Only the Arrhenius model can more or less account for this softening at low strain rates.
+
+As stated in the research conducted by Tize Mha \eal \cite{TizeMha-2023}, the Johnson--Cook, Zerilli--Armstrong, or Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as presented in Figure \ref{fig:RawData}.
+Indeed, at the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ until reaching a value of roughly $\varepsilon=0.2$ to $0.3$. 
+Afterward, it decreases, maintaining a relatively constant value until the end of the compression test.
+The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
 As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
-Correctly defining the hyperparameters of this neural network (number of hidden layers, number of neurons, activation functions, etc.) allows us to obtain a flow law that faithfully reproduces the data obtained from compression tests.
+Properly defining the hyperparameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
 
-According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we developed in Tize Mha \eal \cite{TizeMha-2023} a two hidden layers ANN based flow law whose general structure is reported in Figure \ref{fig:ANN-2HL}.
-This ANN contains an input layer of three neurons corresponding to the entries of the model ($\varepsilon$, $\mdot\varepsilon$ and $T$), an output layer with one neuron ($\sigma$), and $2$ hidden layers.
-
-All details about the artificial neural network, setup of the experimental data and the training method is reported the paper proposed by Pantalé \cite{Pantale-2023}.
-%Thus, all the neurons of the $k^{th}$ layer are connected to all the neurons of the ($k-1^{th}$) layer, as shown in~Figure~\ref{fig:ANN-2HL}.
+According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we have developed a two-hidden-layer artificial neural network based flow law in Tize Mha \eal \cite{TizeMha-2023}. 
+Figure \ref{fig:ANN-2HL} shows the general structure of this ANN. 
+The input layer of the ANN consists of three neurons that correspond to the model inputs, which are $\varepsilon$, $\mdot\varepsilon$, and $T$. 
+The output layer of the ANN contains one neuron representing $\sigma$, while there are two hidden layers.
+All details regarding the artificial neural network, experimental data setup, and training method are detailed in the paper proposed by Pantalé \cite{Pantale-2023}.
 
@@
 
-We again used the Tensorflow library for the development of the training program, and the ADAM optimizer was used for the training phase.
-The provided database presented in Section \ref{subsec:ExperimentalProcedure} consists of $21,030$ quadruplets of strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$) and stress ($\sigma$) values.
-%The training data were those from the tests presented in Section \ref{sec:ComTestResults} and were composed of $21,030$ quadruplets of ($\varepsilon$, $\mdot\varepsilon$, $T$, $\sigma$) values.
+We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
+The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
 
-We selected 6 different networks, named 3-$n$-$m$-1, where $n$ is the number of neurons in the first hidden layer and $m$ is the number of neurons in the second hidden layer, to show the importance of selecting the adequate number of neurons in the two layers.
+We selected six different networks, named 3-$n$-$m$-1, where $n$ represents the number of neurons in the first hidden layer and $m$ indicates the number of neurons in the second hidden layer to demonstrate the significance of choosing the appropriate number of neurons in these two layers.
 
-The training was performed on the basis of $5000$ epochs of the experimental dataset.
-It took $40$~min of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of RAM and an Intel 4-core i7-10510U processor to obtain the converged parameters of the ANN model.
+The training was conducted based on $5,000$ epochs of the experimental dataset.
+It took 40 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit operating system with 16 GB of RAM and an Intel 4-core i7-10510U processor until obtaining the converged parameters.
 
-Figure \ref{fig:ANN-conv} shows the evolution of the training error defined by the $\log_{10}$ of the internal $\RMSE$ during the training phase and Table \ref{tab:Errors} summarizes the final values of this criterion, along with the final values of the $\MARE$ and the $\RMSE$ for the 6 configurations of the neural network.
-On the basis of those results, we have selected the 3-15-7-1 network for further study, as it has the best convergence evolution and the lowest final error values ($\MARE=0.62\%$ and $\RMSE=0.38~\MPa$), while keeping a reasonable number of internal parameters ($N_{int}=180$).
+Figure \ref{fig:ANN-conv} shows the evolution of the training error, defined by the $\log_{10}$ of the internal $\RMSE$, during the training phase.
+Table \ref{tab:Errors} summarizes the final values of this criterion, as well as the final values of the $\MARE$ and the $\RMSE$ for all six neural network configurations.
+Based on these results, the 3-15-7-1 network was chosen for further investigation. 
+This network exhibited the most efficient convergence and achieved the lowest final error values of $\MARE=0.62\%$ and $\RMSE=0.38~\MPa$, while also maintaining a reasonable number of internal parameters ($N_{int}=180$).
 
@@
 \textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
+\toprule
+$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
 \hline
-$N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
-\toprule
 $\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
@@
 \end{figure}
-This model will be used as the material flow law for the numerical simulations presented in Section \ref{subsec:DRXSimulation}.
+This model will serve as the material flow equation for the numerical simulations discussed in Section \ref{subsec:DRXSimulation}.
 
@@
 
-In order to assess the effectiveness of the implementation of the DRX model presented in the previous sections, a compression test is simulated in this section.
-For this purpose, the material used for this simulation is a medium-carbon P20 iron alloy, which was used for the identification of this model.
-An axisymmetric Finite Element Method (FEM) model of hot cylinder compression with a height of $15$ mm and a diameter of $5$ mm is used, as shown in Figure \ref{fig:Mesh}.
-The frictional coefficient at the material/Die interface was assumed to be $0.2$ \cite{zhang2019elevated,sun2020kinetique}.
-The mesh consists of 986 CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
-The FEM model is simulated using Abaqus/Implicit due to the computation time related to the low strain rates.
-A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ mm of the total height is imposed on the upper part of the cylinder during the compression along the vertical axis of the specimen.
-The radial displacement $u_r$ of the upper part of the specimen is left free, while its axial displacement $u_z$ is imposed.
-The lower part of the cylinder remains fixed during the simulation.
-The effect of reducing the cylinder in combination with strain rate and temperature effect has been also evaluated in this simulation, and conclusions have been drawn.
-For this simulation, three temperatures ($1050\celsius$, $1150\celsius$, and $1250\celsius$) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$ and $1.0~\ps$) are considered.
+To evaluate the effectiveness of the DRX model presented earlier, we propose a numerical simulation of a compression test in this section.
+Our simulation concerns a medium-carbon P20 iron alloy, the same material used for the model's identification.
+An axisymmetric Finite Element (FE) model of hot cylinder compression with a height of $h=15$~mm and a diameter of $\phi=10$~mm is used, as shown in Figure \ref{fig:Mesh}.
+The assumed friction coefficient at the material/die interface is $\mu=0.2$ \cite{zhang2019elevated,sun2020kinetics}.
+The mesh is composed of $986$ ($17\times58$) CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
+Abaqus/Implicit is used to run the FE model simulation because of the long time needed to simulate a low strain rate compression.
+A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ of the total height is imposed on the upper part of the cylinder along the vertical axis of the specimen during compression.
+The upper and the lower parts of the specimen can slip in the radial direction according to the friction coefficient and the contact conditions.
+The axial displacement ($u_z$) of the upper part is imposed with a fixed velocity while the axial displacement of the lower part remains fixed during the simulation.
+The simulation evaluated the impact of reducing the cylinder height with the effects of strain rate and temperature. 
+Conclusions were drawn based on this analysis.
+The simulation considered three temperatures ($1050\degree$C, $1150\degree$C, and $1250\degree$C) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$, and $1.0~\ps$).
 \begin{figure}[H]
 \centering
-\includegraphics[width=0.6\columnwidth]{Figures/CyCompression2}
-\caption{Numerical model for the compression test}
+\includegraphics[height=0.7\columnwidth]{Figures/CyCompression2}
+\caption{Numerical FE model for the simulation of the compression test.}
 \label{fig:Mesh}
@@
 
-Temperature and strain rate play a crucial role in influencing dynamic recrystallization in materials, particularly for metals and alloys in the sense that they lead to the formation of new grains within the material.
-Indeed, higher temperature and low strain rate generally lead to increased nucleation rates and faster growth rates of new grains during dynamic recrystallization while in opposite lower temperature and higher strain rate lead to imcomplete dynamic recrystallization.
-At elevated temperatures, the mobility of atoms and dislocations is enhanced, allowing for the creation of new grain boundaries and the growth of new grains.
-This results in a finer and more equiaxed grain structure.
-Also, higher temperatures can lead to a higher fraction of recrystallized material because the enhanced mobility of dislocations promotes the formation of new grains.
-This can result in a significant change in the microstructure and mechanical properties of the material.
-Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} illustrate the simulated results of the DRX fraction of P20 steel under varying deformation conditions.
-Figure \ref{fig:TempEffect} illustrates that as the temperature rises, the scope of dynamic recrystallization expands.
-The gradual rise in the dynamic recrystallization fraction within the center is evident, spreading outward.
-This expansion is attributed to heightened thermal activation and increased atomic diffusion at elevated temperatures, rendering the material more susceptible to dynamic recrystallization.
-The $X_{drx}$ clearly increases with increasing temperature and reduction.
+Temperature and strain rate are critical factors that influence dynamic recrystallization in materials, particularly metals and alloys. 
+This process leads to the formation of new grains within the material. 
+Higher temperatures and lower strain rates typically result in increased nucleation rates and faster growth rates of new grains during dynamic recrystallization. 
+Conversely, lower temperatures and higher strain rates can lead to incomplete dynamic recrystallization.
+At high temperatures, the increased mobility of both atoms and dislocations facilitates the formation of fresh grain boundaries and promotes the growth of new grains, resulting
+in a more refined and isotropic grain structure.
+In addition, higher temperatures can raise the proportion of recrystallized material, with the enhanced dislocation mobility contributing to new grain creation.
+Consequently, this may result in a substantial change of the microstructure and the mechanical properties of the material.
+Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} display the simulated results of the DRX fraction of P20 steel under different deformation conditions.
+Figure \ref{fig:TempEffect} shows that as the temperature increases, the extent of dynamic recrystallization widens.
+The gradual increase in the dynamic recrystallization fraction in the center is noticeable, spreading outward.
+This expansion is a result of higher thermal activation and increased atomic diffusion at higher temperatures, which makes the material more vulnerable to dynamic recrystallization.
+The dynamic recrystallization degree ($X_{drx}$) unequivocally grows with the increase in temperature and reduction.
 At $45\%$ and $60\%$ reduction, the $X_{drx}$ of P20 steel
-reached $100\%$ in the central part of the specimen for all the initial sample temperatures.
+attained $100\%$ in the center of the specimen at all the initial sample temperatures.
 Indeed, the plastic deformation of a material is accompanied by the creation of dislocations.
-These dislocations represent a "store of elastic energy".
-When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganisation of the crystal structure, in two stages: restoration and recrystallisation.
-The nature of the phases does not change (those that are thermodynamically stable), the atoms keep the same lattice, but the grain boundaries and the orientation of the crystallites change.
+These dislocations represent a "storage of elastic energy".
+When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganization of the crystal structure in two stages: restoration and recrystallization.
+The nature of the phases remains unchanged (those that are thermodynamically stable), and the atoms retain the same lattice. 
+However, the grain boundaries and the orientation of the crystallites undergo changes.
 
@@
 \centering
-\includegraphics[width=0.98\columnwidth]{Figures/Temp_DRX}
+\includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
 \caption{$X_{drx}$ values at a strain rate of $0.01~\ps$ for different reductions and initial temperatures.}
@@
 \centering
-\includegraphics[width=0.98\columnwidth]{Figures/SR_DRX}
+\includegraphics[height=0.6\columnwidth]{Figures/SR_DRX}
 \caption{$X_{drx}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
@@
 
-The temperature at which these phenomena occur depends on the rate of deformation: the more a material is deformed, the more elastic energy it 'stores', so the earlier (at a lower temperature) restoration and recrystallisation will begin.
-According to Figure \ref{fig:SREffect}, the magnitude of dynamic recrystallization diminishes with escalated strain rates, leading to a reduction in the extent of recrystallization.
-This outcome is attributed to the accelerated pace of deformation at higher strain rates, elevating the critical strain and lowering the likelihood of internal dynamic recrystallization within the material.
+The temperature at which these phenomena occur depends on the rate of deformation. 
+The amount of elastic energy stored by a material increases with the degree of deformation, initiating restoration and recrystallization at a lower temperature.
+As shown in Figure \ref{fig:SREffect}, escalating strain rates result in a decrease in the extent of recrystallization due to reduced dynamic recrystallization magnitude.
+This result is due to the faster strain rate, which increases the critical strain and decreases the chance of internal dynamic recrystallization in the material.
 
@@
 
-In this section, a comparison beteween experimental and simulation will be carried out.
-Indeed, the percentage of dynamic recrystallization of selected regions is observed and then compared to the simulation.
-The Figure \ref{fig:expNumDRX} presents a comparison between experimental data and simulation for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate $0.01~\ps$.
-Five zones have been selected to observe the percentage of recrystallization, which varies between $5\%$ and $100\%$.
-In fact, $5\%$ corresponds to the value associated with the dead zone; which is the contact between the sample and die exposed to friction effects.
-On the other hand, $100\%$ corresponds to the value observed at the center of the sample, where deformation is higher.
-In the center of the sample, the temperature is high, leading to a significant accumulation of energy.
-Conversely, at the edges of the sample, a relatively complete recrystallization is observed because the temperature during deformation migrates from the center towards the outer regions of the piece, enabling recrystallization to take place.
-Microscopic observations corresponding to each zone reveal large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, whereas small grains (Figure \ref{fig:expNumDRX} (a)) are observed at the center of the sample, resulting from complete recrystallization.
+In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
+Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate of $0.01~\ps$.
+Five zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
+The $5\%$ corresponds to the dead zone, representing the contact area between the sample and die experiencing friction effects.
+In contrast, $100\%$ corresponds to the value observed at the center of the sample where deformation is the highest.
+The temperature is elevated at the center of the sample, leading to a significant accumulation of energy.
+Conversely, at the edges of the sample, a relatively complete recrystallization is observed.
+This is because the temperature during deformation shifts from the center towards the outer regions of the piece, allowing recrystallization to occur.
+Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
+\OP{Is it possible to have a table of comparison between the num and exp values of $X_{drx}$?}
 \begin{figure}[H]
@@
 \includegraphics[width=0.98\columnwidth]{Figures/expNumDRX}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \textcolor{red}{to see if I will remplace these pictures by new ones...}}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \OP{Please, enhance and finalize this figure}}
 \label{fig:expNumDRX}
@@
 
-In this study, we have harnessed the capabilities of ANN technique to gain a profound understanding of the dynamic recrystallization process and its evolution under varying conditions.
-The integration of ANN modeling, fundamental material models, simulation software, and experimental validation has led to a comprehensive framework that contributes significantly to the field of materials science and engineering.
-Initially, we successfully employed a ANN model to fit flow stress curves, enabling the prediction of critical conditions using the Poliak model.
-Doing this has allowed us to accurately anticipate the conditions at which the DRX process initiates, providing an invaluable tool for anticipating material behavior under specific deformation scenarios.
+In this study, we used the abilities of the ANN technique to deeply comprehend the dynamic recrystallization process and its adaptations in varying conditions.
+Through the fusion of ANN modeling, fundamental material models, simulation software, and experimental confirmation, a comprehensive framework has been created that greatly enhances the materials science and engineering field.
+Initially, we successfully used an ANN model to efficiently filter flow stress curves, which enabled us to predict critical conditions using the Poliak model.
+This allows us to accurately anticipate the conditions at which the DRX process begins, providing a valuable tool for predicting material behavior under specific deformation scenarios.
 
-We harnessed the predicted critical conditions to feed into the JMAK model and by doing so, we achieved the prediction of the DRX volumic fraction, thereby offering insights into the kinetics and mechanisms governing recrystallization.
-This integration bridges the gap between theoretical models and real-world phenomena, offering a deeper understanding of the intricate processes taking place during deformation.
-Taking our investigation further, we have seamlessly integrated the JMAK model into the ABAQUS software, a widely-used platform for simulation and analysis.
-Through this integration, we were able to simulate the evolution of DRX during hot compression tests, capturing the process's response to varying conditions.
-By comparing our simulation results with experimental data and employing microstructure analysis, we validated the accuracy of our simulations and affirmed the efficacy of our predictive models.
+We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volumetric fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
+This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more profound comprehension of the complex processes occurring during deformation.
+Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests. 
+This allowed us to capture the process's response to varying conditions without bias.
+By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.
 
-It is important to note that while our research marks a significant milestone, it also presents opportunities for future exploration.
-Fine-tuning our model, expanding our dataset, and refining the integration process can further enhance the accuracy and applicability of our predictions.
-Moreover, the successful linkage of theory, simulation, and experimentation provides a robust framework for tackling complex material behavior challenges in industries spanning from manufacturing to aerospace.
+It is noteworthy that although our research represents a significant milestone, it also presents opportunities for future exploration.
+Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
+Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace.
 
@@
 $X_{drx}^{e,p}$ & DRX's Volume fraction : $e, p$ for experimental and prediction respectively \\
-FEA & Finite element analysis \\
+FE  & Finite Element \\
 HS  & Hansel--Spittel \\
@@
 
+\OP{Check bibliography for errors and add doi for all references}
 \reftitle{References}

### 2023-08-29 Article.tex
Article update with Refs and one Figure

@@
 
-Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible plastic deformation.
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible deformation.
 It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
 When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
-During this deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
-DRX differs from static recrystallization (SRX), which takes longer to form new grains and occurs at lower temperatures.
+During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
+DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
 The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
-As the metal deforms, internal energy increases.
-At high temperatures, metal atoms have enough mobility to rearrange themselves, forming new equiaxed grains free of strain.
-Typically, these newly formed grains are much smaller than the original grains of the undeformed material.
+Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
 Their growth is accelerated by the stored energy and high temperatures.
-DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness.
-Additionally, it decreases the total strain energy, resulting in a more uniform microstructure and better material properties.
+DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.
 
-During high-rate hot deformation, dislocation density typically rises while a dynamic recovery (DRC) helps to mitigate such increases.
-DRX occurs when the dislocation density rises to an extent beyond the DRC’s accommodation.
-This is especially true for low and medium stacking fault energies \OP{what is it?} \textcolor{red}{mettalurgical phenomena that occurs when there is a deviation from the regular arrangement of atoms in a crystal's structure, I explained it more in details in Chapter 1 of my thesis} in fcc metals.\OPP{can you explain what you mean?}\textcolor{red}{These previous sentenses help to understand the DRX's initiation}.
+As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
-However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and degree of deformation.
-DRX is a crucial phenomenon that must be considered and controlled in industrial processes that use hot working to shape metals and alloys into products.
+However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography.
-However, this technique demands abundant sampling prior to and after the critical deformation.
-Additionally, the cooling phase entails phase changes from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
+However, this technique demands abundant sampling prior to and after the critical deformation which represents the level of strain that leads  the material begins to experience recovery and recrystallization processes, leading to the formation of new grains and a reduction in the average grain size.
+Additionally, the cooling phase entails phase changes (according to the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
 Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
@@
 For instance, Barnett \eal \cite{barnett2000predicting} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
-This approach defines the critical stress required for the initiation of SRX during deformation.
+This approach defines the critical stress required for the initiation of DRX during deformation.
 According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
 The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
-This understanding is crucial for materials processing and design purposes.
 
 The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
-They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta = f(\sigma)$} \textcolor{red}{Done throughout the paper} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements.
-This indicates the onset of an additional softening mechanism, in addition to DRC.
+They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta = f(\sigma)$} \textcolor{red}{Done !
+throughout the paper} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
+Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
 Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
@@
 This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
-Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine essential parameters.
+Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.
 
-Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (CreNieMo steel) using the Avrami kinetics model equation.
+Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
 They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
-Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of Mn alloy, with a focus on DRX and grain growth phenomena.
+Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
 Their results showed consistency with multiple compression tests.
@@
 Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
-Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triangular boundaries before affecting the lamellae.
-Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
+Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
+Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
 
 The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
-Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
+Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done !
+throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
 The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
-Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials.
-Hence, this study offers a replacement of the two smoothing methods with an ANN to procure the critical conditions for DRX.
-In other words, the proposed method suggests using an artificial neural network to directly model the relationship between stress $\sigma$ and rate hardening $\theta$, removing the need for explicit smoothing of experimental data.
-By properly training the ANN with relevant data, it can learn the underlying relationship between stress and dynamic recrystallization (DRX), ultimately providing a more precise estimation of the critical conditions for DRX.
+Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials like our previous work Tize Mha \eal \cite{TizeMha-2023} and many other works.
+Then the predictions of $\sigma(\varepsilon)$ are used as inputs for the $\theta(\sigma)$ prediction.
+Hence, this study offers a replacement of the two smoothing methods with an ANN approach to estimate the critical conditions for DRX.
 
@@
 To enhance the outcomes attained from the critical value identification process, we suggest employing the universal approximator capability of artificial neural networks.
-This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
-An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay}.
+An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay !}.
 The identical process applies to all 20 stress/strain curves.
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed} \textcolor{red}{Okay}}
+\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed} \textcolor{red}{Okay !}}
 \label{fig:AnnTheta}
@@
 
-\OP{Figure 6 has been removed because I think it is useless.} \textcolor{red}{Okay}
+\OP{Figure 6 has been removed because I think it is useless.} \textcolor{red}{Okay !}
 %\begin{figure}[H]
@@
 \centering
-\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay}}\vspace{-1mm}
+\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay !}}\vspace{-1mm}
 \begin{tabular}{cccccc}
@@
 The degree of recrystallization can be determined through experimental means.
-Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}. \OP{REF ?} \textcolor{red}{Done}
+Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}. \OP{REF ?} \textcolor{red}{Done !}
 
@@
 \end{figure}
-\OP{See the new proposed figure 6}
+\OP{See the new proposed figure 6} \textcolor{red}{Okay for the new Figure !}
 
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done !}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 \end{table}
-
-The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
-From this figure, it can be observed that the predictions align well with the experimental data, thus demonstrating the validity of the used model.
-\OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension}
-These results will therefore be used subsequently in the simulation section.
 \begin{figure}[H]
@@
 	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
-\caption{Comparison between DRX experimental data and JMAK model based prediction.
-\OP{I don't see the comparison?
-Is there many superposed curves ???} \textcolor{red}{As I said in my previous mail, I was writing the paper like the experimental data are already provided.
-Everything is okay now, I think !}}
+	\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???} \textcolor{red}{ Done !}}
 	\label{fig:nDRX}
 \end{figure}
-\OP{I think this is not finished yet ?}
+\OP{I think this is not finished yet ?} \textcolor{red}{More explanations have been added bellow}
+
+\textcolor{blue}{The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
+This figure shows the comparisons between the predicted and experimentally measured $X_{drx}$ under the tested temperatures and strain rates.
+The curves represent the variations of the predicted volume fractions of DRX with plastic strain.
+It can be easily found that the volume fraction of DRX is significantly dependent on the strain, temperature, as well as strain rate values.
+The DRX kinetic curves are characterized by S-shape.
+With the increase of strain, the volume fraction of DRX gradually increases.
+For a given temperature and strain, the volume fraction of DRX increases with the decrease of strain rate; while for a fixed strain rate and strain, the volume fraction of DRX increases with the increase of temperature.
+The deviation between the experimental and predicted volume fractions of DRX is not much important indicating that the proposed approach is suitable for predicting DRX for the studied superalloy under the wide tested forming conditions.
+The decrease of DRX with the increase of the strain rate can be explained by the fact that the volume fraction
+of dynamic recrystallization is sensitive to the forming temperature and strain rate. Especially, under high forming temperature
+and low strain rate, the dynamic recrystallization is easy to take
+place due to the high grain boundaries mobility. However, due to
+the low grain boundaries mobility, the dynamic recrystallization
+rate is slow under the low forming temperature and high strain
+rate.
+The correlation observed between experimental and prediction  leads to the validation of the model used in that study and therefore these results will be used subsequently in the simulation section}.
+\OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension !}
 
@@
 %----------------------------------------------------------------------------------
-
 In this section, we will focus on numerically validating the previously performed identification of dynamic recrystallization.
@@
 Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate of $0.01~\ps$.
-Five zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
+Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
 The $5\%$ corresponds to the dead zone, representing the contact area between the sample and die experiencing friction effects.
@@
 Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
-\OP{Is it possible to have a table of comparison between the num and exp values of $X_{drx}$?}
+\OP{Is it possible to have a table of comparison between the num and exp values of $X_{drx}$?} \textcolor{red}{We didn't evaluate experimentaly the DRX's value if I remember.
+Maybe in the future We will think to do something like that !}
 \begin{figure}[H]
 \centering
-\includegraphics[width=0.98\columnwidth]{Figures/expNumDRX}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \OP{Please, enhance and finalize this figure}}
+\includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \OP{Please, enhance and finalize this figure} \textcolor{red}{Done !}}
 \label{fig:expNumDRX}
@@
 
-\OP{Check bibliography for errors and add doi for all references}
+\OP{Check bibliography for errors and add doi for all references} \textcolor{red}{Almost done but Refs 29  to 35 didn't take into account doi evenif they were given !}
 \reftitle{References}

### 2023-08-29 Article.tex
Update of article + biblio + figure

@@
 
-Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing non-reversible deformation.
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation.
 It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
@@
 Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
-However, this technique demands abundant sampling prior to and after the critical deformation which represents the level of strain that leads  the material begins to experience recovery and recrystallization processes, leading to the formation of new grains and a reduction in the average grain size.
-Additionally, the cooling phase entails phase changes (according to the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
+Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
 Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
 In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
-For instance, Barnett \eal \cite{barnett2000predicting} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
+For instance, Barnett \eal \cite{barnett2000predicting}\OP{M.J.
+suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation.
+You could find review papers about this.)} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
 This approach defines the critical stress required for the initiation of DRX during deformation.
@@
 The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
-They observed the appearance of an inflection point on the $\theta(\sigma)$ \OP{I suggest the following writing: $\theta(\sigma)$ instead of $\theta = f(\sigma)$} \textcolor{red}{Done !
-throughout the paper} curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
-Najafizadeh and Jonas \cite{najafizadeh2006predicting} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
+They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
+Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
+Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
 Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
@@
 The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
-Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ \OP{I suggest the following writing: $\sigma=f(\varepsilon)$ instead of $\sigma(\varepsilon)$} \textcolor{red}{Done !
-throughout the paper} curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
+Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
 The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
@@
 In this subsection we will determine the critical deformation required to initiate recrystallization.
-Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
+Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow} were the pioneers in investigating this phenomenon.
 Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
-Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
+Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, jonas2003critical} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
 Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
@@
 The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
-An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}. \OP{Have to improve this later} \textcolor{red}{Okay !}.
+An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
 The identical process applies to all 20 stress/strain curves.
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.\OP{Caption changed} \textcolor{red}{Okay !}}
+\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
 \label{fig:AnnTheta}
@@
 \includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
-\caption{Work hardening computation for $1$ strain rate and $5$ temperatures.
-\OP{Im' not sure that this caption is related to the current figure.} \textcolor{red}{As the results provided by Olivier using an ANN model for each curve are not too much far from those obtained using a single ANN model, I've kept just the Figure directly obtained using a single ANN to illustrate the inflection points.
-This is for illustrative purposes only, as the critical values used for the rest of the calculation are those based on one ANN model for each curve}.}
+\caption{Work hardening computation for one strain rate and five temperatures.}
 \label{fig:nThetaOP}
@@
 The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
-Consequently, the Poliak and Jonas \cite{Poliak-1996,ei2003initiation,ei2003critical,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
+Consequently, the Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
 The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
@@
 
-\OP{Figure 6 has been removed because I think it is useless.} \textcolor{red}{Okay !}
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.99\columnwidth]{Figures/fThetaOP}
-%\caption{Work hardening polynomial fiting based on Poliak and Jonas model \cite{najafizadeh2006predicting}.}
-%\label{fig:fThetaOP}
-%\end{figure}
-
 \begin{table}[h!]
 \centering
-\caption{Critical conditions based on the proposed approach.\OP{Caption changed} \textcolor{red}{Okay !}}\vspace{-1mm}
+\caption{Critical conditions based on the proposed approach.}\vspace{-1mm}
 \begin{tabular}{cccccc}
@@
 The degree of recrystallization can be determined through experimental means.
-Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}. \OP{REF ?} \textcolor{red}{Done !}
+Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}.
 
@@
 \includegraphics[width=0.7\columnwidth]{Figures/picDRX}
-\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.% \OP{Is it a copy/paste from a publication?
-If so, you can't put it as it!} \textcolor{red}{Of course it was taken from publication as reference is mentioned.
-Please, I will appreciate if you could rearrange it as it would have been made.
-Thanks !}
-}
+\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.}
 \label{fig:DRXschema}
 \end{figure}
-\OP{See the new proposed figure 6} \textcolor{red}{Okay for the new Figure !}
 
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model  \cite{wan2017experimental} \OP{REF?} \textcolor{red}{Done !}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
-\OP{Please define steady stress after the peak stress} \textcolor{red}{The steady stress is considered as the minimum one after the peak stress}
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \OP{Who wrote this?
-REF?} \textcolor{red}{Now references are given before the equation} according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
+The steady stress is considered as the minimum one after the peak stress.
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
 \begin{equation}
@@
 	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
-	\caption{Comparison between DRX experimental data and JMAK model based prediction. \OP{I don't see the comparison? Is there many superposed curves ???} \textcolor{red}{ Done !}}
+	\caption{DRX experimental data (dots) and JMAK model based prediction (plain lines).}
 	\label{fig:nDRX}
 \end{figure}
-\OP{I think this is not finished yet ?} \textcolor{red}{More explanations have been added bellow}
 
-\textcolor{blue}{The curves of $X_{drx}(\varepsilon)$ are provided in Figure \ref{fig:nDRX} using the critical conditions calculated by the Poliak method.
-This figure shows the comparisons between the predicted and experimentally measured $X_{drx}$ under the tested temperatures and strain rates.
-The curves represent the variations of the predicted volume fractions of DRX with plastic strain.
-It can be easily found that the volume fraction of DRX is significantly dependent on the strain, temperature, as well as strain rate values.
-The DRX kinetic curves are characterized by S-shape.
-With the increase of strain, the volume fraction of DRX gradually increases.
-For a given temperature and strain, the volume fraction of DRX increases with the decrease of strain rate; while for a fixed strain rate and strain, the volume fraction of DRX increases with the increase of temperature.
-The deviation between the experimental and predicted volume fractions of DRX is not much important indicating that the proposed approach is suitable for predicting DRX for the studied superalloy under the wide tested forming conditions.
-The decrease of DRX with the increase of the strain rate can be explained by the fact that the volume fraction
-of dynamic recrystallization is sensitive to the forming temperature and strain rate. Especially, under high forming temperature
-and low strain rate, the dynamic recrystallization is easy to take
-place due to the high grain boundaries mobility. However, due to
-the low grain boundaries mobility, the dynamic recrystallization
-rate is slow under the low forming temperature and high strain
-rate.
-The correlation observed between experimental and prediction  leads to the validation of the model used in that study and therefore these results will be used subsequently in the simulation section}.
-\OP{I don't agree!} \textcolor{red}{Please have a look on Figure \ref{fig:nDRX} for more comprehension !}
+The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX}.
+The figure compares the experimentally measured $X_{drx}$ with the predicted values under the tested strain rates and temperatures.
+\OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data.
+Also check that the color of the dots is on in Figure 7.}
+The curves illustrate the changes in predicted volume fractions of DRX with plastic strain.
+It is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
+The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
+At a constant temperature and strain, the DRX volume fraction increases with decreasing strain rate.
+Conversely, at a fixed strain rate and strain, the DRX volume fraction increases with rising temperature.
+The difference between the predicted and experimental volume fractions of DRX is insignificant, confirming the suitability of the proposed approach for DRX prediction in the studied superalloy under various forming conditions.
+The reduction of DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to forming temperature and strain rate.
+Dynamic recrystallization is prone to occur at high forming temperatures and low strain rates due to increased grain boundary mobility.
+However, because of the limited mobility of grain boundaries, the rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
+The validation of the model used in the study, as evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation section.
 
@@
 Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
-\OP{Is it possible to have a table of comparison between the num and exp values of $X_{drx}$?} \textcolor{red}{We didn't evaluate experimentaly the DRX's value if I remember.
-Maybe in the future We will think to do something like that !}
+
 \begin{figure}[H]
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$. \OP{Please, enhance and finalize this figure} \textcolor{red}{Done !}}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$.}
 \label{fig:expNumDRX}
@@
 
-\OP{Check bibliography for errors and add doi for all references} \textcolor{red}{Almost done but Refs 29  to 35 didn't take into account doi evenif they were given !}
 \reftitle{References}

### 2023-08-29 Article.tex
Last comments taken into account and one ref added

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process while hot-compressing steel.
+\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process \textcolor{red}{during} hot-compressing steel.
 To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
@@
 The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
-This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations.
-The Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
+This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations \textcolor{red}{whereas the} Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
 A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
@@
 
-Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation.
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation (\textcolor{red}{Meaning : Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation}).
 It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
@@
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
+Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication} \textcolor{red}{That is an experimental method to evalute DRX volume fraction}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
@@
 In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
-For instance, Barnett \eal \cite{barnett2000predicting}\OP{M.J.
+For instance, Yan Peng \eal \cite{peng2022dynamic}\OP{M.J.
 suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation.
-You could find review papers about this.)} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
+You could find review papers about this.)} \textcolor{red}{Done !} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
 This approach defines the critical stress required for the initiation of DRX during deformation.
@@
 Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
-This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
+This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
 Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.
@@
 For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
-Nonetheless, we will outline the key aspects necessary to comprehend the suggested methodology.
+Nonetheless, we will outline the key aspects necessary to \textcolor{red}{understand} the suggested methodology.
 %The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
@@
 \end{table}
+\textcolor{red}{Those who want to go deep could read the previous paper as experimental setup is more explained there}
+
 Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
@@
 The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
-Furthermore, this frictional effect becomes more apparent as lubrication reduces over time.
+Furthermore, this frictional effect becomes more apparent as lubrication reduces over time . \textcolor{red}{Previous paper !}
 
@@
 Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
-In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
+In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a \textcolor{red}{threshold}.
 However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
@@
 Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
-Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the deformation parameters (deformation rate, temperature, and deformation) condition dynamic recrystallization (DRX), which can only be triggered once the critical deformation is reached and can be determined via metallography.
+Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the \textcolor{red}{physical} parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), which \textcolor{red}{Which is for DRX} can only be triggered once the critical deformation is reached and can be determined via metallography.
 However, this technique necessitates extensive sampling pre- and post-critical deformation.
-In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis.
+In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis \textcolor{red}{During de cooling after deformation, there is phaseS changes in the microstruture which depends on the cooling rate and this can affects SRX}.
 Hence simpler techniques, like developing analytical models have been implemented.
@@
 First, critical stresses and strains are determined using the ANN model to filter curves effectively.
-Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of forecasting the volume fraction of dynamic recrystallization.
+Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of \textcolor{red}{predicting} the volume fraction of dynamic recrystallization.
 
 %----------------------------------------------------------------------------------
-\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
+\subsection{DRX model's parameters identification\label{subsec:DRXParameters} \textcolor{red}{I think We can keep the paper organization like this but I understand what you mean ! thanks !}}
 %----------------------------------------------------------------------------------
@@
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 \end{equation}
-With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
+With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
 \begin{equation}
@@
 
-The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX}.
-The figure compares the experimentally measured $X_{drx}$ with the predicted values under the tested strain rates and temperatures.
+The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C).
 \OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data.
-Also check that the color of the dots is on in Figure 7.}
-The curves illustrate the changes in predicted volume fractions of DRX with plastic strain.
-It is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
+Also check that the color of the dots is on in Figure 7.} \textcolor{red}{Done !}
+The curves illustrate the changes in predicted volume fractions of DRX with plastic strain and it is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
 The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
@@
 
-We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volumetric fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
-This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more profound comprehension of the complex processes occurring during deformation.
+We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volume fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
+This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more \textcolor{red}{deep} comprehension of the complex processes occurring during deformation.
 Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests.
-This allowed us to capture the process's response to varying conditions without bias.
+This allowed us to capture the process's response to varying conditions without bias \textcolor{red}{This is related to the architecture of the ANN model, nothing else}.
 By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.
@@
 Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
-Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace.
+Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace \textcolor{red}{or other applications}.
 

### 2023-08-30 Article.tex
Changing threshold by plateau
Finalization of the paper + new figure

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process \textcolor{red}{during} hot-compressing steel.
+\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process during hot-compressing steel.
 To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
@@
 The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
-This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations \textcolor{red}{whereas the} Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
+This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations whereas the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
 A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
@@
 
-Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation (\textcolor{red}{Meaning : Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation}).
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation.
 It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
@@
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication} \textcolor{red}{That is an experimental method to evalute DRX volume fraction}.
+Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
@@
 In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
-For instance, Yan Peng \eal \cite{peng2022dynamic}\OP{M.J.
-suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation.
-You could find review papers about this.)} \textcolor{red}{Done !} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
+For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
 This approach defines the critical stress required for the initiation of DRX during deformation.
@@
 For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
-Nonetheless, we will outline the key aspects necessary to \textcolor{red}{understand} the suggested methodology.
-%The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
-%At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
-%In this new study, the ANN model will be used for predicting dynamic recrystallization, as explained in the introduction.
-%It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
+Nonetheless, we will outline the key aspects necessary to understand the suggested methodology.
 
@@
 \end{table}
-\textcolor{red}{Those who want to go deep could read the previous paper as experimental setup is more explained there}
 
-Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
+As detailed in Tize Mha \eal \cite{TizeMha-2023}, and reported in Figure \ref{fig:GleebleProcess}, hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\columnwidth]{Figures/GleebleProcess}
+\caption{\textls[-25]{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator.}}
+\label{fig:GleebleProcess}
+\end{figure}
 The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
@@
 The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
-Furthermore, this frictional effect becomes more apparent as lubrication reduces over time . \textcolor{red}{Previous paper !}
+Furthermore, this frictional effect becomes more apparent as lubrication reduces over time as reported in Tize Mha \eal \cite{TizeMha-2023}.
 
@@
 Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
-In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a \textcolor{red}{threshold}.
+In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
 However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
@@
 Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
-Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the \textcolor{red}{physical} parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), which \textcolor{red}{Which is for DRX} can only be triggered once the critical deformation is reached and can be determined via metallography.
-However, this technique necessitates extensive sampling pre- and post-critical deformation.
-In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis \textcolor{red}{During de cooling after deformation, there is phaseS changes in the microstruture which depends on the cooling rate and this can affects SRX}.
+Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
+However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
+In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallographic analysis difficult.
 Hence simpler techniques, like developing analytical models have been implemented.
@@
 In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
-The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the DRX model.
+The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
 We obtain the parameters of the JMAK model through a two-step process.
 First, critical stresses and strains are determined using the ANN model to filter curves effectively.
-Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of \textcolor{red}{predicting} the volume fraction of dynamic recrystallization.
+Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization.
 
 %----------------------------------------------------------------------------------
-\subsection{DRX model's parameters identification\label{subsec:DRXParameters} \textcolor{red}{I think We can keep the paper organization like this but I understand what you mean ! thanks !}}
+\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
 %----------------------------------------------------------------------------------
@@
 
-To enhance the outcomes attained from the critical value identification process, we suggest employing the universal approximator capability of artificial neural networks.
+To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
 This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
@@
 \end{figure}
-The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by Equation (\ref{eq:AARE}):
+The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by the following equation:
 \begin{equation}
@@
 \end{equation}
-and the root-mean-squared error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
+and the root-mean-squared error ($\RMSE$) defined by the following equation:
 \begin{equation}
@@
 The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C).
-\OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data.
-Also check that the color of the dots is on in Figure 7.} \textcolor{red}{Done !}
 The curves illustrate the changes in predicted volume fractions of DRX with plastic strain and it is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
@@
 Conversely, at the edges of the sample, a relatively complete recrystallization is observed.
-This is because the temperature during deformation shifts from the center towards the outer regions of the piece, allowing recrystallization to occur.
+This is because the temperature during deformation shifts from the center towards the upper and lower regions of the piece (due to the fact that the anvils are cooled), allowing recrystallization to occur.
 Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
@@
 We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volume fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
-This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more \textcolor{red}{deep} comprehension of the complex processes occurring during deformation.
+This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more deep comprehension of the complex processes occurring during deformation.
 Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests.
-This allowed us to capture the process's response to varying conditions without bias \textcolor{red}{This is related to the architecture of the ANN model, nothing else}.
+This allowed us to capture the process's response to varying conditions without bias.
 By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.
@@
 Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
-Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace \textcolor{red}{or other applications}.
+Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace or other applications.
 

### 2023-08-30 Article.tex
Article + biblio update

@@
 Their growth is accelerated by the stored energy and high temperatures.
-DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.
+DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{javidikia2023grain, dourandish2022microstructure, shen2021effect}.
 
@@
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication}.
+Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication, khan2021interactions}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
@@
 This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
-This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978} or Arrhenius \cite{Sellars-1966} flow law type.
+This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{mha2022generalized} or Arrhenius \cite{Sellars-1966} flow law type.
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.

### 2023-08-31 Article.tex
Final version send to the editor

@@
 
-As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
+As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
@@
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
-Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
 Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
@@
 They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
+Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
 Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
@@
 They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
-Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
+Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
 Their results showed consistency with multiple compression tests.
-Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructural evolution of TiAl-based alloys during hot compression.
+Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
 Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
@@
 
-Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
+Dynamic recrystallization is a significant phenomenon for regulating a material's microstructure and mechanical properties during hot working.
 In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
@@
 However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
-In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallographic analysis difficult.
+In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
 Hence simpler techniques, like developing analytical models have been implemented.
@@
 As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
-Properly defining the hyperparameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
+Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
 
@@
 validation, O.P.;
-formal analysis, O.P.;
+formal analysis, O.P. and P.D.;
 investigation, P.D.;
@@
 data curation, P.T.M. and P.D.;
-writing---original draft preparation, P.T.M.;
+writing---original draft preparation, O.P. and P.T.M.;
 writing---review and editing, O.P.;

### 2023-10-02 Article.tex
Some easy corrections

@@
 Their growth is accelerated by the stored energy and high temperatures.
-DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{javidikia2023grain, dourandish2022microstructure, shen2021effect}.
+DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{Javidikia-2023, Dourandish-2022, Shen-2021}.
 
@@
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{babu2022implication, khan2021interactions}.
+Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022, Khan-2021}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
@@
 In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
-For instance, Yan Peng \eal \cite{peng2022dynamic} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
+For instance, Yan Peng \eal \cite{Peng-2022} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
 This approach defines the critical stress required for the initiation of DRX during deformation.
-According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
+According to Gottstein \eal \cite{Gottstein-2004}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
 The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
 
-The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
+The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2}.
 They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
+Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
 Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
@@
 This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
-Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.
+Li \eal \cite{Li-2015} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{Estrin-1984,Mecking-1981} to determine the Avrami equation coefficients.
 
-Zhang \eal \cite{zhang2016kinetics} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
+Zhang \eal \cite{Zhang-2016} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
 They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
-Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
+Cho \eal \cite{Cho-2005} and Razali \eal \cite{Razali-2021} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
 Their results showed consistency with multiple compression tests.
-Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
-Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
-Cui \eal \cite{cui2016hot} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
-Recently, Chen \eal \cite{chen2023finite} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
+Wan \eal \cite{Wan-2017} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
+Li \eal \cite{Li-2018} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
+Cui \eal \cite{Cui-2016} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
+Recently, Chen \eal \cite{Chen-2023} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
 
@@
 The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
-All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
+All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in \textcolor{purple}{$0.001$} increments.
 \begin{figure}[H]
@@
 In this subsection we will determine the critical deformation required to initiate recrystallization.
-Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow} were the pioneers in investigating this phenomenon.
+Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
 Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
-Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, jonas2003critical} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
+Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
 Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+This \textcolor{purple}{can be done by characterizing} each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
-Consequently, the Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} method, which is currently well-regarded, will be used in this investigation.
+Consequently, the Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} method, which is currently well-regarded, will be used in this investigation.
 The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
@@
 The degree of recrystallization can be determined through experimental means.
-Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence  \cite{wan2017experimental}.
+Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence \cite{Wan-2017}.
 
@@
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Wan-2017}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
 \begin{equation}
@@
 This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
-This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{mha2022generalized} or Arrhenius \cite{Sellars-1966} flow law type.
+This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \textcolor{purple}{\cite{TizeMha-2023}} or Arrhenius \cite{Sellars-1966} flow law type.
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
@@
 An axisymmetric Finite Element (FE) model of hot cylinder compression with a height of $h=15$~mm and a diameter of $\phi=10$~mm is used, as shown in Figure \ref{fig:Mesh}.
-The assumed friction coefficient at the material/die interface is $\mu=0.2$ \cite{zhang2019elevated,sun2020kinetics}.
+The assumed friction coefficient at the material/die interface is $\mu=0.2$ \cite{Zhang-2019,Sun-2020}.
 The mesh is composed of $986$ ($17\times58$) CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).

### 2023-10-02 Article.tex
Update bibliography

@@
 The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
-All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in \textcolor{purple}{$0.001$} increments.
+All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
 \begin{figure}[H]
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-This \textcolor{purple}{can be done by characterizing} each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
-This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \textcolor{purple}{\cite{TizeMha-2023}} or Arrhenius \cite{Sellars-1966} flow law type.
+This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{mha2022generalized} or Arrhenius \cite{Sellars-1966} flow law type.
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.

### 2023-10-03 Article.tex
Modifs based on reviewers recommandations

--- 2023-08-31 Article.tex
@@
 
-As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
+As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
@@
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
-Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
 Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
@@
 They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
+Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
 Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
@@
 They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
-Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
+Cho \eal \cite{cho2005prediction} and Razali \eal \cite{razali2021new} used a well-established model to predict the microstructural evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
 Their results showed consistency with multiple compression tests.
-Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
+Wan \eal \cite{wan2017experimental} employed the same equation to predict the microstructural evolution of TiAl-based alloys during hot compression.
 Li \eal \cite{li2018finite} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
@@
 
-Dynamic recrystallization is a significant phenomenon for regulating a material's microstructure and mechanical properties during hot working.
+\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
 In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
@@
 However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
-In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
+In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallographic analysis difficult.
 Hence simpler techniques, like developing analytical models have been implemented.
-Several studies analyzing the initiation of DRX have been conducted with this objective in mind.
+Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
 
-In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
+\textcolor{red}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
 The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
@@
 First, critical stresses and strains are determined using the ANN model to filter curves effectively.
-Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization.
+Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.
 
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
-\caption{Filtering of the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
+\caption{Filtrage des données de contrainte/déformation à l'aide du réseau de neurones artificiels (ANN) pour $\mdot\varepsilon=0.001~\text{s}^{-1}$ et $T=1050\celsius$.}
 \label{fig:AnnFit}
@@
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Avrami-1939} , commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{chen2014dynamic,li2019effect,wang2021artificial}:
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$ \cite{zener1944effect}, according to the following equation as described in \cite{chen2014dynamic,li2019effect,wang2021artificial} :
 \begin{equation}
@@
 \end{equation}
-With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later.
+With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later and the effective activation energy parameter $Q$ value is $437.385$ kJ.mol$^{-1}$.
 
@@
 As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
-Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
+Properly defining the hyperparameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
 
@@
 validation, O.P.;
-formal analysis, O.P. and P.D.;
+formal analysis, O.P.;
 investigation, P.D.;
@@
 data curation, P.T.M. and P.D.;
-writing---original draft preparation, O.P. and P.T.M.;
+writing---original draft preparation, P.T.M.;
 writing---review and editing, O.P.;

### 2023-10-03 Article.tex
Robust command for comment in the text

--- 2023-10-02 Article.tex
@@
 \DeclareRobustCommand{\MPa}{\text{MPa}}
+\DeclareRobustCommand{\PTM}[1]{~\begingroup\sethlcolor{green}\textcolor{red}{\hl{\textbf{P.T.M.:} #1}}\endgroup~}
 
@@
 
-Dynamic recrystallization is a significant phenomenon for regulating a material's microstructure and mechanical properties during hot working.
+\PTM{The following two paragraphs will be removed}
+
+\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
 In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
@@
 Hence simpler techniques, like developing analytical models have been implemented.
-Several studies analyzing the initiation of DRX have been conducted with this objective in mind.
+Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
 
-In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
+\textcolor{red}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
 The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
@@
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Wan-2017}, commonly known as the JMAK model, expressed by the following equation:
+The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Avrami-1939} , commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
@@
 The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$ \cite{Zenner-1944}, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
 \begin{equation}

### 2023-10-03 Article.tex
Revised version of the paper

@@
 \DeclareRobustCommand{\MPa}{\text{MPa}}
-\DeclareRobustCommand{\PTM}[1]{~\begingroup\sethlcolor{green}\textcolor{red}{\hl{\textbf{P.T.M.:} #1}}\endgroup~}
-
-% This is used to add comments into the text
-%
-% Will have to be removed from final version
-%
-\usepackage{soul}
-\usepackage{color}
-\definecolor{VWyellow}{RGB}{255,251,150}
-\DeclareRobustCommand{\OP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
-\DeclareRobustCommand{\OPP}[1]{\begingroup\sethlcolor{VWyellow}\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}
 
@@
 
-\PTM{The following two paragraphs will be removed}
-
-\textcolor{red}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
-In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
-However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
-Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
-Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
-Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
-However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
-In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
-Hence simpler techniques, like developing analytical models have been implemented.
-Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
-
-\textcolor{red}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
-The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
-We obtain the parameters of the JMAK model through a two-step process.
-First, critical stresses and strains are determined using the ANN model to filter curves effectively.
-Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.
+%\PTM{The following two paragraphs will be removed}
+%
+%\textcolor{purple}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
+%In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
+%However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
+%Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
+%Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
+%Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
+%However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
+%In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
+%Hence simpler techniques, like developing analytical models have been implemented.
+%Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
+%
+%\textcolor{purple}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
+%The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
+%We obtain the parameters of the JMAK model through a two-step process.
+%First, critical stresses and strains are determined using the ANN model to filter curves effectively.
+%Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.
 
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN based filtering model's archicture \label{subsec:ANNbasics}}
+\subsubsection{ANN based filtering model's \textcolor{purple}{architecture} \label{subsec:ANNbasics}}
 %----------------------------------------------------------------------------------
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-This \textcolor{purple}{can be done by characterizing} each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+\textcolor{purple}{This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).}
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
-\caption{Filtrage des données de contrainte/déformation à l'aide du réseau de neurones artificiels (ANN) pour $\mdot\varepsilon=0.001~\text{s}^{-1}$ et $T=1050\celsius$.}
+\caption{Filtering of the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
 \label{fig:AnnFit}
@@
 The degree of recrystallization can be determined through experimental means.
-Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence \cite{Wan-2017}.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
-\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.}
-\label{fig:DRXschema}
-\end{figure}
+%Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence \cite{Wan-2017}.
+%\begin{figure}[!ht]
+%\centering
+%\includegraphics[width=0.7\columnwidth]{Figures/picDRX}
+%\caption{Schematic diagram of three stages during DRX, nucleation, nucleus growth and grain contact.}
+%\label{fig:DRXschema}
+%\end{figure} 
+\textcolor{purple}{For some visual representation of microstructure evolution during DRX, the interested reader can refer to Chen \eal \cite{Chen-2019}.}
 
@@
 The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$ \cite{Zenner-1944}, according to the following equation \cite{Chen-2014,Li-2019,Wang-2021}:
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon \cite{Zenner-1944} parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \textcolor{purple}{(where $Q$ is the effective activation energy parameter $Q=437.4~\text{kJ/mol}$, $R$ is the universal gas constant $R=8.314~\text{J/mol/K}$)}, according to the following equation \textcolor{purple}{reported by other researchers such as \cite{Chen-2014,Li-2019,Wang-2021} for similar steel compositions and deformation conditions}:
 \begin{equation}
 \begin{cases}
-\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s}
+\varepsilon_c = A_cZ^{n_c} \\ \varepsilon_p = A_pZ^{n_p} \\ \sigma_c = B_cZ^{m_c} \\ \sigma_p = B_pZ^{m_p}\\ \sigma_s = B_sZ^{m_s},
 \end{cases}
@@
 \end{equation}
-With the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described in this paper later and the effective activation energy parameter $Q$ value is $437.385$ kJ.mol$^{-1}$.
+with the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described here after.
+The procedure for determining of the value of $Q$ is detailed in \cite{TizeMha-2023}.
 
@@
 \hline
-$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141	$&$10265.8	$&$0.235832	$\\
+$4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141$&$10265.8$&$0.235832$\\
 \toprule
@@
 \end{table}
+
+The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C).
 \begin{figure}[H]
@@
 \end{figure}
-
-The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C).
+\textcolor{purple}{Figure \ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.
+From this later, we determined the location of one of experimental point in Figure \ref{fig:nDRX} (the red one for $\varepsilon=0.55$).
+The same approach using different temperatures and strains is used to obtain the other experimental points reported in Figure \ref{fig:nDRX}.}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\columnwidth]{Figures/micrograph}
+	\caption{\textcolor{purple}{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.}}
+	\label{fig:eDRX}
+\end{figure}
 The curves illustrate the changes in predicted volume fractions of DRX with plastic strain and it is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
@@
 We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
-The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
+The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples \textcolor{purple}{(we have $701\times30$ quadruples because $\varepsilon\in[0,0.7]$ with an increment of $0.001$, so we have $701$ values and 30 data curves)} of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
 
@@
 This model will serve as the material flow equation for the numerical simulations discussed in Section \ref{subsec:DRXSimulation}.
+\textcolor{purple}{Once the neural network is trained and a stable solution is obtained, it is re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
+The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021, Pantale-2023}.}
 
@@
 \includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
-\caption{$X_{drx}$ values at a strain rate of $0.01~\ps$ for different reductions and initial temperatures.}
+\caption{$X_{drx}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
 \label{fig:TempEffect}
@@
 In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
-Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a deformation strain rate of $0.01~\ps$.
+Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a \textcolor{purple}{strain rate of $\mdot{\varepsilon}=0.1~\ps$}.
 Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.01~\ps$.}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and \textcolor{purple}{strain rate $\mdot{\varepsilon}=0.1~\ps$}.}
 \label{fig:expNumDRX}

### 2023-10-04 Article.tex
Removing two refences as proposed by editor

@@
 Their growth is accelerated by the stored energy and high temperatures.
-DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{Javidikia-2023, Dourandish-2022, Shen-2021}.
+DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{Javidikia-2023, Shen-2021}.
 
@@
 The experimental tests used in this work are identical to those previously published by Tize Mha \eal \cite{TizeMha-2023}.
-For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
+For additional information, readers can refer to the publications by our research group \cite{Pantale-2021}.
 Nonetheless, we will outline the key aspects necessary to understand the suggested methodology.
@@
 The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
-As proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
+As proposed by Pantalé \eal \cite{Pantale-2021} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
 Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
 
-According to the method proposed by Pantalé \eal \cite{Pantale-2021, Pantale-2023}, we have developed a two-hidden-layer artificial neural network based flow law in Tize Mha \eal \cite{TizeMha-2023}.
+According to the method proposed by Pantalé \eal \cite{Pantale-2021}, we have developed a two-hidden-layer artificial neural network based flow law in Tize Mha \eal \cite{TizeMha-2023}.
 Figure \ref{fig:ANN-2HL} shows the general structure of this ANN.
@@
 The output layer of the ANN contains one neuron representing $\sigma$, while there are two hidden layers.
-All details regarding the artificial neural network, experimental data setup, and training method are detailed in the paper proposed by Pantalé \cite{Pantale-2023}.
+All details regarding the artificial neural network, experimental data setup, and training method are detailed in the paper proposed by Pantalé \eal \cite{Pantale-2021}.
 
@@
 \textcolor{purple}{Once the neural network is trained and a stable solution is obtained, it is re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
-The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021, Pantale-2023}.}
+The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021}.}
 

### 2023-10-04 Article.tex
Reduce number of self-citations to 3

@@
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022, Khan-2021}.
+Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.

### 2023-10-09 Article.tex
Clear purple text

@@
 The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
-All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in \textcolor{purple}{$0.001$} increments.
+All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$ increments.
 \begin{figure}[H]
@@
 
-%\PTM{The following two paragraphs will be removed}
-%
-%\textcolor{purple}{Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
-%In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
-%However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
-%Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
-%Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
-%Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the physical parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), can only be triggered once the critical deformation is reached and can be determined via metallography.
-%However, this technique necessitates extensive sampling of the pre- and post-critical deformation.
-%In addition, during the cooling phase, phase transformations can occur that alter the deformed structure as it descends from the hot working temperature, making metallography analysis difficult.
-%Hence simpler techniques, like developing analytical models have been implemented.
-%Several studies analyzing the initiation of DRX have been conducted with this objective in mind}.
-%
-%\textcolor{purple}{In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
-%The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the JMAK model.
-%We obtain the parameters of the JMAK model through a two-step process.
-%First, critical stresses and strains are determined using the ANN model to filter curves effectively.
-%Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of predicting the volume fraction of dynamic recrystallization}.
-
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN based filtering model's \textcolor{purple}{architecture} \label{subsec:ANNbasics}}
+\subsubsection{ANN based filtering model's architecture\label{subsec:ANNbasics}}
 %----------------------------------------------------------------------------------
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-\textcolor{purple}{This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).}
+This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
@@
 %\end{figure} 
-\textcolor{purple}{For some visual representation of microstructure evolution during DRX, the interested reader can refer to Chen \eal \cite{Chen-2019}.}
+For some visual representation of microstructure evolution during DRX, the interested reader can refer to Chen \eal \cite{Chen-2019}.
 
@@
 The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon \cite{Zenner-1944} parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, \textcolor{purple}{(where $Q$ is the effective activation energy parameter $Q=437.4~\text{kJ/mol}$, $R$ is the universal gas constant $R=8.314~\text{J/mol/K}$)}, according to the following equation \textcolor{purple}{reported by other researchers such as \cite{Chen-2014,Li-2019,Wang-2021} for similar steel compositions and deformation conditions}:
+It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon \cite{Zenner-1944} parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, (where $Q$ is the effective activation energy parameter $Q=437.4~\text{kJ/mol}$, $R$ is the universal gas constant $R=8.314~\text{J/mol/K}$), according to the following equation reported by other researchers such as \cite{Chen-2014,Li-2019,Wang-2021} for similar steel compositions and deformation conditions:
 \begin{equation}
@@
 \end{figure}
-\textcolor{purple}{Figure \ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.
+Figure \ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.
 From this later, we determined the location of one of experimental point in Figure \ref{fig:nDRX} (the red one for $\varepsilon=0.55$).
-The same approach using different temperatures and strains is used to obtain the other experimental points reported in Figure \ref{fig:nDRX}.}
+The same approach using different temperatures and strains is used to obtain the other experimental points reported in Figure \ref{fig:nDRX}.
 \begin{figure}[H]
@@
 	\includegraphics[width=0.5\columnwidth]{Figures/micrograph}
-	\caption{\textcolor{purple}{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.}}
+	\caption{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.}
 	\label{fig:eDRX}
@@
 This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
-This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \textcolor{purple}{\cite{TizeMha-2023}} or Arrhenius \cite{Sellars-1966} flow law type.
+This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{TizeMha-2023} or Arrhenius \cite{Sellars-1966} flow law type.
 Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
@@
 We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
-The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples \textcolor{purple}{(we have $701\times30$ quadruples because $\varepsilon\in[0,0.7]$ with an increment of $0.001$, so we have $701$ values and 30 data curves)} of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
+The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples (we have $701\times30$ quadruples because $\varepsilon\in[0,0.7]$ with an increment of $0.001$, so we have $701$ values and 30 data curves) of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
 
@@
 This model will serve as the material flow equation for the numerical simulations discussed in Section \ref{subsec:DRXSimulation}.
-\textcolor{purple}{Once the neural network is trained and a stable solution is obtained, it is re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
-The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021}.}
+Once the neural network is trained and a stable solution is obtained, it is re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
+The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021}.
 
@@
 In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
-Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a \textcolor{purple}{strain rate of $\mdot{\varepsilon}=0.1~\ps$}.
+Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a strain rate of $\mdot{\varepsilon}=0.1~\ps$.
 Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and \textcolor{purple}{strain rate $\mdot{\varepsilon}=0.1~\ps$}.}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$}.
 \label{fig:expNumDRX}

### 2023-10-10 Article.tex
Add new figure

@@
 %----------------------------------------------------------------------------------
-\subsubsection{Experimental validation \label{subsec:ExpValid}}
+\subsubsection{\textcolor{purple}{Comparison with some experiments}\label{subsec:ExpValid}}
 %----------------------------------------------------------------------------------
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$}.
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
 \label{fig:expNumDRX}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
+\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
+\label{fig:expNumDRX2}
 \end{figure}

### 2023-10-10 Article.tex
Small paragraph added

@@
 
+\textcolor{purple}{To further demonstrate the validity of the proposed model as demonstrated during the identification for a strain rate $\mdot\varepsilon = 0.001\ps$, we carried out a comparison between the microstructure obtained experimentally for a strain $\varepsilon=0.55$ and its numerical correspondence for a reduction of $45\%$ as can be seen in Figure 16.
+This figure shows that recrystallization is not complete at the edge of the specimen, nor at the point of contact between the specimen and the anvils.
+This is why unrecrystallized grains can be seen.
+These observations are confirmed numerically.
+This further confirms the validity of the model.}
 \begin{figure}[H]

### 2023-10-10 Article.tex
Add paragraph of comments for fig 16

--- 2023-10-10 Article.tex
@@
 
+\textcolor{purple}{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level.
+It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape.
+As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}$ is less than $5\%$ and the microstructure enhances very large grains.
+We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}$ is in the range of $75\%$ to $90\%$.}
 \begin{figure}[H]
@@
 \includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
+\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
 \label{fig:expNumDRX2}

### 2023-10-10 Article.tex
Change Xdrx to Xdrx predicted in last paragraph

@@
 This expansion is a result of higher thermal activation and increased atomic diffusion at higher temperatures, which makes the material more vulnerable to dynamic recrystallization.
-The dynamic recrystallization degree ($X_{drx}$) unequivocally grows with the increase in temperature and reduction.
-At $45\%$ and $60\%$ reduction, the $X_{drx}$ of P20 steel
+The dynamic recrystallization degree ($X_{drx}^{p}$) unequivocally grows with the increase in temperature and reduction.
+At $45\%$ and $60\%$ reduction, the $X_{drx}^{p}$ of P20 steel
 attained $100\%$ in the center of the specimen at all the initial sample temperatures.
@@
 \includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
-\caption{$X_{drx}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
+\caption{$X_{drx}^{p}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
 \label{fig:TempEffect}
@@
 \includegraphics[height=0.6\columnwidth]{Figures/SR_DRX}
-\caption{$X_{drx}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
+\caption{$X_{drx}^{p}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
 \label{fig:SREffect}
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
+\caption{Experimental and numerical $X_{drx}^{p}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
 \label{fig:expNumDRX}
@@
 It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape.
-As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}$ is less than $5\%$ and the microstructure enhances very large grains.
-We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}$ is in the range of $75\%$ to $90\%$.}
+As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}^{p}$ is less than $5\%$ and the microstructure enhances very large grains.
+We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75\%$ to $90\%$.}
 \begin{figure}[H]
@@
 \includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
-\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
+\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
 \label{fig:expNumDRX2}
@@
 ANN & Artificial neural network \\
-AR  & Arrhenius \\
-CPU & Central processing unit \\
-DRC & Dynamic recovery\\
+%AR  & Arrhenius \\
+%CPU & Central processing unit \\
+%DRC & Dynamic recovery\\
 DRX & Dynamic recrystallization \\
@@
 FE  & Finite Element \\
-HS  & Hansel--Spittel \\
-JC  & Johnson--Cook \\
-MZA & Modified Zerilli--Armstrong \\
+%HS  & Hansel--Spittel \\
+%JC  & Johnson--Cook \\
+%MZA & Modified Zerilli--Armstrong \\
 SRX & Static recrystallization \\
-WH  & Work hardening \\
-ZA  & Zerilli--Armstrong
+WH  & Work hardening
+%ZA  & Zerilli--Armstrong
 \end{tabular}

### 2023-10-11 Article.tex
Remove purple additions

@@
 %----------------------------------------------------------------------------------
-\subsubsection{\textcolor{purple}{Comparison with some experiments}\label{subsec:ExpValid}}
+\subsubsection{Comparison with some experiments\label{subsec:ExpValid}}
 %----------------------------------------------------------------------------------
@@
 
-\textcolor{purple}{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level.
+Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level.
 It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape.
 As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}^{p}$ is less than $5\%$ and the microstructure enhances very large grains.
-We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75\%$ to $90\%$.}
+We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75\%$ to $90\%$.
 \begin{figure}[H]
@@
 \includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
-\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
+\caption{Comparison of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
 \label{fig:expNumDRX2}

### 2023-10-16 Article.tex
Correction of bad label position in section names

@@
 %----------------------------------------------------------------------------------
-\section{Introduction\label{sec:Introduction}}
+\section{Introduction}\label{sec:Introduction}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\section{Materials and experiments\label{sec:MaterialsExperiments}}
+\section{Materials and experiments}\label{sec:MaterialsExperiments}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsection{Experimental procedure and compression tests results\label{subsec:ExperimentalProcedure}}
+\subsection{Experimental procedure and compression tests results}\label{subsec:ExperimentalProcedure}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
+\subsection{DRX model's parameters identification}\label{subsec:DRXParameters}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN based filtering model's architecture\label{subsec:ANNbasics}}
+\subsubsection{ANN based filtering model's architecture}\label{subsec:ANNbasics}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN filtering based model's application \label{subsec:ANNapplication}}
+\subsubsection{ANN filtering based model's application} \label{subsec:ANNapplication}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{Critical conditions evaluation\label{subsec:CrConditions}}
+\subsubsection{Critical conditions evaluation}\label{subsec:CrConditions}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsection{DRXmodel parameters evaluation\label{subsec:DRXparams}}
+\subsection{DRXmodel parameters evaluation}\label{subsec:DRXparams}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\section{Numerical simulation of the compression\label{sec:NumSim}}
+\section{Numerical simulation of the compression}\label{sec:NumSim}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsection{Identification of the ANN constitutive law\label{subsec:ANNConstitutiveLaw}}
+\subsection{Identification of the ANN constitutive law}\label{subsec:ANNConstitutiveLaw}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsection{Dynamic recrystallization simulation\label{subsec:DRXSimulation}}
+\subsection{Dynamic recrystallization simulation}\label{subsec:DRXSimulation}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{Temperature and strain rate effects \label{subsec:TempSReffect}}
+\subsubsection{Temperature and strain rate effects}\label{subsec:TempSReffect}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\subsubsection{Comparison with some experiments\label{subsec:ExpValid}}
+\subsubsection{Comparison with some experiments}\label{subsec:ExpValid}
 %----------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------
-\section{Conclusions\label{sec:Conclusions}}
+\section{Conclusions}\label{sec:Conclusions}
 %----------------------------------------------------------------------------------
@@
 \appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixstart
-\appendix
-\section[\appendixname~\thesection]{}\label{sec:Appendix}
+%\appendixstart
+%\appendix
+%\section[\appendixname~\thesection]{}\label{sec:Appendix}
 

### 2023-10-16 Article.tex
Include Proofs

@@
 %=================================================================
-\documentclass[metals,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+\documentclass[metals,article,accept,pdftex,moreauthors]{Definitions/mdpi}
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 \copyrightyear{2023}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{ }
-\daterevised{ } % Comment out if no revised date
-\dateaccepted{ }
+\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{31 August 2023 }
+\daterevised{10 October 2023 } % Comment out if no revised date
+\dateaccepted{13 October 2023 }
 \datepublished{ }
@@
 % Full title of the paper (Capitalized)
-\Title{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}
+\Title{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and~Application}
 
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application}
-
+\TitleCitation{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and~Application}
+%MDPI: Title modified, please confirm.
 % Author Orchid ID: enter ID or remove command
@@
 % Authors, for the paper (add full first names)
-\Author{Pierre Tize Mha $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$\orcidE{}, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
+\Author{Pierre Tize Mha %MDPI: Please carefully check the accuracy of names and affiliations. O.P.: This is OK !
+ $^{1}$\orcidD{}, Prashant Dhondapure $^{2}$\orcidE{}, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Tize Mha, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.}
+\AuthorCitation{Tize Mha, %MDPI:  O.P.: OK
+ P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
-$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St.
-W., Montréal, QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
+\address{$^{1}$ \quad Laboratoire Génie de Production, Institut National Polytechnique/Ecole Nationale d'Ingénieurs de Tarbes,  %MDPI: please complete the address information and then check if the address order is correct.
+They should be arranged in ascending order
+ Université de Toulouse, 47 Avenue d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
+$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., %MDPI: Address OK
+ \mbox{Montreal, QC H3C 1K3, Canada}; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}
 
 % Contact information of the corresponding author
-\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562442933}
+\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562-442-933}
 
@@
 
-% Abstract (Do not insert blank lines, i.e. \\)
-\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process during hot-compressing steel.
-To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
-We also employed an artificial neural network (ANN) to model thermo-visco-plastic behavior with a flow law.
-The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
-This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations whereas the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
+% Abstract (Do not insert blank lines, i.e.,~\\)
+\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process while hot compressing steel.
+To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a \linebreak Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
+\linebreak We also employed an artificial neural network (ANN) to model the thermo-visco-plastic behavior with a flow law.
+The precision of quantifying the DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
+This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations, whereas the Johnson--Mehl--Avrami--Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
 A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
-The comparison revealed a strong correlation between simulation and experiment.
-The study investigated the impact of temperature, strain, and strain rate on DRX evolution.
-The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}
+The comparison revealed a strong correlation between the simulation and experiment.
+\linebreak The study investigated the impact of temperature, strain, and strain rate on DRX evolution.
+\linebreak The findings showed that DRX increases with rising temperature and strain but decreases with increasing strain rate.}
 
 % Keywords
-\keyword{Artificial Neural Network; Constitutive Flow Law; Gleeble simulator, Dynamic Recrystallization, Finite Element Analysis}
+\keyword{artificial neural network; constitutive flow law; Gleeble simulator; dynamic recrystallization; finite element analysis}
 
@@
 
-Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation.
-It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
-When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
+Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as~they undergo the process of plastic deformation.
+It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and~hot extrusion.
+\linebreak When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
 During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
-DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
+DRX differs from static recrystallization (SRX), which takes place when there is no deformation applied on the material.
 The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
-Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
+Typically, the~newly formed grains are much smaller than the original grains of the undeformed material.
 Their growth is accelerated by the stored energy and high temperatures.
-DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{Javidikia-2023, Shen-2021}.
-
-As the occurrence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
+DRX provides several benefits in the hot forming process by refining the grain size and enhancing the mechanical properties of the material, including strength and toughness~\cite{Javidikia-2023, Shen-2021}.
+
+As the occurrence of DRX softens the material, the~deformation loads during hot deformation must be adjusted from one pass to another to have a more accurate prediction of DRX.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
-However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
+However, the~extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and~strain.
 By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
-Various experimental techniques have been proposed by researchers to establish DRX's critical conditions such as metallographic analysis \cite{Babu-2022}.
+Various experimental techniques have been proposed by researchers to establish DRX's critical conditions, such as metallographic analysis~\cite{Babu-2022}.
 However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
-Additionally, the cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
+Additionally, the~cooling phase sometimes entails phase changes (depending on the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
 Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
 In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
-For instance, Yan Peng \eal \cite{Peng-2022} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate.
+For instance, Yan Peng \eal~\cite{Peng-2022} determined the critical strain and critical stress for DRX's initiation based on the method proposed by Najafizadeh and Jonas~\cite{Najafizadeh-2006} to establish a DRX kinetic model for hot-rolled conditions based on the relationship between the characteristic parameters of DRX and the temperature and strain rate.
 This approach defines the critical stress required for the initiation of DRX during deformation.
-According to Gottstein \eal \cite{Gottstein-2004}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
-The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.
-
-The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2}.
+According to Gottstein \eal~\cite{Gottstein-2004}, the~critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
+The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$, where $\sigma$ is the stress and $\varepsilon$ is the~strain.
+
+The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen~\cite{Ryan-1989, Ryan-1990, Ryan-1990-2}.
 They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
-Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combination between the current dislocations with the previous one leads to the DRX's initiation.
-Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
-Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
-Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
-This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
-Li \eal \cite{Li-2015} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{Estrin-1984,Mecking-1981} to determine the Avrami equation coefficients.
-
-Zhang \eal \cite{Zhang-2016} investigated the DRX behaviors of a medium carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
-They qualitatively characterized the metallurgical properties based on variations in the Zener-Hollomon parameter.
-Cho \eal \cite{Cho-2005} and Razali \eal \cite{Razali-2021} used a well-established model to predict the microstructure evolution of a Mn alloy, with a focus on DRX and grain growth phenomena.
-Their results showed consistency with multiple compression tests.
-Wan \eal \cite{Wan-2017} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
-Li \eal \cite{Li-2018} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
-Cui \eal \cite{Cui-2016} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple joints boundaries before affecting the lamellae.
-Recently, Chen \eal \cite{Chen-2023} conducted a Finite Element Analysis of DRX, based on GCr15 (52100 steel) microstructure analysis, and found that temperature and strain rate have a significant impact on DRX initiation.
+Later, Poliak and Jonas~\cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} confirmed the hypothesis of DRX, describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements; the combination of the current dislocations with the previous one leads to DRX's initiation.
+Najafizadeh and Jonas~\cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
+Their widely used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
+Once calculated, the~critical conditions serve as input data for the Johnson--Mehl--Avrami--Kolmogorov (JMAK) model~\cite{Avrami-1939}.
+This model is commonly used to estimate the volume fraction of dynamic recrystallization, $X_{drx}$, during hot working.
+\linebreak Li \eal~\cite{Li-2015} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model~\cite{Estrin-1984,Mecking-1981} to determine the Avrami equation~coefficients.
+
+Zhang \eal~\cite{Zhang-2016} investigated the DRX behaviors of a medium-carbon alloy (Cr-Ni-Mo steel) using the Avrami kinetics model equation.
+They qualitatively characterized the alloy's metallurgical properties based on variations in the Zener--Hollomon parameter.
+\linebreak Cho \eal~\cite{Cho-2005} and Razali \eal~\cite{Razali-2021} used a well-established model to predict the microstructure evolution of a Mn alloy with~a focus on DRX and grain growth phenomena.
+\linebreak Their results showed consistency with multiple compression tests.
+Wan \eal~\cite{Wan-2017} employed the same equation to predict the microstructure evolution of TiAl-based alloys during hot compression.
+\mbox{Li \eal~\cite{Li-2018}} validated the reliability of the Avrami kinetics model equation when testing the compression of Inconel 718 bolts.
+Cui \eal~\cite{Cui-2016} analyzed DRX by applying the Avrami kinetics model equation and discovered that the $\beta$-solidifying TiAl alloy usually started evolving at triple-joint boundaries before affecting the lamellae.
+\linebreak Recently, Chen \eal~\cite{Chen-2023} conducted a finite element analysis of DRX based on GCr15 (52100 steel) microstructure analysis and~found that temperature and strain rate have a significant impact on DRX~initiation.
 
 The precision of the critical DRX conditions is closely linked to the method of obtaining the curve $\theta(\sigma)$.
-Using experimental raw data directly does not yield functional curves, thus smoothing the $\sigma(\varepsilon)$ curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
+Using experimental raw data directly does not yield functional curves; thus, smoothing the $\sigma(\varepsilon)$ curve as much as possible or approximating it with a polynomial function that can reproduce the curve and deducing the $\theta(\sigma)$ curve from it is commonly used.
 The drawback of both of these methods is that they do not always ensure a satisfactory smoothing of the curve $\sigma(\varepsilon)$.
-Nevertheless, the Universal Approximator, Artificial Neural Networks (ANN), has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials like our previous work Tize Mha \eal \cite{TizeMha-2023} and many other works.
-Then the predictions of $\sigma(\varepsilon)$ are used as inputs for the $\theta(\sigma)$ prediction.
-Hence, this study offers a replacement of the two smoothing methods with an ANN approach to estimate the critical conditions for DRX.
-
-%----------------------------------------------------------------------------------
-\section{Materials and experiments}\label{sec:MaterialsExperiments}
-%----------------------------------------------------------------------------------
-
-The experimental tests used in this work are identical to those previously published by Tize Mha \eal \cite{TizeMha-2023}.
-For additional information, readers can refer to the publications by our research group \cite{Pantale-2021}.
-Nonetheless, we will outline the key aspects necessary to understand the suggested methodology.
-
-%----------------------------------------------------------------------------------
-\subsection{Experimental procedure and compression tests results}\label{subsec:ExperimentalProcedure}
-%----------------------------------------------------------------------------------
-
-The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
+Nevertheless, the~universal approximator capability %MDPI: OK
+of artificial neural networks (ANN) has demonstrated effectiveness in various domains, such as predicting the flow behavior of materials, as in our previous work Tize Mha \eal~\cite{TizeMha-2023} and many other works.
+Then, the predictions of $\sigma(\varepsilon)$ are used as inputs for the $\theta(\sigma)$ prediction.
+\linebreak Hence, this study offers a replacement of the two smoothing methods with an ANN approach to estimate the critical conditions for~DRX.
+
+%----------------------------------------------------------------------------------
+\section{Materials and~Experiments}\label{sec:MaterialsExperiments}
+%----------------------------------------------------------------------------------
+
+The experimental tests used in this work are identical to those previously published by Tize Mha \eal~\cite{TizeMha-2023}.
+For additional information, readers can refer to the publications by our research group~\cite{Pantale-2021}.
+Nonetheless, we will outline the key aspects necessary to understand the suggested~methodology.
+
+%----------------------------------------------------------------------------------
+\subsection{Experimental Procedure and Compression Test~Results}\label{subsec:ExperimentalProcedure}
+%----------------------------------------------------------------------------------
+
+The material used for this study is a medium-carbon steel with the chemical composition presented in Table~\ref{tab:Composition}.
 \begin{table}[H]
-\centering
-\caption{Chemical composition of medium carbon steel. Fe = balance.}
+\caption{Chemical composition of medium-carbon steel. Fe = balance.}
 \newcolumntype{L}{>{\raggedright\arraybackslash}X}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{LCCCCCCC}
+\begin{tabularx}{\textwidth}{lCCCCCCC}
 \toprule
 \textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
-\toprule
-\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
+\midrule
+Wt~\% %MDPI: Not necessary
+ & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
 \bottomrule
@@
 
-As detailed in Tize Mha \eal \cite{TizeMha-2023}, and reported in Figure \ref{fig:GleebleProcess}, hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
+As detailed in Tize Mha \eal~\cite{TizeMha-2023} and~reported in Figure~\ref{fig:GleebleProcess}, hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical~simulator.
 \begin{figure}[H]
@@
 \end{figure}
-The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
-The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
+The tests were conducted at 5 temperature levels (ranging from 1050 to 1250 $\celsius$) and 6~strain rates (ranging from $0.001$ to $5~\ps$).
+The imposed displacement was set to $d=9$~mm, resulting in a reduction of $60\%$ of the initial height.
+% O.P.
+a correction has been added here because of a mistake.
+The displacement is 60% and the remaining heigh is 40%
 To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
-In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
-They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
-During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
-Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.
-
-The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
-All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$ increments.
+In order to remove thermal gradients, the~samples were heated at a speed of~$2$~\celsius/s until they reached a temperature of 1260 $\celsius$, then held at that temperature for $5$~min.
+They were subsequently cooled down to the test temperature at a speed of $1$ \celsius/s and left at a consistent temperature for $1$~min prior to being formed.
+During compression, the~sample temperature was maintained at a constant level through the machine's thermal control system.
+Subsequently, the~structure was frozen at a fast pace in order to preserve the microstructure for future~analysis.
+
+The raw stress--strain data were exported from the Gleeble thermomechanical simulator as true stress and true strain, and~the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure~\ref{fig:RawData}.
+All stress--strain data are composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$ increments.
 \begin{figure}[H]
@@
 \includegraphics[width=0.9\columnwidth]{Figures/rawData}
-\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device for 5 temperatures ($T$) and 6 strain rates ($\mdot\varepsilon$).}
+\caption{Stress--strain curves of medium-carbon alloy extracted from the Gleeble device for \mbox{5 temperatures} ($T$) and 6 strain rates ($\mdot\varepsilon$).}
 \label{fig:RawData}
@@
 The flow stress ($\sigma$) increases as the strain rate ($\mdot\varepsilon$) rises but decreases as the temperature ($T$) increases.
-Notably, the strain also affects the flow stress.
-At the lowest strain rates, the flow stress increases up to $\sigma_p$ as the strain approaches a value of about $\varepsilon_p=0.2$ to $0.3$.
+Notably, the~strain also affects the flow stress.
+At the lowest strain rates, the~flow stress increases up to $\sigma_p$ as the strain approaches a value of about $\varepsilon_p=0.2$ to $0.3$.
 Then, it decreases to maintain a relatively constant value throughout the entire test.
-Conversely, at strain rates above $1~\ps$, the flow stress increases steadily throughout the test.
-The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
-Furthermore, this frictional effect becomes more apparent as lubrication reduces over time as reported in Tize Mha \eal \cite{TizeMha-2023}.
-
-The initial increase in stress seen during deformation up to $\varepsilon=0.1$ is believed to be due to work hardening (WH).
-After $\varepsilon=0.1$ up to $0.2$, the flow stress indicates a steady decrease as the stress level rises until a peak or inflection point is attained.
+Conversely, at~strain rates above $1~\ps$, the~flow stress increases steadily throughout the test.
+The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as~noted by \mbox{Galos \eal~\cite{Galos-2022}}.
+\linebreak Furthermore, this frictional effect becomes more apparent as lubrication reduces over time, as reported in Tize Mha \eal~\cite{TizeMha-2023}.
+
+\textls[-10]{The initial increase in stress seen during deformation up to $\varepsilon=0.1$ is believed to be due to work hardening (WH).
+Between $\varepsilon=0.1$ and $0.2$, the~flow stress indicates a steady decrease as the stress level rises until a peak or inflection point is attained.
 This peak suggests that thermal softening is now the predominant influence, overtaking work hardening.
-At this stage, the stress-strain curve displays three distinct patterns as strain increases.
-The first pattern is a gradual decrease to a steady state with DRV/DRX softening, which is observed at all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001~\ps$ to $0.1~\ps$, except at $1050\celsius$ and $1100\celsius$.
-The second pattern is higher stress levels without significant softening and work hardening at $1050\celsius$ and $1100\celsius$ with a strain rate of $0.1~\ps$.
+\linebreak At this stage, the~stress--strain curve displays three distinct patterns as strain increases.
+\linebreak The first pattern is a gradual decrease to a steady state with DRV/DRX softening, which is observed at all deformation temperatures and strain rates ranging from $\mdot\varepsilon=0.001$ to $0.1~\ps$, except~at 1050 $\celsius$ and 1100 $\celsius$.
+The second pattern is higher stress levels without significant softening and work hardening at 1050 $\celsius$ and 1100 $\celsius$ with a strain rate of $0.1~\ps$.
 The last pattern is a continuous increase with significant work hardening observed for all deformation temperatures and a strain rate above $1~\ps$.
@@
 The result is that both the peak stress $\sigma_p$ and the onset of steady-state flow occur at higher strain levels.
-The decrease in stress detected across all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is attributed to the event of dynamic recrystallization (DRX).
-
-%----------------------------------------------------------------------------------
-\subsection{DRX model's parameters identification}\label{subsec:DRXParameters}
+The decrease in stress detected across all temperatures and strain rates of $\mdot\varepsilon=0.001-5.0~\ps$ is attributed to the event of dynamic recrystallization (DRX).}
+
+%----------------------------------------------------------------------------------
+\subsection{Identification of DRX Model's Parameters}\label{subsec:DRXParameters}
 %----------------------------------------------------------------------------------
@@
 In this subsection we will determine the critical deformation required to initiate recrystallization.
-Ryan and McQueen \cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
-Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the start of DRX was attributed to this inflection point, and therefore the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$) respectively.
-Later, Poliak and Jonas \cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
-Najafizadeh and Jonas \cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
-Their widely-used approach adopts a $3^\text{rd}$ degree polynomial to describe the curve $\theta(\sigma)$, enabling the identification of critical stress and strain ($\sigma_c$ and $\varepsilon_c$) through the second derivative.
+Ryan and McQueen~\cite{Ryan-1989, Ryan-1990, Ryan-1990-2} were the pioneers in investigating this phenomenon.
+Observing the appearance of an inflection point on the curve $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ before the peak stress $\sigma_p$, the~start of DRX was attributed to this inflection point and,~therefore, the critical values of the strain ($\varepsilon_c$) and stress ($\sigma_c$), respectively.
+Later, Poliak and Jonas~\cite{Poliak-1996, Poliak-2003, Poliak-2003-2, Jonas-2003} demonstrated that this inflection point is associated with a release of thermodynamic free energy during dislocation motion, supporting the DRX hypothesis.
+Najafizadeh and Jonas~\cite{Najafizadeh-2006} developed an analytical technique to determine the critical conditions for DRX initiation, simplifying the thermodynamic model of Poliak and Jonas.
+Their widely used approach adopts a 3{rd} degree polynomial to describe the curve $\theta(\sigma)$, enabling the identification of critical stress and strain ($\sigma_c$ and $\varepsilon_c$) through the second~derivative.
 
 As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
-One challenge is calculating the derivative of stress versus strain values numerically, as compression test data exhibits oscillations, as depicted in Figure \ref{fig:RawData}.
+One challenge is calculating the derivative of stress versus strain values numerically, as~compression test data exhibit oscillations, as~depicted in Figure~\ref{fig:RawData}.
 It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.
 
-To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver \cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
-But, depending on the degree of the polynomial and for the same stress/strain curve, multiple solutions may be obtained.
+To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver~\cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
+\linebreak However, depending on the degree of the polynomial, for the same stress--strain curve, multiple solutions may be obtained.
 This results in multiple possible forms for the $\theta(\sigma)$ function.
@@
 %----------------------------------------------------------------------------------
-\subsubsection{ANN based filtering model's architecture}\label{subsec:ANNbasics}
+\subsubsection{ANN-Based Filtering Model's~Architecture}\label{subsec:ANNbasics}
 %----------------------------------------------------------------------------------
@@
 To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
-This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
+\linebreak This can be done by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
 In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
-Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
+Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$ containing $m$ neurons, given by the following~equation:
 \begin{equation}
@@
 \end{equation}
-where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
-Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
-For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
+where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and~$b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
+Those weights $w_{ij}$ and bias $b_i$, for~each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
+For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provided an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation~(\ref{eq:ANN1}) according to the following equation:
 \begin{equation}
@@
 
-No activation function was used for the output neuron of the ANN, as is typically omitted in regression applications.
-The chosen architecture for our application consists of two hidden layers, one with 7 neurons and the other with 5 neurons, as illustrated in Figure \ref{fig:ANN-7-5}.
-To calculate the number of internal parameters $N_{int}$ in the model, where $n$ and $m$ represent the number of neurons in the first and second hidden layers, respectively, the following formula may be used: $N_{int}=m(2+n)+2n+1$.
-So that for a $7-5$ network, $N_{int}=60$.
+No activation function was used for the output neuron of the ANN, as~is typically omitted in regression applications.
+The chosen architecture for our application consists of two hidden layers, one with 7 neurons and the other with 5 neurons, as~illustrated in Figure~\ref{fig:ANN-7-5}.
+To calculate the number of internal parameters $N_{int}$ in the model, where $n$ and $m$ represent the number of neurons in the first and second hidden layers, respectively, the~following formula may be used: $N_{int}=m(2+n)+2n+1$.
+
+Thus, for a $7-5$ network, $N_{int}=60$.
 \begin{figure}[H]
@@
 \includegraphics[width=0.7\columnwidth]{Figures/ANN-7-5}
-\caption{Two hidden layers artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
+\caption{Two-hidden-layer artificial neural network architecture with 1 input neuron (green) and 1 output neuron (red).}
 \label{fig:ANN-7-5}
 \end{figure}
-The Python program used for training the neural network was created with the dedicated Python library, Tensorflow \cite{Abadi-2016}.
-The training phase employed the Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015}.
-The training was conducted using $50,000$ epochs of the experimental dataset.
-It took approximately 15 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor until the converged parameters were obtained.
-
-%----------------------------------------------------------------------------------
-\subsubsection{ANN filtering based model's application} \label{subsec:ANNapplication}
-%----------------------------------------------------------------------------------
-
-Since the dynamic recrystallization phenomenon only occurs for strain rates between $0.001~\ps$ and $1.0~\ps$, we will use only the first 20 stress/strain curves to identify the DRX critical parameters.
-Each of these 20 curves consists of 701 pairs of strain-stress values and was independently processed by a neural network, resulting in the identification of 20 networks.
-As an example, Figure \ref{fig:AnnFit} displays the stress/strain curve experimental values for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (in blue) and the neural network results identified from this data (in red).
+The Python program used for training the neural network was created with the dedicated Python library, Tensorflow~\cite{Abadi-2016}.
+The training phase employed the Adaptive Moment Estimation (ADAM) optimizer~\cite{Kingma-2015}.
+The training was conducted using 50,000~epochs of the experimental dataset.
+It took approximately 15 min to train the ANN model and obtain the converged parameters on a Dell XPS-13 7390 %MDPI: Manufacturer Dell, City Toulouse, Country France.
+I don't know how to add it to the text.
+ laptop running Ubuntu 22.04 LTS 64-bit with 16 GB of RAM and an Intel 4-core i7-10510U processor.
+
+%----------------------------------------------------------------------------------
+\subsubsection{ANN-Based Filtering Model's~Application} \label{subsec:ANNapplication}
+%----------------------------------------------------------------------------------
+
+Since the dynamic recrystallization phenomenon only occurs for strain rates between $0.001~\ps$ and $1.0~\ps$, we used only the first 20 stress--strain curves to identify the critical DRX parameters.
+Each of these 20 curves consisted of 701 pairs of strain--stress values and was independently processed by a neural network, resulting in the identification of 20~networks.
+As an example, Figure~\ref{fig:AnnFit} displays the stress--strain curve experimental values for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$ (in blue) and the neural network results identified from these data (in red).
 
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
-\caption{Filtering of the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
+\caption{Filtering of the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
 \label{fig:AnnFit}
 \end{figure}
-The models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as defined by the following equation:
+\textls[-15]{A models' accuracy and predictive ability are typically evaluated using specific coefficients, such as the mean absolute relative error ($\MARE$), as~defined by the following equation:}
 \begin{equation}
@@
 \end{equation}
-and the root-mean-squared error ($\RMSE$) defined by the following equation:
+and the root-mean-squared error ($\RMSE$), as defined by the following equation:
 \begin{equation}
@@
 \end{equation}
-where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and $N$ is the total number of data points used to compute those coefficients.
-For the proposed ANN filter $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a $11^{th}$ order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.
-
-It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an $11^{th}$ order polynomial fit, as demonstrated by the lower estimated error.
-Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrate the stress change rate relative to strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
-An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure \ref{fig:AnnTheta}.
+where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value of the stress $\sigma$ predicted using the given model, and~$N$ is the total number of data points used to compute those coefficients.
+\linebreak For the proposed ANN filter, $\RMSE=0.093~\MPa$ and $\MARE=0.231~\%$, while using a 11{th} order polynomial fit of the experimental data leads to $\RMSE=0.120~\MPa$ and $\MARE=0.275~\%$.
+
+It is evident that using the ANN model to depict the $\sigma(\varepsilon)$ curve is superior to using an 11{th}-order polynomial fit, as~demonstrated by the lower estimated error.
+Thus, this architecture of the ANN model is used for all subsequent curves, resulting in the deduction of the hardening curves, which illustrates the stress change rate relative to the strain ($\frac{\partial \sigma}{\partial \varepsilon}$).
+\linebreak An illustration of computing the hardening curve $\theta(\sigma)$ for a single temperature is displayed in Figure~\ref{fig:AnnTheta}.
 The blue line represents the direct calculation of the derivative of the raw stress versus strain, whereas the red line represents the derivative of the stress filtered by the neural network versus strain.
-An overview of the remaining temperatures can be found in Figure \ref{fig:nThetaOP}.
-The identical process applies to all 20 stress/strain curves.
-These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent analysis.
+An overview of the remaining temperatures can be found in Figure~\ref{fig:nThetaOP}.
+The identical process applies to all 20 stress--strain curves.
+These curves deliver essential data regarding the critical stresses and strains required for predicting DRX in the subsequent~analysis.
 
@@
 \includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
-\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress/strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050\celsius$.}
+\caption{Computation of the hardening curve $\theta(\sigma)$ from the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
 \label{fig:AnnTheta}
 \end{figure}
+\unskip
 
@@
 \includegraphics[width=0.99\columnwidth]{Figures/nThetaOP}
-\caption{Work hardening computation for one strain rate and five temperatures.}
+\caption{Work hardening computation for one strain rate and five~temperatures.}
 \label{fig:nThetaOP}
 \end{figure}
-
-%----------------------------------------------------------------------------------
-\subsubsection{Critical conditions evaluation}\label{subsec:CrConditions}
+\unskip
+
+%----------------------------------------------------------------------------------
+\subsubsection{Evaluation of the Critical Conditions}\label{subsec:CrConditions}
 %----------------------------------------------------------------------------------
@@
 The identification of these critical conditions is a difficult task that calls for the creation of models that can compute the corresponding critical stress and strain.
-Consequently, the Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} method, which is currently well-regarded, will be used in this investigation.
-The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure \ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
-The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those curves.
+Consequently, the~Poliak and Jonas~\cite{Poliak-1996,Poliak-2003,Poliak-2003-2,Jonas-2003} method, which is currently well-regarded, will be used in this investigation.
+The method uses a third-degree polynomial function to describe the $\theta(\sigma)$ and $\ln \theta(\varepsilon)$ curves reported in Figure~\ref{fig:nThetaOP} for $\mdot\varepsilon=0.001~\ps$.
+The objective is to locate the inflection points connected to the critical stress $\sigma_c$ and critical strain $\varepsilon_c$, as~well as to extract the peak stress $\sigma_p$ and peak strain $\varepsilon_p$ from those~curves.
 
 The determination of critical values is carried out in two consecutive steps for each of the curves.
-Firstly, based on the definition of the $\theta(\sigma)$ curve as depicted in Figure \ref{fig:nThetaOP}, we use the polyfit method from the numpy library to determine the optimal values of the constants $a_i$ for a third-degree polynomial function $p(\sigma)$ approximating $\theta(\sigma)$:
+Firstly, based on the definition of the $\theta(\sigma)$ curve as depicted in Figure~\ref{fig:nThetaOP}, we use the polyfit method from the numpy library to determine the optimal values of the constants $a_i$ for a third-degree polynomial function $p(\sigma)$ approximating $\theta(\sigma)$:
 \begin{equation}
@@
 \end{equation}
-Secondly, the inflection point $\sigma_c$ can be obtained from the second derivative of $p(\sigma)$ with:
+
+Secondly, %MDPI: Yes
+ the~inflection point $\sigma_c$ can be obtained from the second derivative of $p(\sigma)$ with:
 \begin{equation}
@@
 \end{equation}
-Similarly, the critical strain ($\varepsilon_c$) is calculated by defining a third-degree polynomial function $q(\sigma)$ approximating the $\ln \theta(\varepsilon)$ curve as depicted in Figure \ref{fig:nThetaOP}:
+Similarly, %MDPI:  Ok
+ the~critical strain ($\varepsilon_c$) is calculated by defining a third-degree polynomial function $q(\sigma)$ approximating the $\ln \theta(\varepsilon)$ curve as depicted in Figure~\ref{fig:nThetaOP}:
 \begin{equation}
@@
 \end{equation}
-This later gives the critical strain $\varepsilon_c$ from $\varepsilon_c = -b_1/3b_0$.
-Applying the identical method to the first four strain rates and all temperatures, Table \ref{tab:OPparams} summarizes the critical stress and strain, peak stress, and peak strain.
-Once the critical DRX conditions are established, they can be used as input to determine the DRX volume fraction, which will be discussed in the following section.
-
-\begin{table}[h!]
-\centering
+
+This %MDPI: OK
+ later gives the critical strain $\varepsilon_c$ from $\varepsilon_c = -b_1/3b_0$.
+Applying the identical method to the first four strain rates and all temperatures, Table~\ref{tab:OPparams} summarizes the critical stress and strain, peak stress, and~peak strain.
+Once the critical DRX conditions are established, they can be used as input to determine the DRX volume fraction, which will be discussed in the following~section.
+
+\begin{table}[H]
 \caption{Critical conditions based on the proposed approach.}\vspace{-1mm}
+\setlength{\tabcolsep}{6.1mm}
 \begin{tabular}{cccccc}
 \toprule
-$\mdot{\varepsilon}$ ($\ps$) & $T$ (\celsius) & $\varepsilon_p$ & $\sigma_p$ (MPa) &  $\varepsilon_c$ & $\sigma_c$ (MPa) \\
-\toprule
+\boldmath{$\mdot{\varepsilon}$} \textbf{(}\boldmath{$\ps$}\textbf{)} & \boldmath{$T$} \textbf{(\celsius)} & \boldmath{$\varepsilon_p$} & \boldmath{$\sigma_p$} \textbf{(MPa)} &  \boldmath{$\varepsilon_c$} & \boldmath{$\sigma_c$} \textbf{(MPa)} \\
+\midrule
  & $1050$ & $0.178$ & $37.862$ & $0.083$ & $33.050$\\
@@
  & $1250$ & $0.084$ & $13.883$ & $0.035$ & $11.302$\\
-\hline
+\midrule
  & $1050$ & $0.281$ & $57.915$ & $0.131$ & $51.602$\\
@@
  & $1250$ & $0.139$ & $24.739$ & $0.051$ & $20.004$\\
-\hline
+\midrule
  & $1050$ & $0.571$ & $91.413$ & $0.244$ & $83.814$\\
@@
  & $1250$ & $0.259$ & $40.195$ & $0.119$ & $35.277$\\
-\hline
+\midrule
  & $1050$ & $0.700$ & $127.17$ & $0.577$ & $116.10$\\
@@
 %----------------------------------------------------------------------------------
-\subsection{DRXmodel parameters evaluation}\label{subsec:DRXparams}
-%----------------------------------------------------------------------------------
-
-The DRX process commences at a critical deformation, as previously noted.
-The degree of recrystallization can be determined through experimental means.
-%Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence \cite{Wan-2017}.
+\subsection{Evaluation of the DRX Model's Parameters}\label{subsec:DRXparams}
+%----------------------------------------------------------------------------------
+
+The DRX process commences at a critical deformation, as~previously noted.
+\linebreak The degree of recrystallization can be determined through experimental means.
+%Figure \ref{fig:DRXschema} depicts three phases of recrystallization: nucleation, grain growth, and grain coalescence~\cite{Wan-2017}.
 %\begin{figure}[!ht]
@@
 %\end{figure} 
-For some visual representation of microstructure evolution during DRX, the interested reader can refer to Chen \eal \cite{Chen-2019}.
+For a visual representation of microstructure evolution during DRX, the~interested reader can refer to Chen \eal~\cite{Chen-2019}.
 
 The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
-The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{Avrami-1939} , commonly known as the JMAK model, expressed by the following equation:
+The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model~\cite{Avrami-1939}, commonly known as the JMAK model, expressed by the following equation:
 \begin{equation}
-X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
+X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right],
 \label{eq:drxpred}
 \end{equation}
-With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
+with %MDPI: OK, comma added
+ $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain, respectively.
+$k$ and $n_k$ are the model's parameters, and the experimental equivalence of this volume fraction of DRX is given by
 \begin{equation}
@@
 \end{equation}
-
-Where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress respectively.
-The steady stress is considered as the minimum one after the peak stress.
-It is possible to establish a dependency relationship between these specific stresses/strains and the Zener-Hollomon \cite{Zenner-1944} parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, (where $Q$ is the effective activation energy parameter $Q=437.4~\text{kJ/mol}$, $R$ is the universal gas constant $R=8.314~\text{J/mol/K}$), according to the following equation reported by other researchers such as \cite{Chen-2014,Li-2019,Wang-2021} for similar steel compositions and deformation conditions:
+where $\sigma_p$ and $\sigma_s$ are the peak stress and the steady stress after the peak stress, respectively.
+The steady stress is considered the minimum value after the peak stress.
+It is possible to establish a dependency relationship between these specific stresses and strains and the Zener--Hollomon~\cite{Zenner-1944} parameter $Z = \mdot\varepsilon \exp{\left(\frac{Q}{RT}\right)} \label{eq:ArZ}$, (where $Q$ is the effective activation energy parameter $Q=437.4~\text{kJ/mol}$ and $R$ is the universal gas constant $R=8.314~\text{J/mol/K}$), according to the following equation reported by other researchers such as~\cite{Chen-2014,Li-2019,Wang-2021} for similar steel compositions and deformation conditions:
 \begin{equation}
@@
 \end{equation}
-with the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and $m_s$, the specific strains and stresses' dependency on the Zener-Hollomon parameter whose identification is described here after.
-The procedure for determining of the value of $Q$ is detailed in \cite{TizeMha-2023}.
-
-The JMAK model's parameter identification involves two main steps, starting with determining the 10 coefficients $A$, $n$, $B$, and $m$.
-Secondly, those coefficients are integrated into equation (\ref{eq:paramsZ}) to be used in equations (\ref{eq:drxpred}) and (\ref{eq:drxexp}).
-To calculate these parameters, the curve\_fit method of the scipy library is employed through a Python code.
-These parameter identifications use the critical strains and stresses computed in the preceding sections as input data.
+with the parameters $A_c$, $A_p$, $n_c$, $n_p$, $B_c$, $B_p$, $B_s$, $m_c$, $m_p$, and~$m_s$, which are %MDPI: OK
+the~specific strains and stresses' dependency on the Zener--Hollomon parameter, whose identification is described hereafter.
+The procedure for determining the value of $Q$ is detailed in~\cite{TizeMha-2023}.
+
+The JMAK model's parameter identification involves two main steps, starting with determining the 10 coefficients $A$, $n$, $B$, and~$m$.
+Secondly, those coefficients are integrated into Equation~(\ref{eq:paramsZ}) to be used in Equations~(\ref{eq:drxpred}) and (\ref{eq:drxexp}).
+To calculate these parameters, the~curve\_fit method of the scipy library is employed through a Python code.
+\linebreak These parameter identifications use the critical strains and stresses computed in the preceding sections as input data.
 The curve-fitting method seeks to obtain optimal values for the coefficients by iteratively adjusting them to minimize the gap between predicted and actual critical strains and stresses.
 This optimization process entails experimenting with different combinations of coefficients and assessing their appropriateness for the provided data.
-The curve-fitting technique fine-tunes coefficients until it attains the most accurate match between the model's forecasts and the experimental data.
-
-Once the calculation of the constants that define the dependency of the Zener-Hollomon parameter is completed, an optimization technique can be employed to deduce the JMAK model parameters while minimizing the error between the predicted recrystallization $X_{drx}^{p}$ and the experimental value $X_{drx}^{e}$.
-Table \ref{tab:allparams} displays the dependency of both the Zener-Hollomon parameters and the JMAK model parameters.
-
-\begin{table}[h]
-\centering
-\caption{JMAK model and Zener-Hollomon dependency parameters.}\vspace{-1mm}
+The curve-fitting technique fine-tunes coefficients until it attains the most accurate match between the model's forecasts and the experimental~data.
+
+Once the calculation of the constants that define the dependency of the Zener--Hollomon parameter is completed, an~optimization technique can be employed to deduce the JMAK model parameters while minimizing the error between the predicted recrystallization $X_{drx}^{p}$ and the experimental value $X_{drx}^{e}$.
+Table~\ref{tab:allparams} displays the dependency of both the Zener--Hollomon parameters and the JMAK model's~parameters.
+
+\begin{table}[H]
+\caption{JMAK model and Zener--Hollomon dependency parameters.}\vspace{-1mm}
+\setlength{\tabcolsep}{3.6mm}
 \begin{tabular}{cccccc}
 \toprule
-$A_c$ & $A_p$& $B_c$& $B_p$& $B_s$& $n_c$ \\
-\hline
+\boldmath{$A_c$} & \boldmath{$A_p$}& \boldmath{$B_c$}& \boldmath{$B_p$}& \boldmath{$B_s$}& \boldmath{$n_c$} \\
+\midrule
 $4.4268\times10^{-5}$& $29.85\times10^{-5}$& $0.0720627$&$0.103141$&$10265.8$&$0.235832$\\
@@
 $n_p$ & $m_c$& $m_p$& $m_s$& $k$& $n_k$ \\
-\hline
+\midrule
 $0.203678	$& $0.188236$&$0.181822$&$-0.19708$&$0.48632$&$3.36531$\\
@@
 
-The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C).
+The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure~\ref{fig:nDRX}, where a comparison between the experimental and predicted values is made for the strain rate $\mdot\varepsilon=0.001~\ps$ and three temperatures (1050 $^\circ$C, 1150 $^\circ$C and 1250 $^\circ$C).
 \begin{figure}[H]
@@
 	\includegraphics[width=0.99\columnwidth]{Figures/nDRX1}
-	\caption{DRX experimental data (dots) and JMAK model based prediction (plain lines).}
+	\caption{DRX experimental data (dots) and JMAK model-based prediction (plain lines).}
 	\label{fig:nDRX}
 \end{figure}
-Figure \ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.
-From this later, we determined the location of one of experimental point in Figure \ref{fig:nDRX} (the red one for $\varepsilon=0.55$).
-The same approach using different temperatures and strains is used to obtain the other experimental points reported in Figure \ref{fig:nDRX}.
+Figure~\ref{fig:eDRX} shows a micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, T = 1050 $^\circ$C, and $\varepsilon=0.55$.
+From~this, we determined the location of one experimental point in Figure~\ref{fig:nDRX} (the red one for $\varepsilon=0.55$).
+The~same approach using different temperatures and strains was used to obtain the other experimental points reported in Figure~\ref{fig:nDRX}.
 \begin{figure}[H]
@@
 	\includegraphics[width=0.5\columnwidth]{Figures/micrograph}
-	\caption{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050^\circ$C and $\varepsilon=0.55$.}
+	\caption{Micrograph of the sample for $\mdot\varepsilon=0.001~\ps$, $T=1050~^\circ$C, and $\varepsilon=0.55$.}
 	\label{fig:eDRX}
 \end{figure}
-The curves illustrate the changes in predicted volume fractions of DRX with plastic strain and it is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
-The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
-At a constant temperature and strain, the DRX volume fraction increases with decreasing strain rate.
-Conversely, at a fixed strain rate and strain, the DRX volume fraction increases with rising temperature.
+
+The curves illustrate the changes in the predicted volume fractions of DRX with plastic strain, and it is evident that the proportion of DRX is strongly affected by strain, temperature, and~strain rate values.
+The DRX kinetics exhibit an S-shaped curve, with~the DRX volume fraction gradually increasing with strain.
+At a constant temperature and strain, the~DRX volume fraction increases with decreasing strain rate.
+Conversely, at~a fixed strain rate and strain, the~DRX volume fraction increases with rising temperature.
 The difference between the predicted and experimental volume fractions of DRX is insignificant, confirming the suitability of the proposed approach for DRX prediction in the studied superalloy under various forming conditions.
-The reduction of DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to forming temperature and strain rate.
+The reduction in DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to the forming temperature and strain rate.
 Dynamic recrystallization is prone to occur at high forming temperatures and low strain rates due to increased grain boundary mobility.
-However, because of the limited mobility of grain boundaries, the rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
-The validation of the model used in the study, as evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation section.
-
-%----------------------------------------------------------------------------------
-\section{Numerical simulation of the compression}\label{sec:NumSim}
+\linebreak However, because~of the limited mobility of grain boundaries, the~rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
+The validation of the model used in the study, as~evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation~section.
+
+%----------------------------------------------------------------------------------
+\section{Numerical Simulation of the~Compression}\label{sec:NumSim}
 %----------------------------------------------------------------------------------
@@
 This requires establishing a constitutive law capable of accurately predicting the material's plastic deformation.
-In our previous publication (Tize Mha \eal \cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
+In our previous publication (Tize Mha \eal~\cite{TizeMha-2023}), we conducted a comparison between analytical constitutive laws and a neural network-based approach.
 The results revealed an artificial neural network model as the most appropriate option for this material.
-As a result, this section has two main focuses: first, a summary of the ANN-based constitutive law identification, as previously presented; and second, the incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization behavior.
-
-%----------------------------------------------------------------------------------
-\subsection{Identification of the ANN constitutive law}\label{subsec:ANNConstitutiveLaw}
-%----------------------------------------------------------------------------------
-
-In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
+As a result, this section has two main focuses: first, a~summary of the ANN-based constitutive law identification, as~previously presented; and second, the~incorporation of this identified ANN model with the JMAK model to predict dynamic recrystallization~behavior.
+
+%----------------------------------------------------------------------------------
+\subsection{Identification of the ANN Constitutive~Law}\label{subsec:ANNConstitutiveLaw}
+%----------------------------------------------------------------------------------
+
+In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$ but~decreasing with increasing temperature $T$.
 This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
-This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{TizeMha-2023} or Arrhenius \cite{Sellars-1966} flow law type.
-Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
-
-As stated in the research conducted by Tize Mha \eal \cite{TizeMha-2023}, the Johnson--Cook, Zerilli--Armstrong, or Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as presented in Figure \ref{fig:RawData}.
-Indeed, at the lowest strain rates, the flow stress $\sigma$ increases with strain $\varepsilon$ until reaching a value of roughly $\varepsilon=0.2$ to $0.3$.
+This type of behavior generally leads to Johnson--Cook~\cite{Johnson-1983}, Zerilli--Armstrong~\cite{Zerilli-1987}, Hansel--Spittel~\cite{Hensel-1978}, PTM~\cite{TizeMha-2023}, or Arrhenius~\cite{Sellars-1966} flow law type.
+Depending on the nature of the stress--strain relationship, modeling with one or another of these models can take into account the actual behavior of the material at certain strain~rates.
+
+As stated in the research conducted by Tize Mha \eal~\cite{TizeMha-2023}, the~Johnson--Cook, Zerilli--Armstrong, or~Hansel--Spittel models provide an estimate of material behavior at strain rates exceeding $1~\ps$, but~they neglect the softening due to DRX that is evident on experimental curves for strain rates below $1~\ps$, as~presented in Figure~\ref{fig:RawData}.
+Indeed, at~the lowest strain rates, the~flow stress $\sigma$ increases with strain $\varepsilon$ until it reaches a value of roughly $\varepsilon=0.2$ to $0.3$.
 Afterward, it decreases, maintaining a relatively constant value until the end of the compression test.
 The Arrhenius model is the only one that can somewhat explain this softening at low strain rates.
-As proposed by Pantalé \eal \cite{Pantale-2021} and Tize Mha \eal \cite{TizeMha-2023}, an effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
-Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression tests.
-
-According to the method proposed by Pantalé \eal \cite{Pantale-2021}, we have developed a two-hidden-layer artificial neural network based flow law in Tize Mha \eal \cite{TizeMha-2023}.
-Figure \ref{fig:ANN-2HL} shows the general structure of this ANN.
-The input layer of the ANN consists of three neurons that correspond to the model inputs, which are $\varepsilon$, $\mdot\varepsilon$, and $T$.
+As proposed by Pantalé \eal~\cite{Pantale-2021} and \mbox{Tize Mha \eal~\cite{TizeMha-2023},} an~effective alternative is to use a flow law defined by an artificial neural network trained directly on experimental data from compression tests.
+Properly defining the hyper-parameters of this neural network, such as the number of hidden layers, number of neurons, and~activation functions, enables us to obtain a flow law that accurately replicates the data acquired from compression~tests.
+
+According to the method proposed by Pantalé \eal~\cite{Pantale-2021}, we have developed a two-hidden-layer artificial neural network-based flow law in Tize Mha \eal~\cite{TizeMha-2023}.
+Figure~\ref{fig:ANN-2HL} shows the general structure of this ANN.
+The input layer of the ANN consists of three neurons that correspond to the model inputs, which are $\varepsilon$, $\mdot\varepsilon$, and~$T$.
 The output layer of the ANN contains one neuron representing $\sigma$, while there are two hidden layers.
-All details regarding the artificial neural network, experimental data setup, and training method are detailed in the paper proposed by Pantalé \eal \cite{Pantale-2021}.
-
+All details regarding the artificial neural network, experimental data setup, and~training method are detailed in the paper proposed by Pantalé \eal~\cite{Pantale-2021}.
+
+We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
+The training database, as~described in \mbox{Section~\ref{subsec:ExperimentalProcedure}}, contains 21,030 quadruples (we have $701\times30$ quadruples because $\varepsilon\in[0,0.7]$ with an increment of $0.001$, so we have $701$ values and 30 data curves) of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and~stress ($\sigma$).
 \begin{figure}[H]
@@
 \includegraphics[width=0.55\columnwidth]{Figures/ANN-scheme-2HL}
-\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
+\caption{Two-hidden-layer artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
 \label{fig:ANN-2HL}
@@
 
-We again used the Tensorflow library to develop the training program and employed the ADAM optimizer for the training phase.
-The training database, as described in Section \ref{subsec:ExperimentalProcedure}, contains $21,030$ quadruples (we have $701\times30$ quadruples because $\varepsilon\in[0,0.7]$ with an increment of $0.001$, so we have $701$ values and 30 data curves) of values for strain ($\varepsilon$), strain rate ($\mdot\varepsilon$), temperature ($T$), and stress ($\sigma$).
-
-We selected six different networks, named 3-$n$-$m$-1, where $n$ represents the number of neurons in the first hidden layer and $m$ indicates the number of neurons in the second hidden layer to demonstrate the significance of choosing the appropriate number of neurons in these two layers.
-
-The training was conducted based on $5,000$ epochs of the experimental dataset.
-It took 40 minutes to train the ANN model on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit operating system with 16 GB of RAM and an Intel 4-core i7-10510U processor until obtaining the converged parameters.
-
-Figure \ref{fig:ANN-conv} shows the evolution of the training error, defined by the $\log_{10}$ of the internal $\RMSE$, during the training phase.
-Table \ref{tab:Errors} summarizes the final values of this criterion, as well as the final values of the $\MARE$ and the $\RMSE$ for all six neural network configurations.
-Based on these results, the 3-15-7-1 network was chosen for further investigation.
-This network exhibited the most efficient convergence and achieved the lowest final error values of $\MARE=0.62\%$ and $\RMSE=0.38~\MPa$, while also maintaining a reasonable number of internal parameters ($N_{int}=180$).
+We selected six different networks, named 3-$n$-$m$-1, where $n$ represents the number of neurons in the first hidden layer and $m$ indicates the number of neurons in the second hidden layer, to demonstrate the significance of choosing the appropriate number of neurons in these two~layers.
+
+The training was conducted based on 5000 epochs of the experimental dataset.
+It took 40 min to train the ANN model and obtain the converged parameters on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64-bit operating system with 16 GB of RAM and an Intel 4-core i7-10510U processor.
+
+Figure~\ref{fig:ANN-conv} shows the evolution of the training error, defined by the $\log_{10}$ of the internal $\RMSE$, during~the training phase.
+Table~\ref{tab:Errors} summarizes the final values of this criterion, as~well as the final values of the $\MARE$ and the $\RMSE$ for all six neural network configurations.
+\linebreak Based on these results, the~3-15-7-1 network was chosen for further investigation.
+\linebreak This network exhibited the most efficient convergence and achieved the lowest final error values of $\MARE=0.62\%$ and $\RMSE=0.38~\MPa$ while also maintaining a reasonable number of internal parameters ($N_{int}=180$).
+The global performance of the model is illustrated in Figure \ref{fig:ANN-3-15-7-1}. % Added missing figure refernec in the text
 
@@
 \includegraphics[width=0.7\columnwidth]{Figures/Conv-ANN-6}
-\caption{Evolution of the convergence of the models during the training procedure for the 6 proposed network architectures.}
+\caption{Evolution of the convergence of the models during the training procedure for the \mbox{6 proposed} network~architectures.}
 \label{fig:ANN-conv}
 \end{figure}
+\unskip
 
 \begin{table}[H]
-\caption{Architecture and accuracy coefficients for all the proposed networks.}
+\caption{Architecture and accuracy coefficients for all the proposed~networks.}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 \textbf{Coefficients} & \textbf{3-7-5-1} & \textbf{3-9-4-1} & \textbf{3-9-5-1} & \textbf{3-9-7-1} & \textbf{3-13-7-1} & \textbf{3-15-7-1} \\
-\toprule
+\midrule
 $N_{int}$ & $74$ & $81$ & $92$ & $114$ & $158$ &$180$\\
-\hline
+\midrule
 $\log_{10}(\RMSE)$ & $-2.40$ & $-2.42$ & $-2.38$ & $-2.45$ & $-2.50$ & $-2.58$ \\
@@
 \end{table}
+\unskip
 
@@
 \includegraphics[width=0.9\columnwidth]{Figures/CompExpANN-3-15-7-1}
-\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma$ by the 3-15-7-1 ANN model.}
+\caption{Comparison %MDPI: Figure citation has been added in the text some lines above here.
+ between the experimental (dots) and predicted (lines) flow stresses $\sigma$ by the 3-15-7-1 ANN~model.}
 \label{fig:ANN-3-15-7-1}
 \end{figure}
-This model will serve as the material flow equation for the numerical simulations discussed in Section \ref{subsec:DRXSimulation}.
-Once the neural network is trained and a stable solution is obtained, it is re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
-The details of the procedure and complete equations set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$ and $T$ can be found in \cite{Pantale-2021}.
-
-%----------------------------------------------------------------------------------
-\subsection{Dynamic recrystallization simulation}\label{subsec:DRXSimulation}
+This model will serve as the material flow equation for the numerical simulations discussed in Section~\ref{subsec:DRXSimulation}.
+Once the neural network was trained and a stable solution was obtained, it was re-implemented as a Fortran 77 VUHARD subroutine to calculate the material flow stress in the Abaqus FEM code.
+The~details of the procedure and complete equation set required to calculate the flow stress $\sigma$ and the three derivatives of the flow stress with respect to $\varepsilon$, $\mdot{\varepsilon}$, and $T$ can be found in~\cite{Pantale-2021}.
+
+%----------------------------------------------------------------------------------
+\subsection{Dynamic Recrystallization~Simulation}\label{subsec:DRXSimulation}
 %----------------------------------------------------------------------------------
@@
 To evaluate the effectiveness of the DRX model presented earlier, we propose a numerical simulation of a compression test in this section.
-Our simulation concerns a medium-carbon P20 iron alloy, the same material used for the model's identification.
-An axisymmetric Finite Element (FE) model of hot cylinder compression with a height of $h=15$~mm and a diameter of $\phi=10$~mm is used, as shown in Figure \ref{fig:Mesh}.
-The assumed friction coefficient at the material/die interface is $\mu=0.2$ \cite{Zhang-2019,Sun-2020}.
-The mesh is composed of $986$ ($17\times58$) CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
-Abaqus/Implicit is used to run the FE model simulation because of the long time needed to simulate a low strain rate compression.
-A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ of the total height is imposed on the upper part of the cylinder along the vertical axis of the specimen during compression.
+Our simulation concerns a medium-carbon P20 iron alloy, the~same material used for the model's identification.
+\linebreak An axisymmetric finite element (FE) model of hot cylinder compression with a height of $h=15$~mm and a diameter of $\phi=10$~mm was used, as~shown in Figure~\ref{fig:Mesh}.
+The assumed friction coefficient at the material/die interface was $\mu=0.2$ \cite{Zhang-2019,Sun-2020}.
+The mesh was composed of $986$ ($17\times58$) CAX4R elements (4-node axisymmetric bi-linear quadrilateral elements with reduced integration and hourglass control).
+Abaqus/Implicit was used to run the FE model simulation because of the long time needed to simulate a low strain rate compression.
+\linebreak A displacement of $60\%, ~45\%, ~30\%$ and $15\%$ of the total height was imposed on the upper part of the cylinder along the vertical axis of the specimen during compression.
 The upper and the lower parts of the specimen can slip in the radial direction according to the friction coefficient and the contact conditions.
-The axial displacement ($u_z$) of the upper part is imposed with a fixed velocity while the axial displacement of the lower part remains fixed during the simulation.
-The simulation evaluated the impact of reducing the cylinder height with the effects of strain rate and temperature.
+The axial displacement ($u_z$) of the upper part was imposed with a fixed velocity, while the axial displacement of the lower part remained fixed during the simulation.
+The simulation evaluated the impact of reducing the cylinder height on the effects of strain rate and temperature.
 Conclusions were drawn based on this analysis.
-The simulation considered three temperatures ($1050\degree$C, $1150\degree$C, and $1250\degree$C) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$, and $1.0~\ps$).
+The simulation considered three temperatures (1050 $\degree$C, 1150 $\degree$C, and~$1250~\degree$C) and four strain rates ($0.001~\ps$, $0.01~\ps$, $0.1~\ps$, and~$1.0~\ps$).
 \begin{figure}[H]
@@
 \includegraphics[height=0.7\columnwidth]{Figures/CyCompression2}
-\caption{Numerical FE model for the simulation of the compression test.}
+\caption{Numerical FE model for the simulation of the compression~test.}
 \label{fig:Mesh}
 \end{figure}
-
-%----------------------------------------------------------------------------------
-\subsubsection{Temperature and strain rate effects}\label{subsec:TempSReffect}
+\unskip
+
+%----------------------------------------------------------------------------------
+\subsubsection{Temperature and Strain Rate~Effects}\label{subsec:TempSReffect}
 %----------------------------------------------------------------------------------
@@
 Conversely, lower temperatures and higher strain rates can lead to incomplete dynamic recrystallization.
-At high temperatures, the increased mobility of both atoms and dislocations facilitates the formation of fresh grain boundaries and promotes the growth of new grains, resulting
+At high temperatures, the~increased mobility of both atoms and dislocations facilitates the formation of fresh grain boundaries and promotes the growth of new grains, resulting
 in a more refined and isotropic grain structure.
-In addition, higher temperatures can raise the proportion of recrystallized material, with the enhanced dislocation mobility contributing to new grain creation.
-Consequently, this may result in a substantial change of the microstructure and the mechanical properties of the material.
-Figure \ref{fig:TempEffect} and Figure \ref{fig:SREffect} display the simulated results of the DRX fraction of P20 steel under different deformation conditions.
-Figure \ref{fig:TempEffect} shows that as the temperature increases, the extent of dynamic recrystallization widens.
+In addition, higher temperatures can raise the proportion of recrystallized material, with~the enhanced dislocation mobility contributing to new grain creation.
+Consequently, this may result in a substantial change in the microstructure and the mechanical properties of the material.
+Figures~\ref{fig:TempEffect} and \ref{fig:SREffect} display the simulated results of the DRX fraction of P20 steel under different deformation conditions.
+Figure~\ref{fig:TempEffect} shows that as the temperature increases, the~extent of dynamic recrystallization widens.
 The gradual increase in the dynamic recrystallization fraction in the center is noticeable, spreading outward.
@@
 The dynamic recrystallization degree ($X_{drx}^{p}$) unequivocally grows with the increase in temperature and reduction.
-At $45\%$ and $60\%$ reduction, the $X_{drx}^{p}$ of P20 steel
+At $45\%$ and $60\%$ reduction, the~$X_{drx}^{p}$ of P20 steel
 attained $100\%$ in the center of the specimen at all the initial sample temperatures.
-Indeed, the plastic deformation of a material is accompanied by the creation of dislocations.
-These dislocations represent a "storage of elastic energy".
-When the temperature is high enough, the dislocations become spontaneously mobile and cause a reorganization of the crystal structure in two stages: restoration and recrystallization.
-The nature of the phases remains unchanged (those that are thermodynamically stable), and the atoms retain the same lattice.
-However, the grain boundaries and the orientation of the crystallites undergo changes.
+Indeed, the~plastic deformation of a material is accompanied by the creation of dislocations.
+These dislocations represent a ``storage of elastic energy''.
+When the temperature is high enough, the~dislocations become spontaneously mobile and cause a reorganization of the crystal structure in two stages: restoration and recrystallization.
+The nature of the phases remains unchanged (those that are thermodynamically stable), and~the atoms retain the same lattice.
+However, the~grain boundaries and the orientation of the crystallites undergo~changes.
 
@@
 \includegraphics[height=0.6\columnwidth]{Figures/Temp_DRX}
-\caption{$X_{drx}^{p}$ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
+\caption{$X_{drx}^{p}$ %MDPI: Done
+ values at a fixed strain rate of $\mdot{\varepsilon}=0.01~\ps$ for different reductions and initial temperatures $T_0$.}
 \label{fig:TempEffect}
 \end{figure}
-\begin{figure}[H]
-\centering
-\includegraphics[height=0.6\columnwidth]{Figures/SR_DRX}
-\caption{$X_{drx}^{p}$ values at a fixed $T_0=1150\celsius$ for different reductions and strain rates.}
+\unskip
+\begin{figure}[H]
+\centering
+\includegraphics[height=0.55\columnwidth]{Figures/SR_DRX}
+\caption{$X_{drx}^{p}$ %MDPI: Done
+ values at a fixed $T_0=1150\celsius$ for different reductions and strain~rates.}
 \label{fig:SREffect}
@@
 The amount of elastic energy stored by a material increases with the degree of deformation, initiating restoration and recrystallization at a lower temperature.
-As shown in Figure \ref{fig:SREffect}, escalating strain rates result in a decrease in the extent of recrystallization due to reduced dynamic recrystallization magnitude.
-This result is due to the faster strain rate, which increases the critical strain and decreases the chance of internal dynamic recrystallization in the material.
-
-%----------------------------------------------------------------------------------
-\subsubsection{Comparison with some experiments}\label{subsec:ExpValid}
+As shown in Figure~\ref{fig:SREffect}, escalating strain rates result in a decrease in the extent of recrystallization due to reduced dynamic recrystallization magnitude.
+This result is due to the faster strain rate, which increases the critical strain and decreases the chance of internal dynamic recrystallization in the~material.
+
+%----------------------------------------------------------------------------------
+\subsubsection{Comparison with Some~Experiments}\label{subsec:ExpValid}
 %----------------------------------------------------------------------------------
@@
 In this section, we will compare experimental and simulation data by observing the dynamic recrystallization percentage of selected regions.
-Figure \ref{fig:expNumDRX} shows the comparison between experimental data and simulation data for a test conducted at a temperature of $1150\celsius$ with a strain rate of $\mdot{\varepsilon}=0.1~\ps$.
+Figure~\ref{fig:expNumDRX} shows a comparison between experimental data and simulation data for a test conducted at a temperature of $1150~\celsius$ with a strain rate of $\mdot{\varepsilon}=0.1~\ps$.
 Four zones were chosen to observe the percentage of recrystallization, ranging from $5\%$ to $100\%$.
 The $5\%$ corresponds to the dead zone, representing the contact area between the sample and die experiencing friction effects.
-In contrast, $100\%$ corresponds to the value observed at the center of the sample where deformation is the highest.
+In contrast, $100\%$ corresponds to the value observed at the center of the sample, where deformation is the highest.
 The temperature is elevated at the center of the sample, leading to a significant accumulation of energy.
-Conversely, at the edges of the sample, a relatively complete recrystallization is observed.
+Conversely, at~the edges of the sample, a~relatively complete recrystallization is observed.
 This is because the temperature during deformation shifts from the center towards the upper and lower regions of the piece (due to the fact that the anvils are cooled), allowing recrystallization to occur.
-Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX} (d)) in the dead zone, while small grains (Figure \ref{fig:expNumDRX} (a)) are observed in the center of the sample, resulting from complete recrystallization.
+Microscopic observations of each zone show large grains (Figure \ref{fig:expNumDRX}d) in the dead zone, while small grains (Figure \ref{fig:expNumDRX}a) are observed in the center of the sample, resulting from complete~recrystallization.
 
@@
 \includegraphics[width=0.98\columnwidth]{Figures/drxExpNum}
-\caption{Experimental and numerical $X_{drx}^{p}$ values for $T_0=1150\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
+\caption{Experimental %MDPI: Done
+ and numerical $X_{drx}^{p}$ values for $T_0=1150~\celsius$ and strain rate $\mdot{\varepsilon}=0.1~\ps$.}
 \label{fig:expNumDRX}
@@
 
-Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level.
+{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an~initial temperature $T=1050~\celsius$, and a reduction of $45\%$ (i.e., $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level.
 It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape.
-As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}^{p}$ is less than $5\%$ and the microstructure enhances very large grains.
-We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75\%$ to $90\%$.
+As~can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}^{p}$ is less than $5\%$ and the microstructure enhances very large grains.
+We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}^{p}$ is in the range of $75$ to $90\%$.}
 \begin{figure}[H]
@@
 \includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
-\caption{Comparison of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
+\caption{{Comparison %MDPI: Done
+ of the micrography and numerical $X_{drx}^{p}$ values for $T_0=1050~\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$, and $45\%$ reduction ($\varepsilon=0.55$).}}
 \label{fig:expNumDRX2}
@@
 In this study, we used the abilities of the ANN technique to deeply comprehend the dynamic recrystallization process and its adaptations in varying conditions.
-Through the fusion of ANN modeling, fundamental material models, simulation software, and experimental confirmation, a comprehensive framework has been created that greatly enhances the materials science and engineering field.
+Through the fusion of ANN modeling, fundamental material models, simulation software, and~experimental confirmation, a~comprehensive framework has been created that greatly enhances the materials science and engineering fields.
 Initially, we successfully used an ANN model to efficiently filter flow stress curves, which enabled us to predict critical conditions using the Poliak model.
-This allows us to accurately anticipate the conditions at which the DRX process begins, providing a valuable tool for predicting material behavior under specific deformation scenarios.
-
-We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volume fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
+This allowed us to accurately anticipate the conditions at which the DRX process begins, providing a valuable tool for predicting material behavior under specific deformation~scenarios.
+
+We used the predicted critical conditions as input into the JMAK model, resulting in the successful prediction of the volume fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
 This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more deep comprehension of the complex processes occurring during deformation.
-Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests.
-This allowed us to capture the process's response to varying conditions without bias.
-By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.
-
-It is noteworthy that although our research represents a significant milestone, it also presents opportunities for future exploration.
-Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
-Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace or other applications.
+\linebreak Taking our investigation further, we integrated the JMAK model into the widely used ABAQUS software to simulate the evolution of DRX during hot compression tests.
+\linebreak This allowed us to capture the process's response to varying conditions without bias.
+By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive~models.
+
+\textls[-10]{It is noteworthy that although our research represents a significant milestone, it also presents opportunities for future exploration.
+Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and~refining the integration process.
+Moreover, the~successful connection of theory, simulation, and~experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace or other~applications.}
 
@@
 visualization, O.P.;
-supervision, M.J., A.T. and O.P.;
+supervision, M.J., A.T., and O.P.;
 project administration, M.J.;
 funding acquisition, M.J.
-All authors have read and agreed to the published version of the manuscript.}
+All authors have read and agreed to the published version of the~manuscript.}
 
@@
 
-\acknowledgments{The authors acknowledge Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Abdelhalim Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK
-
-\conflictsofinterest{The authors declare no conflict of interest.}
+\acknowledgments{The authors acknowledge Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Abdelhalim Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and~Ecole Nationale d'Ingenieurs de Tarbes, France, for~providing technical data, materials, and~testing~facilities.}%MDPI: We removed titles here: OK
+
+\conflictsofinterest{The authors declare no conflicts of~interest.}
 
@@
 DRX & Dynamic recrystallization \\
-$X_{drx}^{e,p}$ & DRX's Volume fraction : $e, p$ for experimental and prediction respectively \\
-FE  & Finite Element \\
+$X_{drx}^{e,p}$ & DRX's volume fraction : $e, p$ for experimental and predicted values, respectively \\
+FE  & Finite element \\
 %HS  & Hansel--Spittel \\
@@
 %% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
+%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
+If~the appendix sections contain a heading then change the argument to "yes".
 %\appendixstart
@@
 %=====================================
-\bibliography{bibliography}
+\begin{thebibliography}{999}
+
+\bibitem[Javidikia \em{et~al.}(2023)Javidikia, Sadeghifar, Champliaud, and
+  Jahazi]{Javidikia-2023}
+Javidikia, M.; Sadeghifar, M.; Champliaud, H.; Jahazi, M.
+\newblock Grain size and temperature evolutions during linear friction welding
+  of Ni-base superalloy Waspaloy: Simulations and experimental validations.
+\newblock {\em J. Adv. Join. Process.} {\bf 2023}, {\em
+  8},~100150.
+\newblock {\url{https://doi.org/10.1016/j.jajp.2023.100150}}.
+
+\bibitem[Shen \em{et~al.}(2021)Shen, Zhang, Hu, Sun, Gao, Liu, and
+  Yu]{Shen-2021}
+Shen, J.; Zhang, L.; Hu, L.; Sun, Y.; Gao, F.; Liu, W.; Yu, H.
+\newblock Effect of subgrain and the associated DRX behaviour on the texture
+  modification of Mg-6.63 Zn-0.56 Zr alloy during hot tensile deformation.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
+  823},~141745.
+\newblock {\url{https://doi.org/10.1016/j.msea.2021.141745}}.
+
+\bibitem[Babu \em{et~al.}(2022)Babu, Mozumder, Athreya, Sarma, and
+  Mandal]{Babu-2022}
+Babu, K.A.; Mozumder, Y.H.; Athreya, C.N.; Sarma, V.S.; Mandal, S.
+\newblock Implication of initial grain size on DRX mechanism and grain
+  refinement in super-304H SS in a wide range of strain rates during
+  large-strain hot deformation.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2022}, {\em
+  832},~142269.
+\newblock {\url{https://doi.org/10.1016/j.msea.2021.142269}}.
+
+\bibitem[Peng \em{et~al.}(2022)Peng, Guo, Liu, Barella, Liang, Gruttadauria,
+  and Mapelli]{Peng-2022}
+Peng, Y.; Guo, S.; Liu, C.; Barella, S.; Liang, S.; Gruttadauria, A.; Mapelli,
+  C.
+\newblock Dynamic recrystallization behavior of low-carbon steel during hot
+  rolling process: Modeling and simulation.
+\newblock {\em J. Mater. Res. Technol.} {\bf 2022}, {\em
+  20},~1266--1290.
+\newblock {\url{https://doi.org/10.1016/j.jmrt.2022.07.039}}.
+
+\bibitem[Najafizadeh and Jonas(2006)]{Najafizadeh-2006}
+Najafizadeh, A.; Jonas, J.J.
+\newblock Predicting the critical stress for initiation of dynamic
+  recrystallization.
+\newblock {\em ISIJ Int.} {\bf 2006}, {\em 46},~1679--1684.
+\newblock {\url{https://doi.org/10.2355/isijinternational.46.1679}}.
+
+\bibitem[Gottstein \em{et~al.}(2004)Gottstein, Frommert, Goerdeler, and
+  Sch{\"a}fer]{Gottstein-2004}
+Gottstein, G.; Frommert, M.; Goerdeler, M.; Sch{\"a}fer, N.
+\newblock Prediction of the critical conditions for dynamic recrystallization
+  in the austenitic steel 800H.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2004}, {\em
+  387},~604--608.
+\newblock {\url{https://doi.org/10.1016/j.msea.2004.02.098}}.
+
+\bibitem[Ryan and McQueen(1989)]{Ryan-1989}
+Ryan, N.D.; McQueen, H.J.
+\newblock Dynamic recovery, strain hardening and flow stress in hot working of
+  316 steel.
+\newblock {\em Czechoslov. J. Phys. B} {\bf 1989}, {\em
+  39},~458--465.
+\newblock {\url{https://doi.org/10.1007/BF01597803}}.
+
+\bibitem[Ryan and McQueen(1990{\natexlab{a}})]{Ryan-1990}
+Ryan, N.D.; McQueen, H.J.
+\newblock Dynamic softening mechanisms in 304 austenitic stainless steel.
+\newblock {\em Can. Metall. Q.} {\bf 1990}, {\em
+  29},~147--162.
+\newblock {\url{https://doi.org/https://doi.org/10.1179/cmq.1990.29.2.147}}.
+
+\bibitem[Ryan and McQueen(1990{\natexlab{b}})]{Ryan-1990-2}
+Ryan, N.D.; McQueen, H.J.
+\newblock Flow stress, dynamic restoration, strain hardening and ductility in
+  hot working of 316 steel.
+\newblock {\em J. Mater. Process. Technol.} {\bf 1990}, {\em
+  21},~177--199.
+\newblock {\url{https://doi.org/10.1016/09240136(90)90005F}}.
+
+\bibitem[Poliak and Jonas(1996)]{Poliak-1996}
+Poliak, E.I.; Jonas, J.J.
+\newblock A one-parameter approach to determining the critical conditions for
+  the initiation of dynamic recrystallization.
+\newblock {\em Acta Mater.} {\bf 1996}, {\em 44},~127--136.
+\newblock {\url{https://doi.org/10.1016/1359-6454(95)00146-7}}.
+
+\bibitem[Poliak and Jonas(2003{\natexlab{a}})]{Poliak-2003}
+Poliak, E.I.; Jonas, J.J.
+\newblock Initiation of dynamic recrystallization in constant strain rate hot
+  deformation.
+\newblock {\em ISIJ Int.} {\bf 2003}, {\em 43},~684--691.
+\newblock {\url{https://doi.org/10.2355/isijinternational.43.684}}.
+
+\bibitem[Poliak and Jonas(2003{\natexlab{b}})]{Poliak-2003-2}
+Poliak, E.I.; Jonas, J.J.
+\newblock Critical strain for dynamic recrystallization in variable strain rate
+  hot deformation.
+\newblock {\em ISIJ Int.} {\bf 2003}, {\em 43},~692--700.
+\newblock {\url{https://doi.org/10.2355/isijinternational43692}}.
+
+\bibitem[Jonas and Poliak(2003)]{Jonas-2003}
+Jonas, J.J.; Poliak, E.I.
+\newblock The critical strain for dynamic recrystallization in rolling mills.
+\newblock In \emph{Materials Science Forum}; Trans Tech Publications Ltd.: Stafa-Zurich, Switzerland, %MDPI: O.P. Added 
+  2003; Volume 426, pp. 57--66.
+\newblock {\url{https://doi.org/10.4028/www.scientific.net/msf.426-432.57}}.
+
+\bibitem[Avrami(1939)]{Avrami-1939}
+Avrami, M.
+\newblock Kinetics of Phase Change. I General Theory.
+\newblock {\em J. Chem. Phys.} {\bf 1939}, {\em 7},~1103--1112.
+\newblock {\url{https://doi.org/10.1063/1.1750380}}.
+
+\bibitem[Li \em{et~al.}(2015)Li, Duan, Li, and Wu]{Li-2015}
+Li, X.; Duan, L.; Li, J.; Wu, X.
+\newblock Experimental study and numerical simulation of dynamic
+  recrystallization behavior of a micro-alloyed plastic mold steel.
+\newblock {\em Mater. Des. } {\bf 2015}, {\em 66},~309--320.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2014.10.076}}.
+
+\bibitem[Estrin and Mecking(1984)]{Estrin-1984}
+Estrin, Y.; Mecking, H.
+\newblock A unified phenomenological description of work hardening and creep
+  based on one-parameter models.
+\newblock {\em Acta Metall.} {\bf 1984}, {\em 32},~57--70.
+\newblock {\url{https://doi.org/0001-6160(84)90202-5}}.
+
+\bibitem[Mecking and Kocks(1981)]{Mecking-1981}
+Mecking, H.; Kocks, U.F.
+\newblock Kinetics of flow and strain-hardening.
+\newblock {\em Acta Metall.} {\bf 1981}, {\em 29},~1865--1875.
+\newblock {\url{https://doi.org/10.1016/0001-6160(81)90112-7}}.
+
+\bibitem[Zhang \em{et~al.}(2016)Zhang, Zhang, Xu, Xia, and Shen]{Zhang-2016}
+Zhang, C.; Zhang, L.; Xu, Q.; Xia, Y.; Shen, W.
+\newblock The kinetics and cellular automaton modeling of dynamic
+  recrystallization behavior of a medium carbon Cr-Ni-Mo alloyed steel in hot
+  working process.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2016}, {\em
+  678},~33--43.
+\newblock {\url{https://doi.org/10.1016/j.msea.2016.09.056}}.
+
+\bibitem[Cho \em{et~al.}(2005)Cho, Jeong, Cha, Bae, and Lee]{Cho-2005}
+Cho, J.R.; Jeong, H.S.; Cha, D.J.; Bae, W.B.; Lee, J.W.
+\newblock Prediction of microstructural evolution and recrystallization
+  behaviors of a hot working die steel by FEM.
+\newblock {\em J. Mater. Process. Technol.} {\bf 2005}, {\em
+  160},~1--8.
+\newblock {\url{https://doi.org/10.1016/j.jmatprotec.2004.01.001}}.
+
+\bibitem[Razali and Joun(2021)]{Razali-2021}
+Razali, M.K.; Joun, M.S.
+\newblock A new approach of predicting dynamic recrystallization using directly
+  a flow stress model and its application to medium Mn steel.
+\newblock {\em J. Mater. Res. Technol.} {\bf 2021}, {\em
+  11},~1881--1894.
+\newblock {\url{https://doi.org/10.1016/j.jmrt.2021.02.026}}.
+
+\bibitem[Wan \em{et~al.}(2017)Wan, Sun, Hu, and Yu]{Wan-2017}
+Wan, Z.; Sun, Y.; Hu, L.; Yu, H.
+\newblock Experimental study and numerical simulation of dynamic
+  recrystallization behavior of TiAl-based alloy.
+\newblock {\em Mater. Des.} {\bf 2017}, {\em 122},~11--20.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2017.02.088}}.
+
+\bibitem[Li \em{et~al.}(2018)Li, Tan, and Zhao]{Li-2018}
+Li, C.; Tan, Y.; Zhao, F.
+\newblock Finite element simulation and process optimization of microstructure
+  evolution in the formation of Inconel 718 alloy bolts.
+\newblock {\em Mater. Res. Express} {\bf 2018}, {\em 6},~026578.
+\newblock {\url{https://doi.org/10.1088/2053-1591/aaf2bb}}.
+
+\bibitem[Cui \em{et~al.}(2016)Cui, Kong, Wang, Chen, and Zhou]{Cui-2016}
+Cui, N.; Kong, F.; Wang, X.; Chen, Y.; Zhou, H.
+\newblock Hot deformation behavior and dynamic recrystallization of a
+  $\beta$-solidifying TiAl alloy.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2016}, {\em
+  652},~231--238.
+\newblock {\url{https://doi.org/10.1016/j.msea.2015.11.097}}.
+
+\bibitem[Chen \em{et~al.}(2023)Chen, Sun, Yang, Liu, Si, and Zhou]{Chen-2023}
+Chen, X.; Sun, J.; Yang, Y.; Liu, B.; Si, Y.; Zhou, J.
+\newblock Finite Element Analysis of Dynamic Recrystallization Model and
+  Microstructural Evolution for GCr15 Bearing Steel Warm--Hot Deformation
+  Process.
+\newblock {\em Materials} {\bf 2023}, {\em 16},~4806.
+\newblock {\url{https://doi.org/10.3390/ma16134806}}.
+
+\bibitem[{Tize Mha} \em{et~al.}(2023){Tize Mha}, Dhondapure, Jahazi, Tongne,
+  and Pantalé]{TizeMha-2023}
+{Tize Mha}, P.; Dhondapure, P.; Jahazi, M.; Tongne, A.; Pantalé, O.
+\newblock {Interpolation and Extrapolation Performance Measurement of
+  Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium
+  Carbon Steel}.
+\newblock {\em Metals} {\bf 2023}, {\em 13}.
+\newblock {\url{https://doi.org/10.3390/met13030633}}.
+
+\bibitem[Pantalé \em{et~al.}(2022)Pantalé, {Tize Mha}, and
+  Tongne]{Pantale-2021}
+Pantalé, O.; {Tize Mha}, P.; Tongne, A.
+\newblock {Efficient implementation of non-linear flow law using neural network
+  into the Abaqus Explicit FEM code}.
+\newblock {\em Finite Elem. Anal. Des.} {\bf 2022}, {\em
+  198},~103647.
+\newblock {\url{https://doi.org/10.1016/j.finel.2021.103647}}.
+
+\bibitem[Galos \em{et~al.}(2022)Galos, Das, Sutcliffe, and Mouritz]{Galos-2022}
+Galos, J.; Das, R.; Sutcliffe, M.P.; Mouritz, A.P.
+\newblock {Review of balsa core sandwich composite structures}.
+\newblock {\em Mater. Des.} {\bf 2022}, \emph{221}, 111013.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2022.111013}}.
+
+\bibitem[Abadi \em{et~al.}(2016)Abadi, Barham, Chen, Chen, Davis, Dean, Devin,
+  Ghemawat, Irving, Isard, Kudlur, Levenberg, Monga, Moore, Murray, Steiner,
+  Tucker, Vasudevan, Warden, Wicke, Yu, and Zheng]{Abadi-2016}
+Abadi, M.; Barham, P.; Chen, J.; Chen, Z.; Davis, A.; Dean, J.; Devin, M.;
+  Ghemawat, S.; Irving, G.; Isard, M.;  et~al.
+\newblock {TensorFlow: A System for Large-Scale Machine Learning}.
+\newblock In {Proceedings of the 12th {{USENIX}} Conference
+  on {{Operating Systems Design}} and {{Implementation}}}, Savannah, GA, {USA},  2--4 November 2016; p. 265--283.
+
+\bibitem[Kingma and Lei(2015)]{Kingma-2015}
+Kingma, D.P.; Lei, J.
+\newblock {Adam: A method for stochastic optimization} \emph{arXiv} {\bf 2015}, arXiv:1412.6980.
+\newblock {\url{https://doi.org/10.48550/arXiv.1412.6980}}.
+
+\bibitem[Chen \em{et~al.}(2019)Chen, Zhang, Du, Wang, and Huang]{Chen-2019}
+Chen, X.; Zhang, J.; Du, Y.; Wang, G.; Huang, T.
+\newblock Dynamic Recrystallization Simulation for X12 Alloy Steel by CA Method
+  Based on Modified L-J Dislocation Density Model.
+\newblock {\em Metals} {\bf 2019}, {\em 9}, 1291.
+\newblock {\url{https://doi.org/10.3390/met9121291}}.
+
+\bibitem[Zener and Hollomon(1944)]{Zenner-1944}
+Zener, C.; Hollomon, J.H.
+\newblock Effect of strain rate upon plastic flow of steel.
+\newblock {\em J. Appl. Phys.} {\bf 1944}, {\em 15},~22--32.
+
+\bibitem[Chen \em{et~al.}(2014)Chen, Lin, Wen, Zhang, and He]{Chen-2014}
+Chen, X.M.; Lin, Y.; Wen, D.X.; Zhang, J.L.; He, M.
+\newblock Dynamic recrystallization behavior of a typical nickel-based
+  superalloy during hot deformation.
+\newblock {\em Mater. Des.} {\bf 2014}, {\em 57},~568--577.
+\newblock {\url{https://doi.org/10.1016/j.matdes.2013.12.072}}.
+
+\bibitem[Li \em{et~al.}(2019)Li, Wang, Li, Jiang, Wang, Zhang, Wang, and
+  Garmestani]{Li-2019}
+Li, L.; Wang, Y.; Li, H.; Jiang, W.; Wang, T.; Zhang, C.C.; Wang, F.;
+  Garmestani, H.
+\newblock Effect of the Zener-Hollomon parameter on the dynamic
+  recrystallization kinetics of Mg--Zn--Zr--Yb magnesium alloy.
+\newblock {\em Comput. Mater. Sci.} {\bf 2019}, {\em
+  166},~221--229.
+\newblock {\url{https://doi.org/10.1016/j.commatsci.2019.05.015}}.
+
+\bibitem[Wang \em{et~al.}(2021)Wang, Chen, Ouyang, Zhou, Hu, and Le]{Wang-2021}
+Wang, T.; Chen, Y.; Ouyang, B.; Zhou, X.; Hu, J.; Le, Q.
+\newblock Artificial neural network modified constitutive descriptions for hot
+  deformation and kinetic models for dynamic recrystallization of novel AZE311
+  and AZX311 alloys.
+\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
+  816},~141259.
+\newblock {\url{https://doi.org/10.1016/j.msea.2021.141259}}.
+
+\bibitem[Johnson and Cook(1983)]{Johnson-1983}
+Johnson, G.R.; Cook, W.H.
+\newblock {A constitutive model and data for materials subjected to large
+  strains, high strain rates, and high temperatures}.
+\newblock {In  Proceedings of the 7th International Symposium on Ballistics, 
+  Hague, The Netherlands, 19--21 April} {1983}; \linebreak pp. 541--547.
+\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}.
+
+\bibitem[Zerilli and Armstrong(1987)]{Zerilli-1987}
+Zerilli, F.J.; Armstrong, R.W.
+\newblock {Dislocation‐mechanics‐based constitutive relations for material
+  dynamics calculations}.
+\newblock {\em J. Appl. Phys.} {\bf 1987}, {\em 61},~1816--1825.
+\newblock {\url{https://doi.org/10.1063/1.338024}}.
+
+\bibitem[Hensel and Spittel(1978)]{Hensel-1978}
+Hensel, A.; Spittel, T.
+\newblock {\em {Kraft- und Arbeitsbedarf Bildsamer Formgebungsverfahren}};
+  Deutscher Verlag für Grundstoffindustrie: Leipzig, Germany, %MDPI: Added
+  1978.
+
+\bibitem[Sellars and McTegart(1966)]{Sellars-1966}
+Sellars, C.M.; McTegart, W.J.
+\newblock {On the mechanism of hot deformation}.
+\newblock {\em Acta Metall.} {\bf 1966}, {\em 14},~1136–1138.
+\newblock {\url{https://doi.org/10.1016/0001-6160(66)90207-0}}.
+
+\bibitem[Zhang \em{et~al.}(2019)Zhang, Sun, and Wang]{Zhang-2019}
+Zhang, M.; Sun, X.; Wang, Y.
+\newblock Elevated temperature deformation characteristics of 15Mn7 steels.
+\newblock {\em Procedia Manuf.} {\bf 2019}, {\em 37},~360--366.
+\newblock {\url{https://doi.org/10.1016/j.promfg.2019.12.060}}.
+
+\bibitem[Sun \em{et~al.}(2020)Sun, Zhang, Wang, Sun, and Wang]{Sun-2020}
+Sun, X.; Zhang, M.; Wang, Y.; Sun, Y.; Wang, Y.
+\newblock Kinetics and numerical simulation of dynamic recrystallization
+  behavior of medium Mn steel in hot working.
+\newblock {\em Steel Res. Int.} {\bf 2020}, {\em 91},~1900675.
+\newblock {\url{https://doi.org/10.1002/srin.201900675}}.
+
+\end{thebibliography}
 

### 2023-10-16 Metals-2023-2.tex
Rename final production article

--- 2023-10-16 Article.tex
@@
 \makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
+\pubvolume{13}
+\issuenum{10}
+\articlenumber{1746}
 \pubyear{2023}
 \copyrightyear{2023}
-\externaleditor{Academic Editor: Firstname Lastname}
+\externaleditor{Academic Editor: Zhanwei Yuan}
 \datereceived{31 August 2023 }
@@
 \dateaccepted{13 October 2023 }
-\datepublished{ }
+\datepublished{15 October 2023 }
 %\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
 %\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
-\hreflink{https://doi.org/} % If needed use \linebreak
+\hreflink{https://doi.org/10.3390/\linebreak met13101746} % If needed use \linebreak
 %\doinum{}
@@
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and~Application}
+\TitleCitation{Artificial Neural Network-Based Critical Conditions for the Dynamic Recrystallization of Medium Carbon Steel and Application}
 %MDPI: Title modified, please confirm.
@@
 % Keywords
-\keyword{artificial neural network; constitutive flow law; Gleeble simulator; dynamic recrystallization; finite element analysis}
+\keyword{\textls[-13]{artificial neural network; constitutive flow law; Gleeble simulator; dynamic recrystallization; finite element analysis}}
 
@@
 
-As the occurrence of DRX softens the material, the~deformation loads during hot deformation must be adjusted from one pass to another to have a more accurate prediction of DRX.
+\textls[-12]{As the occurrence of DRX softens the material, the~deformation loads during hot deformation must be adjusted from one pass to another to have a more accurate prediction of DRX.
 Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
@@
 According to Gottstein \eal~\cite{Gottstein-2004}, the~critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
-The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$, where $\sigma$ is the stress and $\varepsilon$ is the~strain.
+The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$, where $\sigma$ is the stress and $\varepsilon$ is the~strain.}
 
@@
 The raw stress--strain data were exported from the Gleeble thermomechanical simulator as true stress and true strain, and~the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure~\ref{fig:RawData}.
-All stress--strain data are composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$ increments.
+All stress--strain data are composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.001$~increments.
 \begin{figure}[H]
@@
 
-As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
+\textls[-20]{As previously stated, critical values for DRX initiation are determined by identifying the inflection point on the $\theta(\sigma)$ curve between $\varepsilon=0$ and $\varepsilon_c$.
 One challenge is calculating the derivative of stress versus strain values numerically, as~compression test data exhibit oscillations, as~depicted in Figure~\ref{fig:RawData}.
-It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ directly.
-
-To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver~\cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
+It is not feasible to compute the derivative $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$~directly.}
+
+\textls[-5]{To overcome this difficulty, certain authors propose smoothing out the empirical data (perhaps through the utilization of the Excel solver~\cite{Najafizadeh-2006}) or discovering an analytical function (such as a polynomial with a relatively high degree) through a minimization algorithm.
 \linebreak However, depending on the degree of the polynomial, for the same stress--strain curve, multiple solutions may be obtained.
-This results in multiple possible forms for the $\theta(\sigma)$ function.
+This results in multiple possible forms for the $\theta(\sigma)$~function.}
 
@@
 
-Thus, for a $7-5$ network, $N_{int}=60$.
+Thus, for a 7-5 network, $N_{int}=60$.
 \begin{figure}[H]
@@
 \centering
-\includegraphics[width=0.7\columnwidth]{Figures/AnnFit}
+\includegraphics[width=0.8\columnwidth]{Figures/AnnFit}
 \caption{Filtering of the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
@@
 \centering
-\includegraphics[width=0.7\columnwidth]{Figures/AnnTheta}
+\includegraphics[width=0.8\columnwidth]{Figures/AnnTheta}
 \caption{Computation of the hardening curve $\theta(\sigma)$ from the stress--strain data using the ANN for $\mdot\varepsilon=0.001~\ps$ and $T=1050~\celsius$.}
@@
 \end{equation}
+
 Similarly, %MDPI:  Ok
@@
 
-The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure~\ref{fig:nDRX}, where a comparison between the experimental and predicted values is made for the strain rate $\mdot\varepsilon=0.001~\ps$ and three temperatures (1050 $^\circ$C, 1150 $^\circ$C and 1250 $^\circ$C).
+The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure~\ref{fig:nDRX}, where a comparison between the experimental and predicted values is made for the strain rate $\mdot\varepsilon=0.001~\ps$ and three temperatures (1050 $^\circ$C, 1150 $^\circ$C and 1250~$^\circ$C).
 \begin{figure}[H]
@@
 \centering
-\includegraphics[width=0.7\columnwidth]{Figures/Conv-ANN-6}
+\includegraphics[width=0.75\columnwidth]{Figures/Conv-ANN-6}
 \caption{Evolution of the convergence of the models during the training procedure for the \mbox{6 proposed} network~architectures.}
@@
 visualization, O.P.;
-supervision, M.J., A.T., and O.P.;
+supervision, M.J., A.T. and O.P.;
 project administration, M.J.;
@@
 
-\conflictsofinterest{The authors declare no conflicts of~interest.}
+\conflictsofinterest{The authors declare no conflict of~interest.}
 
@@
   Carbon Steel}.
-\newblock {\em Metals} {\bf 2023}, {\em 13}.
+\newblock {\em Metals} {\bf 2023}, {\em 13}, 633.
 \newblock {\url{https://doi.org/10.3390/met13030633}}.
